### 2016-09-21 paper.tex
template

\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscriptaddress]{revtex4}

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage[pdftex]{graphicx}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}

\begin{document}

\bibliographystyle{apsrev}

%
% Title
%

\title{Linear Optics Interferometry}

%
% Authors
%

\author{Si-Hui Tan}
\email[]{sihui\_tan@sutd.edu.sg}
\affiliation{Singapore University of Technology and Design, 8 Somapah Road, Singapore}

\author{Peter P. Rohde}
\email[]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Computation and Intelligent Systems (QCIS), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

\date{\today}

\frenchspacing

%
% Abstract
%

\begin{abstract}
\end{abstract}

\maketitle

\tableofcontents

\section{Introduction}

\section{Linear Optics Quantum Computation}

\section{Boson-sampling}

\section{Conclusion}

%
% Acknowledgments
%

\begin{acknowledgments}
\end{acknowledgments}

%
% Bibliography
%

\bibliography{paper}

\end{document}

### 2016-09-21 paper.tex
added colour codes
Suggested structure of document

@@
 \usepackage[colorlinks]{hyperref}
+\usepackage[dvipsnames]{xcolor}
+
+\newcommand{\sihui}[1]{{\color{Orchid}{#1}}}
+\newcommand{\peter}[1]{{\color{YellowGreen}{#1}}}
+\newcommand{\comment}[1]{{\color{blue}{#1}}}
 
@@
 
-\section{Linear Optics Quantum Computation}
+\sihui{Si-Hui can colour code things she adds like this}
 
-\section{Boson-sampling}
+\peter{And Peter can do it like this}
+
+\comment{Let's add comments and questions like this}
+
+\section{Mathematical Background}
+
+\comment{Mathematical representation for LO networks, and very basic background on quantum optics}
+
+\section{Optical Encoding of Quantum Information}
+
+\subsection{Single-Photons}
+
+\subsubsection{Polarisation}
+
+\subsubsection{Dual-Rail}
+
+\subsubsection{Time-Bins}
+
+\subsection{Continuous-Variables}
+
+\subsubsection{Coherent States}
+
+\subsubsection{Squeezed States}
+
+\section{Efficient Circuit Decompositions of Linear Optics Networks}
+
+\comment{Discuss the Reck et al. decomposition}
+
+\section{Experimental Implementation}
+
+\subsection{State Preparation}
+
+\subsubsection{Single-Photons}
+
+\subsubsection{Bell Pairs}
+
+\subsubsection{Coherent States}
+
+\subsubsection{Squeezed States}
+
+\subsection{Linear Optics Networks}
+
+\subsubsection{Bulk Optics}
+
+\subsubsection{Waveguides}
+
+\subsubsection{Time-Bins}
+
+\comment{Discuss fibre-loop architecture}
+
+\subsection{Measurement}
+
+\subsubsection{Photodetection}
+
+\comment{Discuss number-resolved and bucket detectors, multiplexed detection, APDs, current micropillar detectors}
+
+\subsubsection{Homodyning}
+
+\section{Applications for Linear Optics Interferometry}
+
+\subsection{Linear Optics Quantum Computation}
+
+\subsection{Boson-Sampling}
+
+\subsection{Quantum Metrology}
+
+\comment{Discuss NOON states - Heisenberg limited}
+
+\comment{Discuss MORDOR scheme}
+
+\subsection{Encrypted Quantum Computation}
+
+\section{State of the Art}
+
+\comment{Discuss where experiments are at at the moment}
 

### 2016-10-06 paper.tex
updated doc
updated title and affiliation

@@
 
-\title{Linear Optics Interferometry}
+\title{The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications}
 
@@
 \homepage{http://www.peterrohde.org}
-\affiliation{Centre for Quantum Computation and Intelligent Systems (QCIS), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
+\affiliation{Centre for Quantum Software \& Information (CQSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
 
@@
 
-\section{Mathematical Background}
+\section{Mathematical background}
 
@@
 
-\section{Optical Encoding of Quantum Information}
+\section{Optical encoding of quantum information}
 
-\subsection{Single-Photons}
+\subsection{Single-photons}
 
@@
 
-\subsubsection{Dual-Rail}
+\subsubsection{Dual-rail}
 
-\subsubsection{Time-Bins}
+\subsubsection{Time-bins}
 
-\subsection{Continuous-Variables}
+\subsection{Continuous-variables}
 
-\subsubsection{Coherent States}
+\subsubsection{Coherent states}
 
-\subsubsection{Squeezed States}
+\subsubsection{Squeezed states}
 
-\section{Efficient Circuit Decompositions of Linear Optics Networks}
+\section{Efficient circuit decompositions of linear optics networks}
 
@@
 
-\section{Experimental Implementation}
+\section{Experimental implementation}
 
-\subsection{State Preparation}
+\subsection{State preparation}
 
-\subsubsection{Single-Photons}
+\subsubsection{Single-photons}
 
-\subsubsection{Bell Pairs}
+\subsubsection{Bell pairs}
 
-\subsubsection{Coherent States}
+\subsubsection{Coherent states}
 
-\subsubsection{Squeezed States}
+\subsubsection{Squeezed states}
 
-\subsection{Linear Optics Networks}
+\subsection{Linear optics networks}
 
-\subsubsection{Bulk Optics}
+\subsubsection{Bulk-optics}
 
@@
 
-\subsubsection{Time-Bins}
+\subsubsection{Time-bins}
 
@@
 
-\section{Applications for Linear Optics Interferometry}
+\section{Applications for linear optics interferometry}
 
-\subsection{Linear Optics Quantum Computation}
+\subsection{Linear optics quantum computation}
 
-\subsection{Boson-Sampling}
+\subsection{Boson-sampling}
 
-\subsection{Quantum Metrology}
+\subsection{Quantum metrology}
 
@@
 
-\subsection{Encrypted Quantum Computation}
+\subsection{Encrypted quantum computation}
 
-\section{State of the Art}
+\section{State of the art}
 

### 2017-01-09 paper.tex
added ack
Added a new paragraph to math section.

@@
 \newcommand{\comment}[1]{{\color{blue}{#1}}}
+\newcommand{\ah}{\hat{a}}
+\newcommand{\adagh}{\hat{a}^\dag}
 
@@
 \section{Mathematical background}
+\comment{Mathematical representation for LO networks, and very basic background on quantum optics}\\
+\sihui{A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j,\alpha}$, where $j$ is the path label and $\alpha$ is a quantum number that describes any internal degrees of freedom of the photon.
+The creation and annihilation operators satisfy the bosonic comutator relationship $[\ah_{j,\alpha},\adagh_{k,\beta}]=\delta_{j,k}\delta_{\alpha,\beta}$.
+When multiple photons are present, they experience quantum interference when both quantum labels are the same.
 
-\comment{Mathematical representation for LO networks, and very basic background on quantum optics}
+A linear optical interferometer}
 
@@
 \begin{acknowledgments}
+P.P.R. is funded by an ARC Future Fellowship (project FT160100397).
 \end{acknowledgments}

### 2017-02-28 paper.tex
Additions to math. section.

--- 2016-10-06 paper.tex
@@
 \section{Mathematical background}
+\comment{Mathematical representation for LO networks, and very basic background on quantum optics}\\
+\sihui{A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer.
+The creation and annihilation operators satisfy the bosonic comutator relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.
+A similar commutator relationship can be  written up when more degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present.
+When multiple photons are present, they experience quantum interference when all quantum labels are the same.
 
-\comment{Mathematical representation for LO networks, and very basic background on quantum optics}
+The action of a $2d$-port linear optical interferometer (with an equal number of input and output ports) is expressed as an application of unitary operations on the creation operators,
+
+\begin{align}
+b_i^{\dag}=\sum_{j=1}^d U_{ij}a_j^\dag \ ,
+\end{align}
+where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in SU(d)$.
+All such transformation can be expressed as sequence of beamsplitters and waveplates \cite{bib:Reck1994}.
+In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons into a sequence of beamsplitters and internal transformations.
+Toolkits using group theory are being developed to deal with partial distinguishabilities among interfering photons \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}.
+Others use
+quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}.
+
+}
 

### 2017-04-04 paper.tex
added bits to paragraph on Reck et al.

@@
 \comment{Discuss the Reck et al. decomposition}
+The task of implementing an arbitrary quantum computation on linear optics comes down to implementing an arbitrary $n\times n$ unitary matrix.
+If a non-unitary transformation is desired, it can be embedded within a unitary matrix with larger dimensions.
+An algorithm for expressing an arbitrary unitary matrix in terms of beamsplitters and phase-shifters, or equivalently Mach-Zedner interferometers, exists \cite{bib:Reck1994,bib:Englert2001} and has been widely used {\bf (find examples)}.
+Later, it has been shown that any nontrivial beam splitter is universal for linear optics \cite{bib:Bouland2014}.
 

### 2017-04-14 paper.tex
Added a characterizations section.

--- 2017-02-28 paper.tex
@@
 
+Technical advancements have been made on many fronts.
+It is possible now to put single-photon sources and linear-optical networks on a silica chip.
+The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized.
+This increases the scalability of optical implementations of quantum information protocols.
+
 \section{Mathematical background}
 \comment{Mathematical representation for LO networks, and very basic background on quantum optics}\\
-\sihui{A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer.
+
+A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer.
 The creation and annihilation operators satisfy the bosonic comutator relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.
@@
 Others use
-quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}.
+quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}. \sihui{Experimental implementation [Walmsley, Jennewein]}
 
-}
+\section{Optical encoding of quantum information on single-photons}
 
-\section{Optical encoding of quantum information}
-
-\subsection{Single-photons}
+%\subsection{Single-photons}
 
@@
 
-\subsection{Continuous-variables}
+%\subsection{Continuous-variables}
 
-\subsubsection{Coherent states}
+%\subsubsection{Coherent states}
 
-\subsubsection{Squeezed states}
+%\subsubsection{Squeezed states}
 
@@
 
+The task of implementing an arbitrary quantum computation on linear optics comes down to implementing an arbitrary $n\times n$ unitary matrix.
+If a non-unitary transformation is desired, it can be embedded within a unitary matrix with larger dimensions.
+An algorithm for expressing an arbitrary unitary matrix {\it exactly} in terms of a sequence of $\mathcal{O}(n^2)$ beamsplitters and phase-shifters exists \cite{bib:Reck1994}.
+Alternatively, Mach-Zedner interferometer can also be used as building blocks instead of beamsplitters and phase shifters \cite{bib:Reck1994, bib:Englert2001}.
+Later, it has been shown that any nontrivial beam splitter, that does more than swapping modes around or add phases to them, is universal for linear optics \cite{bib:Bouland2014}.
+However, they do not provide a construction for arbitrary unitaries.
+
+If the linear optical transformations can be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
+Their approach reduces the required number of beamsplitters but increases the total number of optical elements needed increases by a factor of 2.
+
+\section{Reconstructing the linear optical network}
+\sihui{Discuss the role of quantum tomography here. 
+Algorithms using O'Brien and Laing, Schaffner and Tillmann--using single-photon, and two-photon inputs to reconstruct the Euler angles of the circuit.
+Others using coherent-state inputs which has a lower requirement on the state-preparation side.}
+
+In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase shifters is known once it is built.
+However, owing to manufacturing imperfections, a precise characterization of these devices is still needed post-production.
+One of the ways, this can be done is via a quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11} .
+However, quantum process tomography is an expensive method in terms of number of measurements required to characterize the network, and it becomes impractical for large optical networks which can be as large as 900 modes (check citations for number of modes).
+
 \section{Experimental implementation}
@@
 \subsection{State preparation}
+\sihui{Cat state--Schoelkopf group}
 

### 2017-04-14 paper.tex
Added to characterization section.

@@
 One of the ways, this can be done is via a quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11} .
-However, quantum process tomography is an expensive method in terms of number of measurements required to characterize the network, and it becomes impractical for large optical networks which can be as large as 900 modes (check citations for number of modes).
+However, quantum process tomography is an expensive method in terms of number of measurements required to characterize the network, and it becomes impractical for large optical networks which can now be as large as 900 modes (check citations for number of modes).
+Alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.
+
+Generally, the unitary matrix of the $d\times d$ linear optical device are complex numbers $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$.
+The scheme in \cite{bib:Laing12} relies on injecting one-photon and two-photon states into the linear optical network with correlated photon detection.
+First, they note some equivalencies: two unitaries $U$ and $U'$ are equivalent if there exist two diagonal unitary matrices $D_1^U$ and $D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are regarded as unknown and trivial phases on the input and output ports of the network, to which the one-photon and two-photon data are insensitive to.
+This reduces the first row and first column elements to real numbers, i.e.
+$\theta_{1j}=\theta_{i1}=0$.
+Second, the photon statistics remain unchanged under the complex conjugation of $U$.
+Thus, the imaginary part of $M_{2,2}$ must be non-negative.
 

### 2017-04-17 paper.tex
Added more to characterization section.

@@
 
-\comment{Discuss the Reck et al. decomposition}
-
 The task of implementing an arbitrary quantum computation on linear optics comes down to implementing an arbitrary $n\times n$ unitary matrix.
@@
 \section{Reconstructing the linear optical network}
-\sihui{Discuss the role of quantum tomography here. 
-Algorithms using O'Brien and Laing, Schaffner and Tillmann--using single-photon, and two-photon inputs to reconstruct the Euler angles of the circuit.
-Others using coherent-state inputs which has a lower requirement on the state-preparation side.}
 
@@
 Thus, the imaginary part of $M_{2,2}$ must be non-negative.
+Then assuming that the first two rows and columns are non-vanishing, and that there is no total loss in the interferometer, the matrix to be recovered is
+\begin{align}
+U=\left (\begin{array}{cccc}
+r_{11} & r_{12} & \ldots & r_{1m} \\
+r_{21} & r_{22}e^{i\theta_{22}} &\ldots & r_{2m}e^{i\theta_{2m}}\\
+\vdots & \vdots & \ddots & \vdots \\
+r_{m1} & r_{m2}e^{i\theta_{m2}} & \ldots & r_{mm}e^{i\theta_{mm}}
+ \end{array}\right ) \ .
+\end{align}
+In the paper, they showed that it is possible to write the paramaters $r_{ij}$, and $\theta_{ij}$ for $i,j\geq 2$ in terms of the $2m-1$ real parameters of the first column and row, and the visibility of two-photon inputs.
+The remaining $2m-1$ real parameters can be found via one-photon
+transmissions.
+An increased accuracy of the characterization is possible by estimating and correcting systematic errors that arise due to mode mismatch \cite{Dhand16}.
+Others have used numerical methods to find the closest parameters that yield the observed visibilities \cite{bib:Spagnolo16,bib:Tillmann16}.
+
+Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead \cite{bib:Rahimi-Keshari13,bib:Heilmann15}.
+Such states are produced by a standard laser source, thus reducing the resource needed.
+The $r_{jk}$ terms are found by the square root of the ratios of output intensity at the $k$th port to the input intensity at the $j$th port.
+The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha_1}\ket{\alpha_2}$ created by splitting a single coherent state on a 50-50 beamsplitter, and then imparting a relative phase, $\phi$, between them.
+The states $\ket{\alpha_1}$ and $\ket{\alpha_2}$ are input into port 1, and $j$ respectively.
+The output intensity at the $j$th port is
+\begin{align}
+I_k=I(r_{1k}^2+r_{jk}^2+2 r_{1k}r_{kj}\cos(\phi+\theta_{jk})) \ ,
+\end{align}
+where $\theta_{jk}=0$ for $k=1$.
+By scanning the phase shift $\phi$ and then locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$.
+An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$.
+In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure.
+whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.
 

### 2017-04-20 paper.tex
Added stub for Peter.
Started section on time-bin qubits.

@@
 \subsubsection{Time-bins}
+Time-bin qubits is quantum information that is encoded on the time-of-arrival of single photons.
+It was first conceived for a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}.
+If the photon passes through the shorter (longer) path, then it will arrive at the output port in an ``early" (``late") time bin.
+Thus, photon will exit the interferometer in a state that is a superposition of these two states.
+Owing to difficulties in implementing qubit operations in this basis, it was at that time mostly used for demonstrating quantum communication over long distance \cite{bib:Thew02,bib:Marcikic04}.
+With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operations, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}.
+At the same time, an ultrafast measurement technique for recovering time-bin qubits was also demonstrated \cite{bib:Donohue2013}.
 
@@
 \subsection{State preparation}
-\sihui{Cat state--Schoelkopf group}
 
 \subsubsection{Single-photons}
+
+\sihui{ SPDC, quantum-dot micropillar sources}
 
@@
 \comment{Discuss fibre-loop architecture}
+
+\sihui{Peter to fill this in}
+\cite{bib:Motes14}
 

### 2017-04-20 paper.tex
Added more to time-bin section.

@@
 It was first conceived for a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}.
-If the photon passes through the shorter (longer) path, then it will arrive at the output port in an ``early" (``late") time bin.
+If the photon passes through the shorter (longer) path, then it will arrive at the output port in an ``early" (``late") time bin labelled $\ket{e}$ ($\ket{\ell}$).
 Thus, photon will exit the interferometer in a state that is a superposition of these two states.
@@
 With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operations, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}.
+These gates form an universal set for quantum computing.
 At the same time, an ultrafast measurement technique for recovering time-bin qubits was also demonstrated \cite{bib:Donohue2013}.
+
+In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin qubits have a polarization register which is used to toggle between the mode in which qubits are stored and transmitted, {\it i.e.} the ``register" mode, and the mode in which qubits are manipulated, {\it i.e.} the ``processing" mode using a polarization rotation.
+Other operations needed are a displacement operation moves a time-bin qubit in the processing polarization in time relative to other qubits, a partial polarization rotation between the register and processing polarizations to couple them, and a photon number measurement in a bin.
+The polarization rotation and polarization coupling operations were implemented using a fast integrated optical switch based on polarization-sensitive cross-phase modulation with a switching time of less than 10 ps.
+The displacement was implemented using a calcite crystal of a size that is of a path-length difference equal to an integer multiple of the time-bin separation.
+Using these operations and post-selection using a single-photon detectors, the authors were able to perform a heralded CPHASE gate \cite{bib:KLM01}.
 

### 2017-04-23 paper.tex
Added to time-bin encoding.

@@
 
+In Donohue {\it et al.} \cite{bib:Donohue2013}, time bins were converted into frequency bins using a nonlinear optical process known as sum-frequency generation (SFG) by pumping them on a crystal with a laser beam.
+The waveforms of the input photons and the pump beam are chirped in opposite directions in frequency, so that the output is a set of two peaks separated in frequency by an amount proportional to the time separation of the time bins.
+The output can then be measured with detectors that are slow compared to this separation.
+This is unlike conventional time-bin measurements which involves sending a time-bin state through an unbalanced Mach-Zedner interferometer matched to a bin separation to produce three output pulses that are separated by the time delay, and then having to resolve the middle pulse in time.
+
+Apart from these promising advances in produce time-bin qubit gates and ultrafast time-bin measurements, scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}.
+This is discussed in more detail in Section \ref{sec:timebins}.
+
 %\subsection{Continuous-variables}
@@
 
-\subsubsection{Time-bins}
+\subsubsection{Time-bins}\label{sec:timebins}
 

### 2017-04-25 paper.tex
Started section on single photon sources.

@@
 
-\sihui{ SPDC, quantum-dot micropillar sources}
+Sources of single photons for applications of quantum information processing are 
+separated into two main categories \cite{bib:Kok05}; those produced by spontaneous 
+parametric down-conversion (SPDC), and those by solid-state emitters in a cavity. 
+Both categories have seen some leaps recently in their record production of numbers 
+of single photons while preserving good qualities in their single photons. To 
+date, SPDC has been able to produce up to ten entangled photons 
+\cite{bib:WangChen16,bib:Chen17}, and five-photon quantum interference has been 
+reported using a quantum dot emitter in a microcavity \cite{bib:WangHe16}.
+
+In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ is pumped with a strong 
+laser and with a small probability, the pump beam is absorbed by the crystal to 
+produce two beams of lower energy known as the signal and idler beams. Owing to 
+conservation of energy and momentum, the two beams have spatio-temporal 
+correlations that can be engineered to produce twin-beam states which have 
+perfectly correlated photon numbers. If a single photon were to be detected in one 
+of the beams, and then it is certain that the other beam would be in the state of a 
+single photon. Some commonly used nonlinear crystals for SPDC are beta barium 
+borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled 
+potassium titanyl phosphate (PPKTP). Recently, techniques using bismuth triborate 
+(BiBO) have improved to the extent of becoming one of the record-holders of single-
+photon production.
+\cite{bib:WangChen16}.
 

### 2017-04-26 paper.tex
Added to single-photon source section.

@@
 (BiBO) have improved to the extent of becoming one of the record-holders of single-
-photon production.
-\cite{bib:WangChen16}.
+photon production \cite{bib:WangChen16}.
+
+\sihui{ Discuss architectures for producing entangled photon states like GHZ, maybe here or in a different subsection.}
+
+Solid-state single photon sources come from semiconducting nanostructures and 
+nitrogen valencies (NV) centers in diamond. Both types are versatile and efficient 
+sources of single photons, however the photons they produce have suffered from lack 
+of indistinguishability that is necessary for quantum information processing.
+Recent developments in the former show promising developments. Notably, a scheme has 
+been developed using laser pulses to excite an electronic resonance of a 
+semiconducting quantum dot to trigger the emission of single photons 
+\cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,
+bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,bib:Ding16,bib:237403,bib:Sweeney14}. Then by embedding the quantum dot in a 
+micropillar cavity that has the same resonant frequency as the dot, the scheme
+exploits the Purcell effect to achieve higher single-photon production efficiency. 
+Such resonant excitation of quantum dots overcome the homogenous broadening of the 
+excited state that causes degradation of photon purity and hence 
+indistinguisnability.
 

### 2017-04-27 paper.tex
Updated single photon.

--- 2017-04-25 paper.tex
@@
 (BiBO) have improved to the extent of becoming one of the record-holders of single-
-photon production.
+photon production \cite{bib:WangChen16}.
+
+\sihui{ Discuss architectures for producing entangled photon states like GHZ, maybe here or in a different subsection.}
+
+Solid-state single photon sources come from semiconducting nanostructures and 
+nitrogen valencies (NV) centers in diamond. Both types are versatile and efficient 
+sources of single photons, however, the photons they produce have suffered from 
+lack of indistinguishability that is necessary for quantum information processing.
+Recent developments in the former show promising developments. Notably, much 
+progress has been made using resonant excitation of quantum dots. Laser pulses are 
+used to excite their electronic resonance and trigger the emission of single 
+photons \cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,
+bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
+bib:237403,bib:Sweeney14}. An architecture that embeds the quantum dot in a 
+micropillar cavity with the same resonant frequency as the dot exploits the 
+Purcell effect to achieve higher single-photon production efficiency 
+†\cite{bib:Ding16,bib:213601}. 
+Such resonant excitation of quantum dots overcome the homogenous broadening of the 
+excited state that causes degradation of photon purity and hence improves
+indistinguishability. Using a time-bin loop-based architecture \cite{bib:Motes14} 
+on a stream of single photons produced by such a quantum dot, the same group was 
+able to demonstrate quantum interference between five indistinguishable photons 
 \cite{bib:WangChen16}.

### 2017-05-04 paper.tex
Added comments in single-photon section.
Latest updates. Includes all sections Peter added. Added subsection on LOQC. Added a missing reference for large optical circuits towards the beginning of the paper.

--- 2017-04-25 paper.tex
@@
 \email[]{sihui\_tan@sutd.edu.sg}
-\affiliation{Singapore University of Technology and Design, 8 Somapah Road, Singapore}
-
+\affiliation{Singapore University of Technology and Design, Singapore University of Technology and Design, 8 Somapah Rd, Singapore 487372}
+\affiliation{Centre for 
+Quantum Technologies, National University of Singapore, Block S15, 3 Science Drive 2, Singapore 117543, Singapore}
 \author{Peter P. Rohde}
@@
 
-\sihui{Si-Hui can colour code things she adds like this}
-
-\peter{And Peter can do it like this}
-
-\comment{Let's add comments and questions like this}
+\comment{To do}
 
@@
 \section{Mathematical background}
-\comment{Mathematical representation for LO networks, and very basic background on quantum optics}\\
 
 A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer.
-The creation and annihilation operators satisfy the bosonic comutator relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.
-A similar commutator relationship can be  written up when more degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present.
+The creation and annihilation operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.
+A similar commutation relationship can be written when additional degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present.
 When multiple photons are present, they experience quantum interference when all quantum labels are the same.
@@
 where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in SU(d)$.
-All such transformation can be expressed as sequence of beamsplitters and waveplates \cite{bib:Reck1994}.
-In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons into a sequence of beamsplitters and internal transformations.
+All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994}.
+In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons as a sequence of beamsplitters and internal transformations.
 Toolkits using group theory are being developed to deal with partial distinguishabilities among interfering photons \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}.
-Others use
-quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}. \sihui{Experimental implementation [Walmsley, Jennewein]}
+Others use quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}.
+\sihui{Experimental implementation [Walmsley, Jennewein]}
 
 \section{Optical encoding of quantum information on single-photons}
+
+Using quantum states of light, there are a multitude of approaches to encoding quantum information. Beginning with a logical qubit,
+\begin{align}
+\ket\psi_L = \alpha \ket{0}_L + \beta\ket{1}_L,
+\end{align}
+we now discuss the most prominent such encodings, which have been widely employed. We will specifically focus on single-photon encodings, as opposed to, for example, continuous variable encodings.
+
+These encodings are all isomorphic to one another, but nonetheless, because they are represented using entirely different physical systems, they each exhibit their own unique advantages and disadvantages, and methods by which to implement operations upon them.
 
@@
 
+In polarisation encoding, the polarisation of a single photon in a single spatial mode encodes a logical qubit. Specifically, we represent the logical qubit as,
+\begin{align}
+\ket\psi_L = \alpha\ket{H} + \beta\ket{V},	
+\end{align}
+where $H$ ($V$) denotes a horizontally (vertically) polarised single photon.
+
+Polarisation encoding has the elegance that the most common optical error mechanisms, such as loss or path-length mismatch, affect the two logical basis states equally.
+Furthermore, single-qubit operations may be directly implemented using wave-plates, which implement a rotation in polarisation space.
+Relevant to the preparation of large entangled states, such as cluster states, polarising beamsplitters can be employed to perform non-deterministic Bell state projections.
+
+When physically constructing protocols based on polarisation-encoding, for obvious reasons it is extremely important that optical components be polarisation-preserving.
+Not doing so would obviously corrupt the logical state.
+Some waveguide technologies, for example, exhibit different refractive indices for the two polarisations.
+
 \subsubsection{Dual-rail}
 
+In dual-rail encoding, a single photon encodes a logical qubit as a superposition across two spatial modes,
+\begin{align}
+\ket\psi_L = \alpha\ket{1,0} + \beta\ket{0,1},
+\end{align}
+where $\ket{i,j}$ is a two-mode state with $i$ ($j$) photons in the first (second) spatial mode.
+Using this encoding, phase-shifters and beamsplitters between the two spatial modes implement arbitrary single-qubit operations.
+Converting between polarisation- and dual-rail-encoding is trivial using polarising beamsplitters, which separate horizontal and vertical components into distinct spatial modes, or vice-versa.
+
+Unfortunately, because the two basis states evolve via independent paths, our dual-rail qubits are susceptible to path-length-mismatch, a problem that does not affect polarisation encoding.
+Nonetheless, there are certain advantages to using two paths as opposed to one as is the case in single-rail encoding where the presence or absence of a photon denotes the logical bit.
+The loss of a photon in a dual-rail qubit is easily noted by its absence, whereas in a single-rail encoding, it would have been confused for one of the states.
+Moreover, a no-go result precludes universal quantum computation using just linear optics without the use of measurements in a single-rail encoding \cite{bib:Wu13}, thus making dual-rail encoding a more attractive alternative.
+
 \subsubsection{Time-bins}
-Time-bin qubits is quantum information that is encoded on the time-of-arrival of single photons.
-It was first conceived for a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}.
-If the photon passes through the shorter (longer) path, then it will arrive at the output port in an ``early" (``late") time bin labelled $\ket{e}$ ($\ket{\ell}$).
-Thus, photon will exit the interferometer in a state that is a superposition of these two states.
-Owing to difficulties in implementing qubit operations in this basis, it was at that time mostly used for demonstrating quantum communication over long distance \cite{bib:Thew02,bib:Marcikic04}.
-With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operations, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}.
+
+Time-bin qubits encode quantum information into the time-of-arrival of single photons, which have fixed polarisation and reside in a single spatial mode.
+Effectively, we discretise the direction of propagation of photons into discrete bins, which are treated as orthogonal basis states.
+Specifically, we are employing the encoding,
+\begin{align}
+\ket\psi_L = \alpha\ket{1}_{t}\ket{0}_{t+\tau} + \beta \ket{0}_{t}\ket{1}_{t+\tau},
+\end{align}
+where $\ket{0}_t$ ($\ket{1}_t$) denotes the vacuum (single-photon) state with arrival time $t$.
+Here $\tau$ is the time-bin separation, which must be sufficiently large that the temporal envelopes of neighbouring photons do not overlap, thereby ensuring orthogonality of the logical basis states.
+
+This encoding is particularly resource-savvy, since a single spatial mode (e.g length of optical fibre) can encapsulate many time-bin qubits as a `time-bin-train'.
+The amount of quantum information that can be encoded into the train is limited only by its physical length.
+
+Unlike polarisation or dual-rail encoding, time-bin encoding does not lend itself to `native' single-qubit operations.
+Rather, fast switching can be used to spatially separate neighbouring time-bins, implement a beamsplitter operation between them, before converting back to time-bin encoding.
+
+Time-bin encoding was first conceived via a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}.
+If the photon passes through the shorter (longer) path, it will arrive at the output port in an `early' (`later') time-bin labelled $\ket{e}$ ($\ket{\ell}$).
+Thus, the photon will exit the interferometer in a state that is a superposition of these two states.
+Owing to difficulties in implementing qubit operations in this basis, it was at the time mostly used for demonstrating quantum communication over long distances \cite{bib:Thew02,bib:Marcikic04}.
+With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operation, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}.
 These gates form an universal set for quantum computing.
@@
 
-In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin qubits have a polarization register which is used to toggle between the mode in which qubits are stored and transmitted, {\it i.e.} the ``register" mode, and the mode in which qubits are manipulated, {\it i.e.} the ``processing" mode using a polarization rotation.
-Other operations needed are a displacement operation moves a time-bin qubit in the processing polarization in time relative to other qubits, a partial polarization rotation between the register and processing polarizations to couple them, and a photon number measurement in a bin.
-The polarization rotation and polarization coupling operations were implemented using a fast integrated optical switch based on polarization-sensitive cross-phase modulation with a switching time of less than 10 ps.
+In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin qubits have a polarization register which is used to toggle between the mode in which qubits are stored and transmitted, {\it i.e.} the `register' mode, and the mode in which qubits are manipulated, {\it i.e.} the `processing' mode using a polarization rotation.
+Other operations needed are a displacement operation, that moves a time-bin qubit in the processing polarization in time relative to other qubits, a partial polarization rotation between the register and processing polarizations to couple them, and a photon number measurement in a bin.
+The polarization rotation and polarization coupling operations were implemented using a fast integrated optical switch based on polarization-sensitive cross-phase modulation with a switching time of less than 10ps.
 The displacement was implemented using a calcite crystal of a size that is of a path-length difference equal to an integer multiple of the time-bin separation.
@@
 
-In Donohue {\it et al.} \cite{bib:Donohue2013}, time bins were converted into frequency bins using a nonlinear optical process known as sum-frequency generation (SFG) by pumping them on a crystal with a laser beam.
+In Donohue {\it et al.} \cite{bib:Donohue2013}, time-bins were converted into frequency bins using a nonlinear optical process known as sum-frequency generation (SFG) by pumping them on a crystal with a laser beam.
 The waveforms of the input photons and the pump beam are chirped in opposite directions in frequency, so that the output is a set of two peaks separated in frequency by an amount proportional to the time separation of the time bins.
 The output can then be measured with detectors that are slow compared to this separation.
-This is unlike conventional time-bin measurements which involves sending a time-bin state through an unbalanced Mach-Zedner interferometer matched to a bin separation to produce three output pulses that are separated by the time delay, and then having to resolve the middle pulse in time.
+This is unlike conventional time-bin measurements which involve sending a time-bin state through an unbalanced Mach-Zedner interferometer matched to the time-bin separation to produce three output pulses that are separated by the time delay, and then having to resolve the middle pulse in time.
 
-Apart from these promising advances in produce time-bin qubit gates and ultrafast time-bin measurements, scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}.
+Apart from these promising advances in implementing time-bin qubit gates and ultrafast time-bin measurements, scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}.
 This is discussed in more detail in Section \ref{sec:timebins}.
@@
 If a non-unitary transformation is desired, it can be embedded within a unitary matrix with larger dimensions.
-An algorithm for expressing an arbitrary unitary matrix {\it exactly} in terms of a sequence of $\mathcal{O}(n^2)$ beamsplitters and phase-shifters exists \cite{bib:Reck1994}.
-Alternatively, Mach-Zedner interferometer can also be used as building blocks instead of beamsplitters and phase shifters \cite{bib:Reck1994, bib:Englert2001}.
-Later, it has been shown that any nontrivial beam splitter, that does more than swapping modes around or add phases to them, is universal for linear optics \cite{bib:Bouland2014}.
-However, they do not provide a construction for arbitrary unitaries.
+An algorithm for expressing an arbitrary unitary matrix {\it exactly} in terms of a sequence of beamsplitters and phase-shifters was described by Reck \emph{et al.} \cite{bib:Reck1994}.
+This decomposition requires $\mathcal{O}(n^2)$ linear optical elements, and the algorithm for finding the decomposition has polynomial runtime.
+Thus, such decompositions can always be determined and implemented efficiently.
+The layout for the original Reck \emph{et al.} decomposition is shown in Fig.~\ref{fig:Reck}.
+However, since then a multitude of alternate decompositions have been found.
+A notable downside of the original decomposition is that different photons experience different circuit depth, i.e pass through different numbers of optical elements, resulting in asymmetry in losses and the accumulation of errors.
+
+\begin{figure}[!htb]
+\includegraphics[width=\columnwidth]{reck}
+\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
+\end{figure}
+
+Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Reck1994, bib:Englert2001}.
+Later, it has been shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
+However, they do not provide an explicit construction for arbitrary unitaries.
 
 If the linear optical transformations can be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
-Their approach reduces the required number of beamsplitters but increases the total number of optical elements needed increases by a factor of 2.
+Their approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.
 
@@
 
-In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase shifters is known once it is built.
+In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built.
 However, owing to manufacturing imperfections, a precise characterization of these devices is still needed post-production.
-One of the ways, this can be done is via a quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11} .
-However, quantum process tomography is an expensive method in terms of number of measurements required to characterize the network, and it becomes impractical for large optical networks which can now be as large as 900 modes (check citations for number of modes).
-Alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.
+One approach for achieving this is via quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
+However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterize the network, with exponential overhead, becoming impractical for large optical networks which can contain hundreds of modes using present-day technology \cite{bib:Harris16}.
+However, alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.
 
-Generally, the unitary matrix of the $d\times d$ linear optical device are complex numbers $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$.
-The scheme in \cite{bib:Laing12} relies on injecting one-photon and two-photon states into the linear optical network with correlated photon detection.
-First, they note some equivalencies: two unitaries $U$ and $U'$ are equivalent if there exist two diagonal unitary matrices $D_1^U$ and $D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are regarded as unknown and trivial phases on the input and output ports of the network, to which the one-photon and two-photon data are insensitive to.
-This reduces the first row and first column elements to real numbers, i.e.
+Generally, the unitary matrices of $d\times d$ linear optical devices are complex $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$.
+The scheme in \cite{bib:Laing12} relies on injecting one- and two-photon states into the network with correlated photon detection.
+First, they note some equivalencies: two unitaries $U$ and $U'$ are equivalent if there exist two diagonal unitary matrices $D_1^U$ and $D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are regarded as unknown and trivial phases on the input and output ports of the network, to which the one- and two-photon data are insensitive to.
+This reduces the first row and column elements to real numbers, i.e.
 $\theta_{1j}=\theta_{i1}=0$.
-Second, the photon statistics remain unchanged under the complex conjugation of $U$.
+Second, the photo-statistics remain invariant under complex conjugation by $U$.
 Thus, the imaginary part of $M_{2,2}$ must be non-negative.
-Then assuming that the first two rows and columns are non-vanishing, and that there is no total loss in the interferometer, the matrix to be recovered is
+Then, assuming the first two rows and columns are non-vanishing, and there is no total loss in the interferometer, the matrix to be recovered is
 \begin{align}
@@
 \end{align}
-In the paper, they showed that it is possible to write the paramaters $r_{ij}$, and $\theta_{ij}$ for $i,j\geq 2$ in terms of the $2m-1$ real parameters of the first column and row, and the visibility of two-photon inputs.
+They showed it is possible to write the parameters $r_{ij}$, and $\theta_{ij}$ for $i,j\geq 2$ in terms of the $2m-1$ real parameters of the first column and row, and the visibility of two-photon inputs.
 The remaining $2m-1$ real parameters can be found via one-photon
 transmissions.
-An increased accuracy of the characterization is possible by estimating and correcting systematic errors that arise due to mode mismatch \cite{Dhand16}.
+An increased accuracy in the characterization is possible by estimating and correcting systematic errors that arise due to mode mismatch \cite{Dhand16}.
 Others have used numerical methods to find the closest parameters that yield the observed visibilities \cite{bib:Spagnolo16,bib:Tillmann16}.
 
-Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead \cite{bib:Rahimi-Keshari13,bib:Heilmann15}.
-Such states are produced by a standard laser source, thus reducing the resource needed.
-The $r_{jk}$ terms are found by the square root of the ratios of output intensity at the $k$th port to the input intensity at the $j$th port.
+Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead of Fock states \cite{bib:Rahimi-Keshari13,bib:Heilmann15}.
+Such states are produced by a standard laser source, thus reducing experimental resources.
+The $r_{jk}$ terms are found by the square root of the ratios of output intensities at the $k$th port to the input intensity at the $j$th port.
 The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha_1}\ket{\alpha_2}$ created by splitting a single coherent state on a 50-50 beamsplitter, and then imparting a relative phase, $\phi$, between them.
 The states $\ket{\alpha_1}$ and $\ket{\alpha_2}$ are input into port 1, and $j$ respectively.
-The output intensity at the $j$th port is
+The output intensity at the $j$th port is then
 \begin{align}
@@
 where $\theta_{jk}=0$ for $k=1$.
-By scanning the phase shift $\phi$ and then locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$.
-An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$.
-In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure.
-whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.
+By scanning the phase shift $\phi$ and locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$.
+An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase-shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$.
+In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure, whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.
 
@@
 
+Significant progress has been made in the experimental realisation of linear optics protocols, and have become standard and widespread. We now discuss some of these advances.
+
 \subsection{State preparation}
 
-\subsubsection{Single-photons}
+The photonic states that are most commonly employed in linear optics protocols can be divided into Fock states (e.g single-photon), and entangled states, such as EPR, GHZ and cluster states.
+We will consider advances in each of these.
 
-Sources of single photons for applications of quantum information processing are 
-separated into two main categories \cite{bib:Kok05}; those produced by spontaneous 
-parametric down-conversion (SPDC), and those by solid-state emitters in a cavity. 
-Both categories have seen some leaps recently in their record production of numbers 
-of single photons while preserving good qualities in their single photons. To 
-date, SPDC has been able to produce up to ten entangled photons 
-\cite{bib:WangChen16,bib:Chen17}, and five-photon quantum interference has been 
-reported using a quantum dot emitter in a microcavity \cite{bib:WangHe16}.
+\subsubsection{Single-photons}\label{sec:singlephotons}
 
-In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ is pumped with a strong 
-laser and with a small probability, the pump beam is absorbed by the crystal to 
-produce two beams of lower energy known as the signal and idler beams. Owing to 
-conservation of energy and momentum, the two beams have spatio-temporal 
-correlations that can be engineered to produce twin-beam states which have 
-perfectly correlated photon numbers. If a single photon were to be detected in one 
-of the beams, and then it is certain that the other beam would be in the state of a 
-single photon. Some commonly used nonlinear crystals for SPDC are beta barium 
-borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled 
-potassium titanyl phosphate (PPKTP). Recently, techniques using bismuth triborate 
-(BiBO) have improved to the extent of becoming one of the record-holders of single-
-photon production.
-\cite{bib:WangChen16}.
+Sources of single photons for applications in quantum information processing can be separated into two main categories: those produced by spontaneous parametric down-conversion (SPDC), and those by solid-state emitters in a cavity.
+Both categories have seen major development recently in photon-number, with high fidelities.
+To-date, SPDC has been able to produce up to ten entangled photons \cite{bib:WangChen16,bib:Chen17}, and five-photon quantum interference has been reported using a quantum dot emitter in a microcavity \cite{bib:WangHe16}.
 
-\subsubsection{Bell pairs}
+In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ non-linearity is pumped with a strong coherent state (i.e laser source) and with a small probability, the pump beam is absorbed by the crystal to produce two beams of lower energy known as the signal and idler.
+Owing to conservation of energy and momentum, the two beams have spatio-temporal correlations that can be engineered to produce twin-beam states with perfect  photon number correlation, of the form
+\begin{align}
+\ket\psi_\mathrm{SPDC} = \sqrt{1-\chi^2} \sum_{n=0}^\infty \chi^n \ket{n,n},	
+\end{align}
+where $\chi$ is the squeezing parameter. If a single photon were to be detected in one of the modes, it is certain that the other mode would similarly contain a single photon.
 
-\subsubsection{Coherent states}
+Some commonly used nonlinear crystals for SPDC are beta barium borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled  potassium titanyl phosphate (PPKTP).
+Recently, techniques using bismuth triborate (BiBO) have improved to the extent of becoming one of the record-holders in single-photon production \cite{bib:WangChen16}.
 
-\subsubsection{Squeezed states}
+Solid-state single photon sources come from semiconducting nanostructures and nitrogen valencies (NV) centers in diamond.
+Both types are versatile and efficient sources of single photons, however, the photons they produce have suffered from the lack of indistinguishability that is necessary for typical quantum information processing applications.
+Recent developments in the former have been very promising.
+Notably, much progress has been made using resonant excitation of quantum dots.
+Here, laser pulses are used to excite their electronic resonance and trigger the emission of single photons \cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
+bib:237403,bib:Sweeney14}.
+An architecture that embeds the quantum dot in a micropillar cavity with the same resonant frequency as the dot exploits the Purcell effect to achieve higher single-photon production efficiency€ \cite{bib:Ding16,bib:213601}.
+Such resonant excitation of quantum dots overcomes the homogenous broadening of the excited state that causes degradation of photon purity and improving indistinguishability.
+Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of single photons produced by such a quantum dot, the same group was able to demonstrate quantum interference between five indistinguishable photons \cite{bib:WangChen16}.
+
+\subsubsection{Einstein-Podolsky-Rosen (EPR) pairs}
+
+An EPR pair, or Bell pair, is one of the four states,
+\begin{align}
+\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \\
+\ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
+\end{align}
+which are all maximally entangled and locally equivalent to one another.
+These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing \cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
+In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.} successfully prepared only under certain measurement outcomes of auxiliary modes.
+Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}.
+They are often used as a building block for preparing other multipartite entangled states.
+
+\subsubsection{Greenberger-Horne-Zeilinger (GHZ) states}
+
+GHZ states form a class of entangled quantum states on multiple subsystems with at least three parties \cite{bib:GHZ89}. For qubit encodings with $n$ subsystems, a GHZ state is of the form
+\begin{align}
+\ket{\Psi_{n}^{\rm (GHZ)}}=\frac{\ket{0}^{\otimes n}+\ket{1}^{\otimes n}}{\sqrt{2}} \ .
+\end{align}
+These states are also non-local, and have been used extensively in experimental test for non-locality \cite{bib:JW00,bib:Zhang15}.
+This has been a subject matter covered in detail by another review \cite{bib:JW12}.
+
+\subsubsection{Cluster states}\label{section:cluster}
+
+Cluster states form another class of multiparty entangled states, and were conceived in the context of arrays of qubits with an Ising-type interaction \cite{bib:Briegel01}.
+
+These states can be represented as a graph, in which vertices are qubits initialized into the superposition state $\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, with CPHASE operation applied between edges, as shown in Fig.~\ref{fig:cluster}.
+For this reason, such states are also referred to as graph states.
+The CPHASE operations generate entanglement between the qubits, and because they commute, are independent of ordering.
+Cluster states are a resource state for a model of quantum computation known as measurement-based quantum computation (MBQC).
+Here, having such a state as a resource enables universal quantum computation using only single-qubit measurements \cite{bib:Raussendorf03}.
+Therefore, the preparation of such states is highly valuable, generating much interest in their efficient preparation.
+
+\begin{figure}[!htb]
+\includegraphics[width=0.6\columnwidth]{cluster_state}
+\caption{The representation of cluster states as a graph.
+Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on CPHASE gates, the ordering of which is irrelevant.} \label{fig:cluster}
+\end{figure}
+
+Unfortunately, implementing CPHASE gates using linear optics is complicated and highly non-deterministic.
+A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell basis.
+These operations fuse smaller cluster states, represented using polarisation encoding, into larger ones, consuming one (type-I fusion) or two (type-II fusion) photons in the process.
+These operations are shown in Fig.~\ref{fig:fusion}.
+Although these operations are non-deterministic with a success probability of $1/2$, they require only a single beamsplitter, already a major improvement over directly implementing CPHASE gates.
+Furthermore, unlike CPHASE gates, fusion operations require only high Hong-Ou-Mandel visibility, rather than the Mach-Zehnder stability required within existing CPHASE gate implementations, a major experimental simplification.
+
+Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing CPHASE gates.
+
+\begin{figure}[!htb]
+\includegraphics[width=0.7\columnwidth]{fusion}
+\caption{Fusion gates for joining smaller cluster states into larger ones.
+Both require only a single polarising beamsplitter, and waveplates.
+The type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, creating an edge between the remaining graphs.
+The type-I gate consumes one fewer photon, but requires number-resolved detection on the detected mode.
+The type-II gate requires only on/off photodetection, but consumes an additional photon.
+Thus, the type-I gate can be employed to fuse two Bell pairs into a 3-qubit cluster state, whereas the type-II gate will only grow clusters when beginning with at least 3 qubits per cluster.} \label{fig:fusion}
+\end{figure}
 
@@
 
+Numerous experimental implementations of various linear optics protocols have been demonstrated, using a variety of architectures.
+The main contenders considered to date are: bulk-optics; waveguides; and time-bin encoding.
+
 \subsubsection{Bulk-optics}
+
+The early implementations of linear optics protocols relied on bulk-optics implementations, in which a circuit is decomposed into a discrete arrangement of optical components, specifically beamsplitters and phase-shifters.
+This corresponds to a direct implementation of the Reck \emph{et al.} decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate decompositions.
+
+Although this approach is effective and conceptually straightforward, it is highly impractical for large interferometers.
+For example, the implementation of a 100-mode interferometer requires on the order of 10,000 discrete optical elements, which must all be simultaneously aligned with interferometric stability, a highly experimentally challenging problem, not to mention incredibly physically large.
 
@@
 
+Alternately, integrated waveguide devices can be employed to implement identical decompositions by etching the modes into paths in an optical chip, where evanescent coupling between closely neighbouring modes implements beamsplitter operations.
+Such devices are extremely compact, allowing the miniaturisation of large numbers of optical elements.
+Importantly, such devices are extremely optically stable, mitigating the need for any kind of dynamic stabilisation
+
 \subsubsection{Time-bins}\label{sec:timebins}
 
-\comment{Discuss fibre-loop architecture}
+Using time-bin encoding of optical qubits, the obvious question is how to perform operations upon them.
+In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains, shown in Fig.~\ref{fig:FL_arch}.
 
-\sihui{Peter to fill this in}
-\cite{bib:Motes14}
+\begin{figure}[!htb]
+\includegraphics[width=\columnwidth]{full_architecture}
+\caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train.
+The source prepares the temporally encoded pulse-train, with time-bin separation $\tau$.
+The pulse-train then enters a dual-loop configuration.
+The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the number of optical modes).
+The architecture is controlled via three dynamically controlled beamsplitters.
+The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, keep it within the outer loop for the required duration, and then couple out of the outer loop, yielding the transformed pulse-train.
+The central beamsplitter must be able to implement arbitrary classically-controlled beamsplitter operations.} \label{fig:FL_arch}
+\end{figure}
 
-\subsection{Measurement}
+The architecture is frugal in its use of optical components, requiring only three dynamic beamsplitters, and several lengths of fibre.
+The beauty of this architecture is that the experimental requirements do not increase with the number of optical modes.
+The only parameter that scales with the number of optical modes is the outer loop, which must be at least long enough to house the entire time-bin-encoded pulse-train.
+Note, however, that the central beamsplitter must be controllable at sub-$\tau$ time-scales, so as to enable each temporal mode to be addressed individually, which is technically challenging.
 
-\subsubsection{Photodetection}
+The workings of the scheme can be thought of as follows: the inner loop allows arbitrary beamsplitter operations between neighbouring time-bins; the outer loop does nothing interferometric, but rather enables the pulse-train to undergo as many applications of the inner loops as necessary.
+It then follows that this scheme is universal for linear optics, as a sufficient number of beamsplitter operations between neighbouring modes enables universal decompositions, using for example, the Reck \emph{et al.} decomposition described earlier.
 
-\comment{Discuss number-resolved and bucket detectors, multiplexed detection, APDs, current micropillar detectors}
+As a simple example of how such time-bin encoding maps to other encodings, in Fig.~\ref{fig:PBS_TB} we show the isomorphism between the polarising beamsplitter operation and a pairwise temporal beamsplitter operation.
+This implies a direct mapping for implementing cluster state preparation within the time-bin scheme.
 
-\subsubsection{Homodyning}
+\begin{figure}[!htb]
+\includegraphics[width=0.7\columnwidth]{PBS_TB}
+\caption{Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train.
+The PBS completely reflects (transmits) the vertical (horizontal) polarisations.
+The evolution of the four logical basis states, and their respective outputs, are shown explicitly.
+Writing out this PBS transformation in matrix form yields a permutation.
+Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.} \label{fig:PBS_TB}
+\end{figure}
+
+The above description applies to passive linear optics, which is sufficient for protocols such as {\sc BosonSampling}, but insufficient for universal optical quantum computation, which requires the addition of ancillary states, and measurement with fast-feedforward.
+To address this, it was shown in \cite{Rohde} that by dynamically preparing ancillary pulse-trains (from the already-existing source), classically controlled by time-resolved measurements at the output, and changing the switching sequence, we can effectively couple in and out arbitrary subsets of the optical modes, enabling partial measurements to be implemented.
+
+\subsection{Photodetection}
+
+Broadly speaking, there are two main classes of photodetectors: non-photon-number-resolving (also referred to as bucket, or on/off) detectors, and photon-number-resolving (PNR) detectors.
+As the names suggest, non-PNR detectors only detect the presence or absence of photons in an incident beam, while PNR detectors are able to measure its number of photons.
+The outcomes of a PNR detector are described by the measurement projectors,
+\begin{align}
+\hat\Pi_n &= \ket{n}\bra{n}, \ n=0,1,\ldots \ ,\nonumber \\	
+\end{align}
+while those of the non-photon-number-resolving detectors are given by
+\begin{align}
+\hat\Pi_\text{off} &= \hat\Pi_0, \nonumber \\
+\hat\Pi_\text{on} &= \hat{I} - \hat\Pi_\text{on}\ .
+\end{align}
+
+The dominant challenge facing the experimental implementation of both types of detectors is inefficiency due to loss, which results in higher photon-number being confused as having lower photon-number.
+In some protocols, such as type-II fusion, which relies on coincidence detection, inefficiency is not problematic.
+However, in most applications, including type-I fusion, this is highly problematic as photon-number confusion results in decoherence via projecting onto the wrong photon-number, unknown to the observer.
+Other common problems that plague these detectors are dark counts which add spurious counts from the background, and dead-time which causes the detector to lose counts during a period when it is inactive immediately after the detection of photons.
+
+\subsubsection{Non-PNR Detectors}
+The first type of non-PNR detectors are photomultiplier tubes (PMTs).
+A PMT comprises of a vacuum tube with a photocathode for light absorption.
+The photoelectric effect then releases electrons in the photocathode, and this current is multiplied by a cascade of secondary electron emissions from a series of electrodes.
+This amplified signal can be picked up to indicate the presence of photons.
+
+In applications for quantum information processing, a well-established alternative to PMTs is the avalanche photodiode (APD).
+These are devices made up of semiconductor material, usually silicon, which is structured as a p-n junction and put into Geiger mode operation.
+When a photon is incident on the APD, electrons that are generated undergo an avalanche and the current that is generated can be measured.
+APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in wavelengths in the visible to near-infrared range.
+A downside to using APD is their deadtime.
+This is a period of time following an avalanche during which the avalanche is stopped by a quenching circuit to reset the APD.
+No photons can be detected during the deadtime and contributes to photon loss in an APD.
+
+The last type of non-PNR detectors we discuss is the superconducting nanowire single-photon detector (SNSPD) which have recently become commercially available.
+This detector uses a narrow superconducting wire that is carrying a current operating at just below the critical current density.
+Above this current density, the superconducting wire would undergo a phase change back to its normal resistance which happens when it absorbs an incident photon.
+The current in the wire would then by-pass it to go through the neighboring region which is still superconducting, and therefore at a lower resistance.
+This causes a voltage spike in the neighboring region which can be detected.
+
+\subsubsection{PNR detectors}
+
+Multiple technologies for realizing PNR detectors already exist and have been described by multiple reviews \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few notable examples here.
+One of these is the superconducting transition edge sensor (TES) .
+In TES, a layer of superconducting material is operated at a temperature in its transition between superconducting and normal resistance.
+Any small change in temperature will thus cause a large change in resistance of this layer which can be measured.
+This happens when photons are absorbed, and heats up the superconductor.
+Such detectors can be made so sensitive that the energy of single photons can be detected.
+Another advantage of the TES is its high efficiency which can be made very close to 100\% \cite{bib:Rosenberg05}, and low dark count rates.
+However, they are quite slow, have low maximum counting rates, and are costly to operate due to their very low operating temperatures.
+
+The visible light photon counter (VLPC) is another kind of PNR detector.
+The way VLPC works is in principle very similar to the APD.
+The top layer where the photon impinges is made of silicon, followed by another gain layer that is lightly doped with arsenic (As).
+When a photon is incident on this detector, it creates electrons which are then accelerated into the gain layer and ionize the As impurities, thereby exciting and scattering more electrons.
+An avalanche multiplication ensues just like in an APD.
+However, owing to the presence of the As gain later, the VLPC has a low multiplication noise which results in a single photon absorption event creating an electrical signal that is always of the same magnitude.
+Thus, the output electrical signal is just proportional to the number of detected photons.
+
+Last, we discuss an approach to creating PNR detectors from non-PNR detectors by connecting a bunch of the latter in parallel to one another, and summing the signals at the output to give a combined signal that is proportional to that of just one.
+Such an approach has been demonstrated with SNSPD connected in parallel \cite{bib:Divochiy08}, and APDs connected in an array that can be either on the same semiconductor substrate, or as an interferometric architecture \cite{bib:Afek09,bib:Chrapkiewicz14,bib:Chen17}.
+A drawback of the parallel-SNSPDs is their low quantum efficiency, while the spatially multiplexed APDs suffer from spurious counts known as crosstalk that arises from avalanches triggered by electrons launched from neighboring APDs \cite{bib:Eraerds07,bib:Afek09,bib:Kalashnikov12}.
 
@@
 
-\subsection{Linear optics quantum computation}
+\subsection{Linear optics quantum computation (LOQC)}
+With the advancement in single-photon state preparation, detectors and quantum interferometers, quantum computation using linear optics has become feasible. 
+For universal quantum computation using linear optics and single photon inputs, nonlinear couplings between the different optical modes are needed.
+Photons, being bosons, do not interact with one another like the way fermions do.
+Hence, some careful engineering has to be done in order to achieve this nonlinear coupling between modes.
+Some of the methods used to introduce this nonlinearity include measurements and feedforwarding \cite{bib:KLM01}, and  photon-atom interactions \cite{bib:Brod16}.
+These nonlinearities have been used to construct entangling gates required for (approximate) universality in quantum computation using the circuit model.
+They have also been used to construct entangled graph states, like the cluster states covered in Section \ref{section:cluster}, that are used in MBQC.
+Comprehensive reviews have been written previously to cover this topic \cite{bib:Kok05,bib:JW12}, hence we will skip some basic information to focus on recent advances.
+There are multiple challenges to implementing a scalable, fully-optical quantum computer, and progress has been focused on overcoming these challenges.
+In this section, we will discuss a few of these challenges, and the advances that have been made to overcome them.
+
+\subsubsection{Challenges and Progress in LOQC}
+To date, the quantum computation still requires the use of non-deterministic operations, each of which succeeds with less than unity probability and has to be run many times before a single try succeeds.
+Moreover extra qubits are needed for error correction.
+These requirements put an overhead on the computational cost, in particular at the single photon production stage where a high rate of production of multiple photons is desired for this purpose.
+Second, feed-forwarding requires detectors with very fast response time.
+In feedforward control, one mode is measured and then some operation that depend on the measurement outcome are effected on other modes.
+The readout from the measurement has to happen before the light beam in the target modes passes.
+The last challenge is that of loss.
+Loss can happen anywhere in the linear optical network, but is especially problematic in coupling between different mediums, and upon absorption of a photon in a detector.
+Loss causes computations to fail.
+In the case that this error is detectable, the computation would have to be repeated.
+If not, the computation returns a wrong result.
+
+ Better single-photon sources that have been discussed in Section \ref{sec:singlephotons} are part of the solution to overcoming the above difficulties.
+Following the footsteps of implementing two-qubit gates using multiple degrees of freedom of single photons \cite{bib:Gasparoni04,bib:Zhao05,bib:Okamoto05,bib:Langford05,bib:Kiesel05,bib:Cernoch08,bib:Gao10,bib:Zhou11}, improvement in our theoretical understanding have also led to more efficient designs of circuits \cite{bib:Lanyon09,bib:Zhou11} that enabled the optical implementation of quantum teleportation of the state of a single photon \cite{bib:Wang15}.
+In this way, three-qubit \cite{bib:Lanyon09,bib:Micuda13,bib:Patel16} and four-qubit \cite{bib:Starek16} gates have also been implemented using LOQC.
+
+ If one wishes to avoid the use of non-deterministic quantum gates, the most promising alternative is to use cross-Kerr nonlinearities which have Hamiltonians for two modes labelled by $a$ and $b$ that is proportional to the form
+ \begin{align}
+ a^\dag(\omega)a(\omega)b^\dag(\omega)b(\omega) \ .
+ \end{align}
+
+ Such Kerr nonlinearities are usually implemented on states of light via atom-photon interactions.
+Whether such cross-Kerr nonlinearities on single photon will help LOQC is a subject of debate.
+On one side, the arguments in the negative come down to fundamental noise limits in atom-photon interactions using phenomenological model of a cross-Kerr medium \cite{bib:Shapiro06,bib:Shapiro07,bib:Gea-Banacloche10}.
+On the other hand, an example of a CPHASE gate using photons that counterpropagate through multiple atom-mediated cross-Kerr interaction sites has been constructed, and theoretically shown to work via a first principle treatment of the multimode light field and atomic medium \cite{bib:Brod16}.
+Regardless of who is right in this debate, increments in the strength of Kerr nonlinearities have been achieved in the last five years \cite{bib:Hoi13,bib:Venkataraman13,bib:Feizpour15,bib:Beck16}, and this avenue remains a tantalizing possibility for deterministic quantum gates.
+
+ The advent of integrated photonic circuits has greatly improved the feasibility of LOQC.
+A small chip on silica can contain what used to be spread over large optical tables in bulk optics.
+They also offer greater interferometric stability so that the requisite quantum interference to happen is less affected by changes in path lengths.
+These have been discussed at lengths in another review \cite{bib:Meany15}.
+Recent breakthroughs with programmable circuits have made a single chip reusable for different applications \cite{bib:Metcalf14,bib:Carolan15}.
+Previously, a different chip has to be manufactured every time a new interferometer setup is desired which is a waste of resources and requires a lead time for production.
+
+ Combining these chips with existing higher-efficiency sources and detectors will expand their capabilities.
+Loss can be mitigated by moving all components onto the same chip as the linear optical circuit \cite{bib:Sprengers11, bib:Silverstone14}.
+What remains is to have fast feedforward also on chip.
+This might pose the greatest challenge yet for universal LOQC.
+Only a handful of experiments have been able to implement adaptive feedforward for the purposes of LOQC \cite{bib:Prevedel07,bib:Xiao-Song12,bib:Mikova12,bib:Zhao14}.
+The bottleneck is in the speed of modulation in the feedforward circuitry.
+The successful implementations of feedforward require the use of a delay loop to slow down the target photons so that the modulator has time to catch up.
+
+  Although there has been tremendous progress in pushing for an all-optical universal quantum computer with single photons, it seems likely that an efficient, and fault-tolerant universal quantum computer will require a hybrid system of photonics and something else.
+Nonetheless, linear optics alone is still a fascinating platform for applications and foundational understanding of quantum mechanics.
 
@@
 
-\subsection{Encrypted quantum computation}
+\section{Conclusion}
 
-\section{State of the art}
+Linear optics interferometry has become a leading contender for the implementation of quantum information processing protocols.
+The preparation, manipulation and measurement of photonic quantum information has become mainstream and widely employed, with impressive experimental accuracies.
 
-\comment{Discuss where experiments are at at the moment}
+We have discussed the various ways in which quantum information can be represented photonically, how they can be manipulated and detected, and some of their leading applications.
 
-\section{Conclusion}
+Although there are countless physical architectures for the implementation of quantum information processing, and it is far from certain which will win `the quantum race for supremacy, optics will always find a home as the only contender for applications involving quantum communication.
+For this reason, the future of linear optics interferometry is a bright one, which will find inevitable applicability in the future quantum world.
 
@@
 \begin{acknowledgments}
-P.P.R. is funded by an ARC Future Fellowship (project FT160100397).
+P.P.R.
+is funded by an ARC Future Fellowship (project FT160100397).
+This research was supported in part by the Singapore National Research Foundation under NRF Award No.
+NRF-NRFF2013-01.
+ST acknowldeges support from the Air Force Office of Scientific Research under AOARD grant FA2386-15-1-4082.
+
 \end{acknowledgments}

### 2017-05-04 paper.tex
Quantum metrology
Added blurb about NOON states and Heisenberg-limited interferometry.
Also described somewhat the MORDOR scheme. More ending comments needed.

@@
 
-\subsubsection{Non-PNR Detectors}
+\subsubsection{Non-photon-number-resolving detectors}
 The first type of non-PNR detectors are photomultiplier tubes (PMTs).
@@
 
-\subsubsection{PNR detectors}
+\subsubsection{Photon-number-resolving detectors}
 
@@
 
-  \subsection{Boson-sampling}
+\subsection{Boson-sampling}\label{sec:bosonsampling}
+\sihui{Peter to do this.}
 
 \subsection{Quantum metrology}
+An archetypal task for quantum metrology is the following: Given a Mach-Zedner interferometer, with an unknown phase shift of magnitude $\varphi$ inserted in one of the two paths (see Fig.
+\ref{fig:MZ}), can one deduce $\varphi$ via a judicious use of quantum states and measurements with a higher sensitivity than that of a completely classical interferometer?
+It is well-known that one indeed can, and the standard deviation, $\Delta\varphi$, after $N$ trials using quantum estimation is
+\begin{align}
+\Delta\varphi=\frac{1}{N} \ ,	
+\end{align}
+which gets a $\sqrt{N}$ improvement over classical phase estimation.
+As this sensitivity is also a fundamental limit arising from Heisenberg's uncertainty principle; we cannot measure definitively the phase, it is known as the Heisenberg limit.
+Most famously, a family of entangled states known as NOON states achieve this limit using $N$ photons in a single trial.
+A NOON state is a superposition state in which $N$ photons are either in the first or second path:
+\begin{align}
+\ket{\psi^{\rm (NOON)}_n}=\frac{1}{\sqrt{2}}(\ket{N,0}+\ket{0,N})\ .	
+\end{align}
+ Many reviews have been written for quantum metrology and Heisenberg-limited quantum phase estimation \cite{bib:Giovannetti04,bib:Dowling08,bib:Giovannetti11} so we will not dwell on the history of this application.
+Instead, we will discuss a new paradigm for quantum metrology that has arisen from our understanding of Boson-sampling.
 
-\comment{Discuss NOON states - Heisenberg limited}
+ \begin{figure}[!htb]
+\includegraphics[width=0.7\columnwidth]{phE}
+\caption{A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.} \label{fig:MZ}	
+\end{figure}
 
-\comment{Discuss MORDOR scheme}
+ As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling is readily available, but executes a task that is believed to be hard classically.
+Surprisingly, an entanglement between a large number of spatial modes is possible with single photons in a passive linear optical device.
+This so-called number-path entanglement can be harnessed for quantum metrology without the use of entangled states like the NOON state \cite{bib:Motes15}.
+Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig.
+\ref{fig:MORDOR}).
+By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve
+\begin{align}
+\Delta \varphi=\mathcal{O}\left(\frac{1}{N^{3/2}}\right) \ ,	
+\end{align}
+with just a string of $N$ single photons, one photon per mode, for up to at least $N=25$ modes.
+
+\begin{figure}[!htb]
+\includegraphics[width=\columnwidth]{MORDOR}
+\caption{Architecture of the quantum Fourier transform interferometer for metrology using single-photon states.
+QFT: Quantum Fourier transform circuit, and $\varphi_k=(k-1)\varphi$.
+Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.} \label{fig:MORDOR}
+\end{figure}
 

### 2017-05-09 paper.tex
Changed the sty file to Revip, cleaned up the look of the paper.

@@
-\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscriptaddress]{revtex4}
+%\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscripta
+%ddress]{revtex4}
+\documentclass[times,final]{elsarticle}
+\usepackage{revip}
+\usepackage{framed,multirow}
+\usepackage{hyperref,mathrsfs,amsmath,amssymb,url,latexsym}
 
@@
 \newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
-\usepackage[pdftex]{graphicx}
-\usepackage{mathrsfs}
-\usepackage[colorlinks]{hyperref}
+\usepackage{graphicx}
+
+%\usepackage[colorlinks]{hyperref}
 \usepackage[dvipsnames]{xcolor}
@@
 
+\definecolor{newcolor}{rgb}{.8,.349,.1}
+
+\journal{Reviews in Physics}
+
 \begin{document}
+\verso{Tan and Rohde}
 
-\bibliographystyle{apsrev}
+\begin{frontmatter}
 
@@
 
-\title{The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications}
+\title{The Resurgence of the linear optics interferometer --- recent advances \& applications}
 
@@
 
-\author{Si-Hui Tan}
-\email[]{sihui\_tan@sutd.edu.sg}
-\affiliation{Singapore University of Technology and Design, Singapore University of Technology and Design, 8 Somapah Rd, Singapore 487372}
-\affiliation{Centre for 
-Quantum Technologies, National University of Singapore, Block S15, 3 Science Drive 2, Singapore 117543, Singapore}
-\author{Peter P. Rohde}
-\email[]{dr.rohde@gmail.com}
-\homepage{http://www.peterrohde.org}
-\affiliation{Centre for Quantum Software \& Information (CQSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
+\author[1,2]{Si-Hui \snm{Tan}}
 
-\date{\today}
+\author[3]{Peter P. \snm{Rohde}\corref{cor1}}
+\cortext[cor1]{Corresponding author: dr.rohde@gmail.com ;http://
+www.peterrohde.org}
 
-\frenchspacing
+\address[1]{Singapore University of Technology and Design, Singapore 
+University of Technology and Design, 8 Somapah Rd, Singapore 487372}
+\address[2]{Centre for 
+Quantum Technologies, National University of Singapore, Block S15, 3 
+Science Drive 2, Singapore 117543, Singapore}
+\address[3]{Centre for Quantum Software \& Information (CQSI), Faculty 
+of Engineering \& Information Technology, University of Technology 
+Sydney, NSW 2007, Australia}
 
-%
-% Abstract
-%
+\received{}
+\finalform{}
+\accepted{}
+\availableonline{}
+\communicated{}
 
 \begin{abstract}
+%%%
+Please Type your abstract here. Type your abstract here. Type your abstract
+here. Type your abstract here. Type your abstract here. Type your
+abstract here. Type your abstract here. Type your abstract here. Type
+your abstract here. Type your abstract here. Type your abstract here.
+Type your abstract here. Type your abstract here.Type your abstract here. 
+Type your abstract here. Type your abstract here. Type your abstract here. 
+Type your abstract here. Type your abstract here. Type your abstract here.
+
+Please Type your abstract here. Type your abstract here. Type your abstract
+Please Type your abstract here. Type your abstract here. Type your abstract
+here. Type your abstract here. Type your abstract here. Type your
+abstract here. Type your abstract here. Type your abstract here. Type
+your abstract here. Type your abstract here. Type your abstract here.
+Type your abstract here. Type your abstract here.
+Please Type your abstract here. Type your abstract here. 
+Type your abstract here.
+%%%%
 \end{abstract}
 
-\maketitle
+\begin{keyword}
+%% MSC codes here, in the form: \MSC code \sep code
+%% or \MSC[2008] code \sep code (2000 is the default)
+\MSC 41A05\sep 41A10\sep 65D05\sep 65D17
+%% Keywords
+\KWD Keyword1\sep Keyword2\sep Keyword3
+\end{keyword}
 
-\tableofcontents
+\end{frontmatter}
 
@@
 
-\subsubsection{Polarisation}
+\subsection{Polarisation}
 
@@
 
-\subsubsection{Dual-rail}
+\subsection{Dual-rail}
 
@@
 
-\subsubsection{Time-bins}
+\subsection{Time-bins}
 
@@
 \begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{reck}
+\centering
+\includegraphics[width=0.7\columnwidth]{reck}
 \caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.6\columnwidth]{cluster_state}
+\centering
+\includegraphics[width=0.3\columnwidth]{cluster_state}
 \caption{The representation of cluster states as a graph.
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.7\columnwidth]{fusion}
+\centering
+\includegraphics[width=0.4\columnwidth]{fusion}
 \caption{Fusion gates for joining smaller cluster states into larger ones.
@@
 \begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{full_architecture}
+\centering
+\includegraphics[width=0.5\columnwidth]{full_architecture}
 \caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train.
@@
 \begin{figure}[!htb]
-\includegraphics[width=0.7\columnwidth]{PBS_TB}
+\centering
+\includegraphics[width=0.4\columnwidth]{PBS_TB}
 \caption{Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train.
@@
  \begin{figure}[!htb]
-\includegraphics[width=0.7\columnwidth]{phE}
+ \centering
+\includegraphics[width=0.4\columnwidth]{phE}
 \caption{A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.} \label{fig:MZ}	
@@
 \begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{MORDOR}
+\centering
+\includegraphics[width=0.5\columnwidth]{MORDOR}
 \caption{Architecture of the quantum Fourier transform interferometer for metrology using single-photon states.
@@
 
-\begin{acknowledgments}
+\section*{Acknowledgments}
 P.P.R.
@@
 
-\end{acknowledgments}
-
 %
@@
 
+\section*{References}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
 \bibliography{paper}

### 2017-05-09 revip-template.tex
Changed the sty file to Revip, cleaned up the look of the paper.

%% This is file `revip-template.tex',
%% 
%% Copyright 2016 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%%
%% $Id: $
%%
%% Use the option review to obtain double line spacing
%\documentclass[times,review,preprint,authoryear]{elsarticle}

%% Use the options `final' to obtain the final layout
%% Use longtitle option to break abstract to multiple pages if overfull.
%% For Review pdf (With double line spacing)
%\documentclass[times,review]{elsarticle}
%% For abstracts longer than one page.
%\documentclass[times,review,longtitle]{elsarticle}
%% For Review pdf without preprint line
%\documentclass[times,review,nopreprintline]{elsarticle}
%% Final pdf
\documentclass[times,final]{elsarticle}
%%
%\documentclass[times,final,longtitle]{elsarticle}
%%

%% Stylefile to load REVIP template
\usepackage{revip}
\usepackage{framed,multirow}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{latexsym}

% Following three lines are needed for this document.
% If you are not loading colors or url, then these are
% not required.
\usepackage{url}
\usepackage{xcolor}

%\usepackage{hyperref}

\definecolor{newcolor}{rgb}{.8,.349,.1}

\journal{Reviews in Physics}

\begin{document}

\verso{Given-name Surname \textit{etal}}

\begin{frontmatter}

\title{Type the title of your paper, only capitalize first
word and proper nouns\tnoteref{tnote1}}%
\tnotetext[tnote1]{This is an example for title footnote coding.}

\author[1]{Given-name1 \snm{Surname1}\corref{cor1}}
\cortext[cor1]{Corresponding author: 
  Tel.: +0-000-000-0000;  
  fax: +0-000-000-0000;}
\author[1]{Given-name2 \snm{Surname2}\fnref{fn1}}
\fntext[fn1]{This is author footnote for second author.}
\author[2]{Given-name3 \snm{Surname3}}
%% Third author's email
\ead{author3@author.com}
\author[2]{Given-name4 \snm{Surname4}}

\address[1]{Affiliation 1, Address, City and Postal Code, Country}
\address[2]{Affiliation 2, Address, City and Postal Code, Country}

\received{1 May 2013}
\finalform{10 May 2013}
\accepted{13 May 2013}
\availableonline{15 May 2013}
\communicated{S. Sarkar}

\begin{abstract}
%%%
Please Type your abstract here. Type your abstract here. Type your abstract
here. Type your abstract here. Type your abstract here. Type your
abstract here. Type your abstract here. Type your abstract here. Type
your abstract here. Type your abstract here. Type your abstract here.
Type your abstract here. Type your abstract here.Type your abstract here. 
Type your abstract here. Type your abstract here. Type your abstract here. 
Type your abstract here. Type your abstract here. Type your abstract here.

Please Type your abstract here. Type your abstract here. Type your abstract
Please Type your abstract here. Type your abstract here. Type your abstract
here. Type your abstract here. Type your abstract here. Type your
abstract here. Type your abstract here. Type your abstract here. Type
your abstract here. Type your abstract here. Type your abstract here.
Type your abstract here. Type your abstract here.
Please Type your abstract here. Type your abstract here. 
Type your abstract here.
%%%%
\end{abstract}

\begin{keyword}
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\MSC 41A05\sep 41A10\sep 65D05\sep 65D17
%% Keywords
\KWD Keyword1\sep Keyword2\sep Keyword3
\end{keyword}

\end{frontmatter}

%\linenumbers

%% main text
\section{Note}
\label{sec1}
Please use \verb+elsarticle.cls+ for typesetting your paper.
Additionally load the package \verb+revip.sty+ in the preamble using
the following command: 
\begin{verbatim} 
  \usepackage{revip}
\end{verbatim}

Following commands are defined for this journal which are not in
\verb+elsarticle.cls+. 
\begin{verbatim}
  \received{}
  \finalform{}
  \accepted{}
  \availableonline{}
  \communicated{}
\end{verbatim}

Any instructions relavant to the \verb+elsarticle.cls+ are applicable
here as well. See the online instruction available on:
\makeatletter
\if@twocolumn
\begin{verbatim}
 http://support.river-valley.com/wiki/
 index.php?title=Elsarticle.cls
\end{verbatim}
\else
\begin{verbatim}
 http://support.river-valley.com/wiki/index.php?title=Elsarticle.cls
\end{verbatim}
\fi

\subsection{Entering text}
\textcolor{newcolor}{\bf Please note that Full Length Papers can have 7
pages (plus one page after revision) and Special Issue Papers can have
10 pages (plus one page after revision). The only exception is the
review article that is submitted to a Special Issue. These limits
include all materials e.g. narrative, figures, tables, references,
etc.}

\section{The first page}
Avoid using abbreviations in the title. Next, list all authors with
their first names or initials and surnames (in that order). Indicate
the author for correspondence (see elsarticle documentation).

Present addresses can be inserted as footnotes. After having listed all
authors' names, you should list their respective affiliations. Link
authors and affiliations using superscript lower case letters.

\subsection{The Abstract}
An Abstract is required for every paper; it should succinctly summarize
the reason for the work, the main findings, and the conclusions of the
study. The abstract should be no longer than 200 words. Do not include
artwork, tables, elaborate equations or references to other parts of
the paper or to the reference listing at the end. ``Comment'' papers
are exceptions, where the commented paper should be referenced in full
in the Abstract.

The reason is that the Abstract should be understandable in itself to
be suitable for storage in textual information retrieval systems.

\textit{Example of an abstract: A biometric sample collected in an
uncontrolled outdoor environment varies significantly from its
indoor version. Sample variations due to outdoor environmental
conditions degrade the performance of biometric systems that
otherwise perform well with indoor samples. In this study, we
quantitatively evaluate such performance degradation in the case
of a face and a voice biometric system. We also investigate how
elementary combination schemes involving min-max or z
normalization followed by the sum or max fusion rule can
improve performance of the multi-biometric system. We use
commercial biometric systems to collect face and voice samples
from the same subjects in an environment that closely mimics the
operational scenario. This realistic evaluation on a dataset of
116 subjects shows that the system performance degrades in
outdoor scenarios but by multimodal score fusion the
performance is enhanced by 20\%. We also find that max rule
fusion performs better than sum rule fusion on this dataset. More
interestingly, we see that by using multiple samples of the same
biometric modality, the performance of a unimodal system can
approach that of a multimodal system.}

\section{The main text}

Please divide your article into (numbered) sections (You can find the
information about the sections at
\url{http://www.elsevier.com/wps/find/journaldescription.cws_home/505619/authorinstructions}).
Ensure that all tables, figures and schemes are cited in the text in
numerical order. Trade names should have an initial capital letter, and
trademark protection should be acknowledged in the standard fashion,
using the superscripted characters for trademarks and registered
trademarks respectively. All measurements and data should be given in
SI units where possible, or other internationally accepted units.
Abbreviations should be used consistently throughout the text, and all
nonstandard abbreviations should be defined on first usage
\citep{Vehlowetal2013}.

\begin{table*}[!t]
\caption{\label{tab1}Summary of different works pertaining to face and
speech fusion}
\centering
\begin{tabular}{|p{2.25cm}|p{2cm}|l|p{4cm}|p{3cm}|p{2cm}|}
\hline
Study & Algorithm used & DB Size & Covariates of interest & 
Top individual performance & Fusion\newline Performance\\
\hline
UK-BWG
(Mansfield et al.,
2001) &
Face, voice:\newline
Commercial & 200 & Time: 1--2 month\newline
separation (indoor) & 
TAR$^*$ at 1\% FAR$^{\#}$\newline
Face: 96.5\%\newline
Voice: 96\%
& --\\
\hline
Brunelli
(Brunelli and
Falavigna, 1995) & 
Face:\newline
Hierarchical\newline
correlation\newline
Voice:\newline
MFCC & 
87 & 
Time: 3 sessions, time\newline
unknown (indoor) & 
Face:\newline
TAR = 92\% at\newline
4.5\% FAR\newline
Voice:\newline
TAR = 63\% at\newline
15\% FAR
&
TAR =98.5\%\newline
at 0.5\% FAR\\
\hline
Jain
(Jain et al., 1999)
&
Face:\newline
Eigenface\newline
Voice:\newline
Cepstrum\newline
Coeff. Based
&
50
&
Time: Two weeks (indoor)
&
TAR at 1\% FAR\newline
Face: 43\%\newline
Voice: 96.5\%\newline
Fingerprint: 96\%
& 
Face $+$ Voice $+$\newline
Fingerprint $=$\newline
98.5\%\\
\hline
Sanderson
(Sanderson and
Paliwal, 2002)
&
Face: PCA\newline
Voice: MFCC &
43 
& Time: 3 sessions (indoor)\newline
Noise addition to voice & 
Equal Error Rate\newline
Face: 10\%\newline
Voice: 12.41\%
&
Equal Error\newline
Rate 2.86\% \\
\hline
Proposed study & 
Face, voice:\newline
Commercial & 116 &
Location: Indoor and\newline
Outdoor (same day)\newline
Noise addition to eye\newline 
coordinates 
&
TARs at 1\% FAR\newline
Indoor-Outdoor\newline
Face: 80\%\newline
Voice: 67.5\%
&
TAR = 98\%\newline
at 1\% FAR\\
\hline
\multicolumn{6}{@{}l}{$^*$TAR--True Acceptance Rate\qquad 
$^{\#}$ FAR--False Acceptance Rate}
\end{tabular}
\end{table*}

\subsection{Tables, figures and schemes}
Graphics and tables may be positioned as they should appear in the
final manuscript. Figures, Schemes, and Tables should be numbered.
Structures in schemes should also be numbered consecutively, for ease
of discussion and reference in the text. \textcolor{newcolor}{\bf
Figures should be maximum half a page size.}

Depending on the
amount of detail, you can choose to display artwork in one column (20
pica wide) or across the page (42 pica wide). Scale your artwork in
your graphics program before incorporating it in your text. If the
artwork turns out to be too large or too small, resize it again in your
graphics program and re-import it. The text should not run along the
sides of any figure. This is an example for citation \citep{NewmanGirvan2004}.

\begin{figure}[!t]
\centering
\includegraphics[scale=.5]{prletfig01}
\caption{Studio setup for capturing face images indoor. Three light
sources L1, L2, L3 were used in conjunction with normal office lights.}
\end{figure}

You might find positioning your artwork within the text difficult
anyway. In that case you may choose to place all artwork at the end of
the text and insert a marker in the text at the desired place. In any
case, please keep in mind that the placement of artwork may vary
somewhat in relation to the page lay-out \citep{HullermeierRifqi2009}.

This can easily be achieved using \verb+endfloat.sty+ package. Please
refer the following documentation to use this package.
\makeatletter
\if@twocolumn
\begin{verbatim}
  http://mirrors.ctan.org/macros/latex/contrib/
  endfloat/endfloat.pdf
\end{verbatim}
\else
\begin{verbatim}
  http://mirrors.ctan.org/macros/latex/contrib/endfloat/endfloat.pdf
\end{verbatim}
\fi
\makeatother

\textcolor{newcolor}{\bf You should insert a caption for the figures
below the figures and for the tables the caption should be above the
tables.}

Please remember that we will always also need highresolution versions
of your artwork for printing, submitted as separate files in standard
format (i.e. TIFF or EPS), not included in the text document. Before
preparing your artwork, please take a look at our Web page:
\url{http://www.elsevier.com/locate/authorartwork}.

\subsection{Lists}

For tabular summations that do not deserve to be presented as
a table, lists are often used. Lists may be either numbered or
bulleted. Below you see examples of both.
\begin{enumerate}
\item The first entry in this list
\item The second entry
\begin{enumerate}
\item A subentry
\end{enumerate}
\item The last entry
\end{enumerate}
\begin{itemize}
\item A bulleted list item
\item Another one
\end{itemize}

\subsection{Equations}
Conventionally, in mathematical equations, variables and
anything that represents a value appear in italics.
All equations should be numbered for easy referencing. The number
should appear at the right margin.
\begin{equation}
S_{\rm pg}'=\frac{S_{\rm pg}-\min(S_{\rm pG})}
 {\max(S_{\rm pG}-\min(S_{\rm pG})}
\end{equation}
In mathematical expressions in running text ``/'' should be used for
division (not a horizontal line).

\section*{Acknowledgments}
Acknowledgments should be inserted at the end of the paper, before the
references, not as a footnote to the title. Use the unnumbered
Acknowledgements Head style for the Acknowledgments heading.

\section*{References}

Please ensure that every reference cited in the text is also present in
the reference list (and vice versa).

\section*{\itshape Reference style}

Text: All citations in the text should refer to:
\begin{enumerate}
\item Single author: the author's name (without initials, unless there
is ambiguity) and the year of publication;
\item Two authors: both authors' names and the year of publication;
\item Three or more authors: first author's name followed by `et al.'
and the year of publication.
\end{enumerate}
Citations may be made directly (or parenthetically). Groups of
references should be listed first alphabetically, then chronologically.

%Numbered style references.
\bibliographystyle{model1-num-names}
\bibliography{refs}

\section*{Supplementary Material}

Supplementary material that may be helpful in the review process should
be prepared and provided as a separate electronic file. That file can
then be transformed into PDF format and submitted along with the
manuscript and graphic files to the appropriate editorial office.

\end{document}

%%

### 2017-05-09 paper.tex
Added intro section

@@
 \usepackage{framed,multirow}
-\usepackage{hyperref,mathrsfs,amsmath,amssymb,url,latexsym}
+\usepackage{hyperref,mathrsfs,amsmath,amssymb,latexsym}
 
@@
 
-\comment{To do}
-
-Technical advancements have been made on many fronts.
-It is possible now to put single-photon sources and linear-optical networks on a silica chip.
+Technical advancements in linear optics have been made on many fronts that make it increasingly attractive for quantum computing applications.
+It is possible now to put single-photon sources and detectors together with linear-optical networks on a silica chip.
 The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized.
 This increases the scalability of optical implementations of quantum information protocols.
+Having all components on chip reduces coupling losses
+
+In combination with the relative ease of transferring quantum states of light through fiber cables, it forms a powerful combination between quantum communication and quantum information processing on-chip.
+
+Spontaneous parametric down-conversion (SPDC), a nonlinear optical process, has been the workhorse for providing entanglement in quantum states of light.
+Through SPDC, indistinguishable single-photon pairs have been a run-of-the-mill process for a few decades, but faced scalability issues as it is a probabilistic process.
+
+There are several proposals for building
+quantum computers that manipulate the state of light,
+ranging from cat-state logic to encoding a qubit in a
+harmonic  oscillator  and  optical  continuous-variable
+quantum computing. Cat states are states of the form, where is a weak coherent state. The logical qubits are determined by the sign of the relative phase Ralph et al., 2003. Gottesman, Kitaev, and
+Preskil proposed quantum error correction codes for
+harmonic oscillators that are used to encode qubit states
+and showed that fault-tolerant quantum computing is
+possible using quantum optics Gottesman et al., 2001.
+Lloyd and Braunstein showed how the concept of quan-
+tum computing can be extended to continuous variables
+and how electromagnetic fields are a natural physical
+representation of this formalism Lloyd and Braunstein,
+1999. For a review article on optical quantum informa-
+tion processing with continuous variables, see
+Braunstein and van Loock 2005.
+
+In this review, we focus on quantum computing with
+linear quantum optics and single photons. It has the ad-
+vantage that the smallest unit of quantum information,
+the photon, is potentially free from decoherence: The
+quantum information stored in a photon tends to stay
+there. The downside is that photons do not naturally
+interact with each other, and in order to apply two-qubit
+quantum gates such interactions are essential. There-
+fore, if we are to construct an optical quantum com-
+puter, we have to introduce an effective interaction be-
+tween photons in one way or another. In Sec. I.D, we
+review the use of so-called large cross-Kerr nonlineari-
+ties to induce a single-photon controlled-NOT operation.
+However, naturally occurring nonlinearities of this sort
+are many orders of magnitude too small for our purposes.
+An alternative way to induce an effective interaction between photons is to make projective measurements with photodetectors.
+The difficulty with this
+technique is that such optical quantum gates are proba-
+bilistic: More often than not, the gate fails and destroys
+the information in the quantum computation. This can
+be circumvented by using an exponential number of op-
+tical modes, but scalability requires only a polynomial
+number of modes see also Sec. I.D. In 2001, Knill, Laflamme, and Milburn
+2001
+
+
+KLM constructed a
+protocol in which probabilistic two-photon gates are
+teleported into a quantum circuit with high probability.
+Subsequent error correction in the quantum circuit is
+used to bring the error rate down to fault-tolerant levels.
+We describe the KLM protocol in detail in Sec. II.
+Initially, the KLM protocol was designed as a proof
+that linear optics and projective measurements allow for
+scalable quantum computing in principle. However, it
+subsequently spurred new experiments in quantum op-
+tics, demonstrating the operation of high-fidelity proba-
+bilistic two-photon gates. On the theoretical front, sev-
+eral improvements of the protocol were proposed,
+leading to ever smaller overhead costs on the computa-
+tion. A number of these improvements is based on
+cluster-state quantum computing, or the one-way quan-
+tum computer. Recently, a circuit-based model was
+shown to have similar scaling properties as the best-
+known cluster-state model. In Sec. III, we describe sev-
+eral improvements to linear optical quantum informa-
+tion processing in considerable detail, and in Sec. IV, we
+describe the issues involved in the use of realistic com-
+ponents such as photon detectors, photon sources, and
+quantum memories. Given these realistic components,
+we discuss loss tolerance and general error correction
+for linear optical quantum computing (LOQC) in Sec. V.
+We will restrict our discussion to the theory of single-
+photon implementations of quantum information pro-
+cessors, and assume some familiarity with the basic con-
+cepts of quantum computing. For an introduction to
+quantum computation and quantum information, see,
+e.g., Nielsen and Chuang 2000. In Sec. VI we conclude
+with an outlook on other promising optical quantum in-
+formation processing techniques, such as photonic band-
+gap structures, weak cross-Kerr nonlinearities, and hy-
+brid matter-photon systems. We start our review with a
+short introduction to linear optics, N-port optical inter-
+ferometers, and circuits, and define the different versions of the optical qubit.
 

### 2017-05-09 paper.tex
Edited intro

--- 2017-05-09 paper.tex
@@
 
-\comment{To do}
-
-Technical advancements have been made on many fronts.
-It is possible now to put single-photon sources and linear-optical networks on a silica chip.
+Technical advancements in linear optics have been made on many fronts that make it increasingly attractive for quantum computing applications.
+It is possible now to put single-photon sources and detectors together with linear-optical networks on a silica chip.
 The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized.
 This increases the scalability of optical implementations of quantum information protocols.
+Having all components on chip reduces coupling losses which would be crucial for fault-tolerant quantum computing.
+With the advantage of potentially piggybacking on existing communication infrastructure, and the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, it forms a powerful platform for quantum information processing.
+
+In this review we will focus on single-photon encoding.
+Although other encodings, particularly those using continuous variable states of light exist, single-photon encodings seem to be the most promising.
+In the last decade, single photons have been produced mainly through spontaneous parametric down-conversion (SPDC), a nonlinear optical process.
+SPDC produces single photons in correlated pairs that has been the workhorse for providing entanglement in quantum states of light.
+Through much development in production schemes, and improvement in crystal quality, the number of high quality indistinguishable photons that can be concurrently produced have increased steadily over the years.
+Single-photon pairs are now run-of-the-mill business for quantum optical labs, and in the last five years, three photons are the landmark.
+The current record for single photons stand at ten.
+We have also seen the meteoric rise of quantum dots for this purpose.
+The latter has the advantage of on-demand single photon production, while SPDC is an inherently probabilistic process.
 
@@
 \centering
-\includegraphics[width=0.7\columnwidth]{reck}
+\includegraphics[width=0.5\columnwidth]{reck}
 \caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	

### 2017-05-10 paper.tex
Added to intro

@@
 
-\title{The Resurgence of the linear optics interferometer --- recent advances \& applications}
+\title{The resurgence of the linear optics interferometer --- recent advances \& applications}
 
@@
 
-In this review we will focus on single-photon encoding.
-Although other encodings, particularly those using continuous variable states of light exist, single-photon encodings seem to be the most promising.
 In the last decade, single photons have been produced mainly through spontaneous parametric down-conversion (SPDC), a nonlinear optical process.
 SPDC produces single photons in correlated pairs that has been the workhorse for providing entanglement in quantum states of light.
-Through much development in production schemes, and improvement in crystal quality, the number of high quality indistinguishable photons that can be concurrently produced have increased steadily over the years.
-Single-photon pairs are now run-of-the-mill business for quantum optical labs, and in the last five years, three photons are the landmark.
-The current record for single photons stand at ten.
-We have also seen the meteoric rise of quantum dots for this purpose.
-The latter has the advantage of on-demand single photon production, while SPDC is an inherently probabilistic process.
+Through development and improvement in production schemes, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
+Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical labs, and in the last five years, three photons have become the standard benchmark.
+Experiments with up to ten photons have now been demonstrated.
+We have also seen the meteoric rise of quantum dots in the role for producing single photons.
+It is now possible to use a quantum dot to produce multiple single photons which are highly indistinguishable.
+Quantum dots produce single photons on demand, a significant advantage over SPDC which is an inherently probabilistic process.
+
+The degree of control over single photons has also improved.
+Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum, new ways to engineer entangled quantum states and implement quantum operations have been discovered.
+These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time,
+
+In Section xxx, ...
 
@@
 
-A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer.
+An idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer.
 The creation and annihilation operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.

### 2017-05-10 paper.tex
Cleaning up section 2

@@
 Having all components on chip reduces coupling losses which would be crucial for fault-tolerant quantum computing.
-With the advantage of potentially piggybacking on existing communication infrastructure, and the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, it forms a powerful platform for quantum information processing.
+With the advantage of potentially piggybacking on existing communication infrastructure, and the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.
 
@@
 
-In Section xxx, ...
+In Section \ref{sec:math}, ...
+And in Section \ref{sec:encoding}
 
-\section{Mathematical background}
+\section{Mathematical background}\label{sec:math}
 
-An idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer.
-The creation and annihilation operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.
-A similar commutation relationship can be written when additional degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present.
-When multiple photons are present, they experience quantum interference when all quantum labels are the same.
-
-The action of a $2d$-port linear optical interferometer (with an equal number of input and output ports) is expressed as an application of unitary operations on the creation operators,
-
+A single photon in a quantum interferometer is described by its creation and annihilation operators, $\adagh_{j}$ and $\hat{a}_j$ respectively, where $j$ is the mode label of the interferometer.
+These operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.
+The action of a $2d$-port linear optical interferometer that has an equal number of input and output ports is expressed as an application of unitary operations on the creation operators,
 \begin{align}
@@
 All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994}.
+By convention, the interferometer is assumed to act only on the spatial mode of the input state.
+
+Additional quantum labels (represented by $\alpha, \beta$) are added on when other degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present:
+\begin{align}
+[\ah_{j,\alpha},\adagh_{k,\beta}]=\delta_{j,k}\delta_{\alpha,\beta}\ .
+\end{align}
+As a consequence, quantum interference between multiple photons only occur when all quantum labels are the same.
 In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons as a sequence of beamsplitters and internal transformations.
@@
 
-\section{Optical encoding of quantum information on single-photons}
+\section{Optical encoding of quantum information on single-photons}\label{sec:encoding}
 

### 2017-05-10 paper.tex
Edit intro and math section.

@@
 The degree of control over single photons has also improved.
-Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum, new ways to engineer entangled quantum states and implement quantum operations have been discovered.
-These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time,
-
-In Section \ref{sec:math}, ...
+Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, new ways to engineer entangled quantum states and implement quantum operations have been discovered.
+These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time.
+We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons.
 And in Section \ref{sec:encoding}
@@
 where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in SU(d)$.
-All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994}.
+All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994} (see Section \ref{sec:decomp}).
 By convention, the interferometer is assumed to act only on the spatial mode of the input state.
 
-Additional quantum labels (represented by $\alpha, \beta$) are added on when other degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present:
+Additional quantum labels are added to the creation and annihilation operators when other degrees of freedom, such as polarization, orbital angular momentum, and time-bins, are present.
+In this case, their commutator relation is
 \begin{align}
-[\ah_{j,\alpha},\adagh_{k,\beta}]=\delta_{j,k}\delta_{\alpha,\beta}\ .
+[\ah_{j,\alpha},\adagh_{k,\beta}]=\delta_{j,k}\delta_{\alpha,\beta}\ ,
 \end{align}
+where $\alpha$ and $\beta$ represent these other degrees of freedom.
 As a consequence, quantum interference between multiple photons only occur when all quantum labels are the same.
-In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons as a sequence of beamsplitters and internal transformations.
+It is also possible to derive an analogous decomposition to that of Reck {\it et al.~}that realizes the unitary transformation on such photons as a sequence of beamsplitters and internal transformations.
 Toolkits using group theory are being developed to deal with partial distinguishabilities among interfering photons \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}.
@@
 
-\section{Efficient circuit decompositions of linear optics networks}
+\section{Efficient circuit decompositions of linear optics networks}\label{sec:decomp}
 

### 2017-05-10 paper.tex
Edited math background.

@@
 We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons.
-And in Section \ref{sec:encoding}
+And in Section \ref{sec:encoding}...
 
@@
 It is also possible to derive an analogous decomposition to that of Reck {\it et al.~}that realizes the unitary transformation on such photons as a sequence of beamsplitters and internal transformations.
-Toolkits using group theory are being developed to deal with partial distinguishabilities among interfering photons \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}.
-Others use quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}.
-\sihui{Experimental implementation [Walmsley, Jennewein]}
+
+Control of indistinguishability of these photons may enable future applications.
+Mathematical methods have been developed to deal with partial distinguishabilities among interfering photons, including those using group theory \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}, and quantum-to-classical transitions \cite{bib:Ra2013}.
+Recently, genuine three-photon interference that has no independent entanglement between any two subpairs of photons was demonstrated  \cite{bib:Agne17,bib:Menssen17}.
 

### 2017-05-11 paper.tex
Revised the time bin section 3.3

@@
 Mathematical methods have been developed to deal with partial distinguishabilities among interfering photons, including those using group theory \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}, and quantum-to-classical transitions \cite{bib:Ra2013}.
-Recently, genuine three-photon interference that has no independent entanglement between any two subpairs of photons was demonstrated  \cite{bib:Agne17,bib:Menssen17}.
+Recently, by controlling multiple degrees of freedom of single photons, genuine three-photon interference that has no independent entanglement between any two subpairs of photons was demonstrated  \cite{bib:Agne17,bib:Menssen17}.
 
@@
 Rather, fast switching can be used to spatially separate neighbouring time-bins, implement a beamsplitter operation between them, before converting back to time-bin encoding.
+An experiment has built on this idea to implement a two-qubit gate by fast switching to a polarization basis \cite{bib:Humphreys2013}.
+Another promising advance is an ultrafast measurement technique for time bins based on converting into frequency bins \cite{bib:Donohue2013}.
+Scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}.
+This is discussed in more detail in Section \ref{sec:timebins}.
 
-Time-bin encoding was first conceived via a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}.
-If the photon passes through the shorter (longer) path, it will arrive at the output port in an `early' (`later') time-bin labelled $\ket{e}$ ($\ket{\ell}$).
-Thus, the photon will exit the interferometer in a state that is a superposition of these two states.
-Owing to difficulties in implementing qubit operations in this basis, it was at the time mostly used for demonstrating quantum communication over long distances \cite{bib:Thew02,bib:Marcikic04}.
-With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operation, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}.
-These gates form an universal set for quantum computing.
-At the same time, an ultrafast measurement technique for recovering time-bin qubits was also demonstrated \cite{bib:Donohue2013}.
+%Time-bin encoding was first conceived via a single-photon passing 
+%through a Mach-Zedner interferometer with its two paths having 
+%different lengths \cite{bib:Brendel99}. If the photon passes 
+%through the shorter (longer) path, it will arrive at the output 
+%port in an `early' (`later') time-bin labelled $\ket{e}$ ($
+%\ket{\ell}$). Thus, the photon will exit the interferometer in a 
+%state that is a superposition of these two states. 
+%Owing to difficulties in implementing qubit operations in this 
+%basis, it was at the time mostly used for demonstrating quantum 
+%communication over long distances \cite{bib:Thew02,bib:Marcikic04}.
 
-In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin qubits have a polarization register which is used to toggle between the mode in which qubits are stored and transmitted, {\it i.e.} the `register' mode, and the mode in which qubits are manipulated, {\it i.e.} the `processing' mode using a polarization rotation.
-Other operations needed are a displacement operation, that moves a time-bin qubit in the processing polarization in time relative to other qubits, a partial polarization rotation between the register and processing polarizations to couple them, and a photon number measurement in a bin.
-The polarization rotation and polarization coupling operations were implemented using a fast integrated optical switch based on polarization-sensitive cross-phase modulation with a switching time of less than 10ps.
-The displacement was implemented using a calcite crystal of a size that is of a path-length difference equal to an integer multiple of the time-bin separation.
-Using these operations and post-selection using a single-photon detectors, the authors were able to perform a heralded CPHASE gate \cite{bib:KLM01}.
+%With the advent of faster optical components, and single-photon 
+%detectors, it has become feasible to perform any single qubit 
+%operation, and a post-selected CPHASE gate on time-bin qubits 
+%\cite{bib:Humphreys2013}. These gates form an universal set for 
+%quantum computing. At the same time, an ultrafast measurement 
+%technique for recovering time-bin qubits was also demonstrated 
+%\cite{bib:Donohue2013}.
 
-In Donohue {\it et al.} \cite{bib:Donohue2013}, time-bins were converted into frequency bins using a nonlinear optical process known as sum-frequency generation (SFG) by pumping them on a crystal with a laser beam.
-The waveforms of the input photons and the pump beam are chirped in opposite directions in frequency, so that the output is a set of two peaks separated in frequency by an amount proportional to the time separation of the time bins.
-The output can then be measured with detectors that are slow compared to this separation.
-This is unlike conventional time-bin measurements which involve sending a time-bin state through an unbalanced Mach-Zedner interferometer matched to the time-bin separation to produce three output pulses that are separated by the time delay, and then having to resolve the middle pulse in time.
+%In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin 
+%qubits have a polarization register which is used to toggle between 
+%the mode in which qubits are stored and transmitted, {\it i.e.} the 
+%`register' mode, and the mode in which qubits are manipulated, {\it 
+%i.e.} the `processing' mode using a polarization rotation. Other 
+%operations needed are a displacement operation, that moves a time-
+%bin qubit in the processing polarization in time relative to other 
+%qubits, a partial polarization rotation between the register and 
+%processing polarizations to couple them, and a photon number 
+%measurement in a bin. The polarization rotation and polarization 
+%coupling operations were implemented using a fast integrated 
+%optical switch based on polarization-sensitive cross-phase 
+%modulation with a switching time of less than 10ps. The 
+%displacement was implemented using a calcite crystal of a size that 
+%is of a path-length difference equal to an integer multiple of the 
+%time-bin separation. Using these operations and post-selection 
+%using a single-photon detectors, the authors were able to perform a 
+%heralded CPHASE gate \cite{bib:KLM01}.
 
-Apart from these promising advances in implementing time-bin qubit gates and ultrafast time-bin measurements, scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}.
-This is discussed in more detail in Section \ref{sec:timebins}.
+%In Donohue {\it et al.} \cite{bib:Donohue2013}, time-bins were 
+%converted into frequency bins using a nonlinear optical process 
+%known as sum-frequency generation (SFG) by pumping them on a 
+%crystal with a laser beam. The waveforms of the input photons and 
+%the pump beam are chirped in opposite directions in frequency, so 
+%that the output is a set of two peaks separated in frequency by an 
+%amount proportional to the time separation of the time bins. The 
+%output can then be measured with detectors that are slow compared 
+%to this separation. This is unlike conventional time-bin 
+%measurements which 
+%involve sending a time-bin state through an unbalanced Mach-Zedner 
+%interferometer matched to the time-bin separation to produce three 
+%output pulses that are separated by the time delay, and then having 
+%to resolve the middle pulse in time.
 

### 2017-05-11 paper.tex
More clean up.

@@
 These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time.
-We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons.
-And in Section \ref{sec:encoding}...
+We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons, and in Section \ref{sec:encoding} with a description of some commonly used qubit encodings.
 
@@
 
-Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Reck1994, bib:Englert2001}.
-Later, it has been shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
+Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}.
+Later, it was shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
 However, they do not provide an explicit construction for arbitrary unitaries.
@@
 If the linear optical transformations can be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
-Their approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.
+This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.
 
@@
 In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built.
-However, owing to manufacturing imperfections, a precise characterization of these devices is still needed post-production.
+However, owing to manufacturing imperfections, a precise characterization of these devices may still be needed post-production.
 One approach for achieving this is via quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
 However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterize the network, with exponential overhead, becoming impractical for large optical networks which can contain hundreds of modes using present-day technology \cite{bib:Harris16}.
-However, alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.
+To mitigate this problem, alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.
 

### 2017-05-11 paper.tex
Clean up Sec. 5

@@
 Generally, the unitary matrices of $d\times d$ linear optical devices are complex $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$.
-The scheme in \cite{bib:Laing12} relies on injecting one- and two-photon states into the network with correlated photon detection.
-First, they note some equivalencies: two unitaries $U$ and $U'$ are equivalent if there exist two diagonal unitary matrices $D_1^U$ and $D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are regarded as unknown and trivial phases on the input and output ports of the network, to which the one- and two-photon data are insensitive to.
-This reduces the first row and column elements to real numbers, i.e.
-$\theta_{1j}=\theta_{i1}=0$.
-Second, the photo-statistics remain invariant under complex conjugation by $U$.
-Thus, the imaginary part of $M_{2,2}$ must be non-negative.
-Then, assuming the first two rows and columns are non-vanishing, and there is no total loss in the interferometer, the matrix to be recovered is
-\begin{align}
-U=\left (\begin{array}{cccc}
-r_{11} & r_{12} & \ldots & r_{1m} \\
-r_{21} & r_{22}e^{i\theta_{22}} &\ldots & r_{2m}e^{i\theta_{2m}}\\
-\vdots & \vdots & \ddots & \vdots \\
-r_{m1} & r_{m2}e^{i\theta_{m2}} & \ldots & r_{mm}e^{i\theta_{mm}}
- \end{array}\right ) \ .
-\end{align}
-They showed it is possible to write the parameters $r_{ij}$, and $\theta_{ij}$ for $i,j\geq 2$ in terms of the $2m-1$ real parameters of the first column and row, and the visibility of two-photon inputs.
-The remaining $2m-1$ real parameters can be found via one-photon
-transmissions.
-An increased accuracy in the characterization is possible by estimating and correcting systematic errors that arise due to mode mismatch \cite{Dhand16}.
-Others have used numerical methods to find the closest parameters that yield the observed visibilities \cite{bib:Spagnolo16,bib:Tillmann16}.
+To characterize these numbers, one can do so by injecting one- and two-photon states into the network with correlated photon detection \cite{bib:Laing12}.
+With some mathematical simplifications, the first row and first column elements can be reduced to real numbers, and then found via one-photon transmissions.
+The remaining $r_{ij}$ and $\theta_{ij}$ parameters can then be written in terms of these real parameters, and the visibility of two-photon inputs.
+%
+%
+%First, they note some equivalencies: two unitaries $U$ and $U'$ are 
+%equivalent if there exist two diagonal unitary matrices $D_1^U$ and 
+%$D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are 
+%regarded as unknown and trivial phases on the input and output ports of 
+%the network, to which the one- and two-photon data are insensitive to. 
+%This reduces the first row and column elements to real numbers, i.e. $
+%\theta_{1j}=\theta_{i1}=0$. Second, the photo-statistics remain invariant 
+%under complex conjugation by $U$. Thus, the imaginary part of $M_{2,2}$ 
+%must be non-negative. Then, assuming the first two rows and columns are 
+%non-vanishing, and there is no total loss in the interferometer, the 
+%matrix to be recovered is
+%\begin{align}
+%U=\left (\begin{array}{cccc}
+%r_{11} & r_{12} & \ldots & r_{1m} \\
+%r_{21} & r_{22}e^{i\theta_{22}} &\ldots & r_{2m}e^{i\theta_{2m}}\\
+%\vdots & \vdots & \ddots & \vdots \\
+%r_{m1} & r_{m2}e^{i\theta_{m2}} & \ldots & r_{mm}e^{i\theta_{mm}}
+% \end{array}\right ) \ .
+%\end{align}
+%They showed it is possible to write the parameters  for $i,j\geq 2$  The
+% remaining $2m-1$ real parameters can be found via one-photon 
+%transmissions.
+%
+An increased accuracy in the characterization is possible by estimating 
+and correcting systematic errors that arise due to mode mismatch 
+\cite{Dhand16}. Others have used numerical methods to find the closest 
+parameters that yield the observed visibilities 
+\cite{bib:Spagnolo16,bib:Tillmann16}.
 
@@
 \centering
-\includegraphics[width=0.4\columnwidth]{PBS_TB}
+\includegraphics[width=0.6\columnwidth]{PBS_TB}
 \caption{Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train.

### 2017-05-11 paper.tex
More clean-up in Sections 5 and 6.

@@
 These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time.
+
 We begin in Section \ref{sec:math} with an overview of the mathematical treatment of linear optical transformation on single photons, and in Section \ref{sec:encoding} with a description of some commonly used qubit encodings.
+Any unitary transformation acting on the spatial label of single photons can be efficiently decomposed into a network of beamsplitters and phase-shifters.
+We discuss this, and an analogous decomposition for single photons with additional internal states, in Section \ref{sec:decomp}.
 
@@
 %detectors, it has become feasible to perform any single qubit 
-%operation, and a post-selected CPHASE gate on time-bin qubits 
+%operation, and a post-selected {\sc cphase} gate on time-bin qubits 
 %\cite{bib:Humphreys2013}. These gates form an universal set for 
@@
 %using a single-photon detectors, the authors were able to perform a 
-%heralded CPHASE gate \cite{bib:KLM01}.
+%heralded {\sc cphase} gate \cite{bib:KLM01}.
 
@@
 The states $\ket{\alpha_1}$ and $\ket{\alpha_2}$ are input into port 1, and $j$ respectively.
-The output intensity at the $j$th port is then
+The output intensity at the $k$th port is then
 \begin{align}
@@
 \end{align}
-where $\theta_{jk}=0$ for $k=1$.
+where $\theta_{jk}=0$ for $k=1$, and $I$ is the intensity of the input coherent states.
 By scanning the phase shift $\phi$ and locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$.
@@
 \begin{align}
-\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \\
+\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \ {\rm and} \\
 \ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
@@
 which are all maximally entangled and locally equivalent to one another.
-These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing \cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
-In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.} successfully prepared only under certain measurement outcomes of auxiliary modes.
+These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing.
+%\cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
+In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.~}successfully prepared only under certain measurement outcomes of auxiliary modes.
 Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}.
-They are often used as a building block for preparing other multipartite entangled states.
 
@@
 
-These states can be represented as a graph, in which vertices are qubits initialized into the superposition state $\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, with CPHASE operation applied between edges, as shown in Fig.~\ref{fig:cluster}.
+These states can be represented as a graph, in which vertices are qubits initialized into the superposition state $\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, with {\sc cphase} operation applied between edges, as shown in Fig.~\ref{fig:cluster}.
 For this reason, such states are also referred to as graph states.
-The CPHASE operations generate entanglement between the qubits, and because they commute, are independent of ordering.
+The {\sc cphase} operations generate entanglement between the qubits, and because they commute, are independent of ordering.
 Cluster states are a resource state for a model of quantum computation known as measurement-based quantum computation (MBQC).
@@
 \caption{The representation of cluster states as a graph.
-Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on CPHASE gates, the ordering of which is irrelevant.} \label{fig:cluster}
+Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on {\sc cphase} gates, the ordering of which is irrelevant.} \label{fig:cluster}
 \end{figure}
 
-Unfortunately, implementing CPHASE gates using linear optics is complicated and highly non-deterministic.
+Unfortunately, implementing {\sc cphase} gates using linear optics is complicated and highly non-deterministic.
 A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell basis.
@@
 These operations are shown in Fig.~\ref{fig:fusion}.
-Although these operations are non-deterministic with a success probability of $1/2$, they require only a single beamsplitter, already a major improvement over directly implementing CPHASE gates.
-Furthermore, unlike CPHASE gates, fusion operations require only high Hong-Ou-Mandel visibility, rather than the Mach-Zehnder stability required within existing CPHASE gate implementations, a major experimental simplification.
+Although these operations are non-deterministic with a success probability of $1/2$, they require only a single beamsplitter, already a major improvement over directly implementing {\sc cphase} gates.
+Furthermore, unlike {\sc cphase} gates, fusion operations require only high Hong-Ou-Mandel visibility, rather than the Mach-Zehnder stability required within existing {\sc cphase} gate implementations, a major experimental simplification.
 
-Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing CPHASE gates.
+Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing {\sc cphase} gates.
 
@@
 The early implementations of linear optics protocols relied on bulk-optics implementations, in which a circuit is decomposed into a discrete arrangement of optical components, specifically beamsplitters and phase-shifters.
-This corresponds to a direct implementation of the Reck \emph{et al.} decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate decompositions.
+This corresponds to a direct implementation of the Reck \emph{et al.~}decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate decompositions.
 
@@
 Using time-bin encoding of optical qubits, the obvious question is how to perform operations upon them.
-In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains, shown in Fig.~\ref{fig:FL_arch}.
+In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains with time-bin separation $\tau$, shown in Fig.~\ref{fig:FL_arch}.
+The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the
+number of optical modes). The architecture is controlled via three 
+dynamically controlled beamsplitters. The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, 
+keep it within the outer loop for the required duration, and then couple 
+out of the outer loop, yielding the transformed pulse-train. The central 
+beamsplitter must be able to implement arbitrary classically-controlled 
+beamsplitter operations.
 
@@
 \centering
-\includegraphics[width=0.5\columnwidth]{full_architecture}
+\includegraphics[width=0.4\columnwidth]{full_architecture}
 \caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train.
-The source prepares the temporally encoded pulse-train, with time-bin separation $\tau$.
-The pulse-train then enters a dual-loop configuration.
-The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the number of optical modes).
-The architecture is controlled via three dynamically controlled beamsplitters.
-The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, keep it within the outer loop for the required duration, and then couple out of the outer loop, yielding the transformed pulse-train.
-The central beamsplitter must be able to implement arbitrary classically-controlled beamsplitter operations.} \label{fig:FL_arch}
+%The source prepares the temporally encoded pulse-train, with time-bin 
+%separation $\tau$.
+%The pulse-train then enters a dual-loop configuration. The inner loop has 
+%%length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is 
+%the number of optical modes). The architecture is controlled via three 
+%dynamically controlled beamsplitters. The first and last need only be on/
+%off switches, whose sole purpose is to couple in the prepared pulse-
+%train, keep it within the outer loop for the required duration, and then 
+%couple out of the outer loop, yielding the transformed pulse-train. The 
+%central beamsplitter must be able to implement arbitrary classically-
+%controlled beamsplitter operations.
+} \label{fig:FL_arch}	
 \end{figure}
@@
 The workings of the scheme can be thought of as follows: the inner loop allows arbitrary beamsplitter operations between neighbouring time-bins; the outer loop does nothing interferometric, but rather enables the pulse-train to undergo as many applications of the inner loops as necessary.
-It then follows that this scheme is universal for linear optics, as a sufficient number of beamsplitter operations between neighbouring modes enables universal decompositions, using for example, the Reck \emph{et al.} decomposition described earlier.
+It then follows that this scheme is universal for linear optics, as a sufficient number of beamsplitter operations between neighbouring modes enables universal decompositions, using for example, the Reck \emph{et al.} decomposition described in Section \ref{sec:decomp}.
 
@@
 The above description applies to passive linear optics, which is sufficient for protocols such as {\sc BosonSampling}, but insufficient for universal optical quantum computation, which requires the addition of ancillary states, and measurement with fast-feedforward.
-To address this, it was shown in \cite{Rohde} that by dynamically preparing ancillary pulse-trains (from the already-existing source), classically controlled by time-resolved measurements at the output, and changing the switching sequence, we can effectively couple in and out arbitrary subsets of the optical modes, enabling partial measurements to be implemented.
+To address this, it was shown in \cite{Rohde15} that by dynamically preparing ancillary pulse-trains (from the already-existing source), classically controlled by time-resolved measurements at the output, and changing the switching sequence, we can effectively couple in and out arbitrary subsets of the optical modes, enabling partial measurements to be implemented.
 
@@
 \begin{align}
-\hat\Pi_n &= \ket{n}\bra{n}, \ n=0,1,\ldots \ ,\nonumber \\	
+\hat\Pi_n &= \ket{n}\bra{n}, \ n=0,1,\ldots \ ,
 \end{align}
@@
 \end{align}
-
 The dominant challenge facing the experimental implementation of both types of detectors is inefficiency due to loss, which results in higher photon-number being confused as having lower photon-number.
@@
 
-\subsubsection{Non-photon-number-resolving detectors}
+\subsubsection{Non-photon-number-resolving (non-PNR) detectors}
 The first type of non-PNR detectors are photomultiplier tubes (PMTs).
@@
 There are multiple challenges to implementing a scalable, fully-optical quantum computer, and progress has been focused on overcoming these challenges.
-In this section, we will discuss a few of these challenges, and the advances that have been made to overcome them.
+We will discuss a few of these challenges, and the advances that have been made to overcome them.
 
-\subsubsection{Challenges and Progress in LOQC}
 To date, the quantum computation still requires the use of non-deterministic operations, each of which succeeds with less than unity probability and has to be run many times before a single try succeeds.
@@
 
- Such Kerr nonlinearities are usually implemented on states of light via atom-photon interactions.
-Whether such cross-Kerr nonlinearities on single photon will help LOQC is a subject of debate.
-On one side, the arguments in the negative come down to fundamental noise limits in atom-photon interactions using phenomenological model of a cross-Kerr medium \cite{bib:Shapiro06,bib:Shapiro07,bib:Gea-Banacloche10}.
-On the other hand, an example of a CPHASE gate using photons that counterpropagate through multiple atom-mediated cross-Kerr interaction sites has been constructed, and theoretically shown to work via a first principle treatment of the multimode light field and atomic medium \cite{bib:Brod16}.
-Regardless of who is right in this debate, increments in the strength of Kerr nonlinearities have been achieved in the last five years \cite{bib:Hoi13,bib:Venkataraman13,bib:Feizpour15,bib:Beck16}, and this avenue remains a tantalizing possibility for deterministic quantum gates.
+ Such Kerr nonlinearities are usually implemented on states of light via 
+ atom-photon interactions. Whether such cross-Kerr nonlinearities on 
+ single photon will help LOQC is a subject of debate. On one side, the 
+ arguments in the negative come down to fundamental noise limits in atom-
+ photon interactions using phenomenological model of a cross-Kerr medium 
+ \cite{bib:Shapiro06,bib:Shapiro07,bib:Gea-Banacloche10}. On the other 
+ hand, an example of a {\sc {\sc cphase}} gate using photons that 
+ counterpropagate through multiple atom-mediated cross-Kerr interaction 
+ sites has been constructed, and theoretically shown to work via a first 
+ principle treatment of the multimode light field and atomic medium 
+ \cite{bib:Brod16}. Regardless of who is right in this debate, increments 
+ in the strength of Kerr nonlinearities have been achieved in the last 
+ five years \cite{bib:Hoi13,bib:Venkataraman13,bib:Feizpour15,bib:Beck16}, 
+ and this avenue remains a tantalizing possibility for deterministic 
+ quantum gates.
 

### 2017-05-11 paper.tex
Cleaned up Section 6.3.

@@
 \end{align}
+Detailed reviews have been written about these detectors \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few notable examples here.
+
+A common example of a non-PNR detector is the avalanche photodiode (APD).
+These devices are made up of semiconductor material, usually silicon, which generate an electron that quickly generates a cascade of electrons.
+This avalanche of electrons generate a current that can be measured.
+APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in a broad spectrum of wavelengths; from the visible to near-infrared range
+% A downside to using APD is their deadtime. This is a period of time 
+%following an avalanche during which the avalanche is stopped by a 
+%quenching circuit to reset the APD. No photons can be detected during the 
+%deadtime and contributes to photon loss in an APD. 
+Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector that has recently become commercially available.
+This detector uses a narrow superconducting wire that carries a current just below the critical current density, above which the superconducting wire would undergo a phase change back to its normal resistance.
+This happens when the SNSPD absorbs an incident photon, and the current in the wire would then by-pass it to go through the neighboring region which is at a lower resistance.
+The voltage spike that ensues is measured to give a photon number count.
+
+PNR detectors are a wonderful addition to the toolbox of linear optics.
+A notable example is the superconducting transition edge sensor (TES) which has an extremely high quantum efficiency.
+The principle it operates on is very similar to the SNSPD, but with a much higher sensitivity that allows it to detect the energy of single photons.
+%low dark count rates. However, they are quite slow, have low maximum 
+%counting rates, and are costly to operate due to their very low operating 
+%temperatures. 
+The visible light photon counter (VLPC) is another kind of PNR detector.
+The way VLPC works is in principle very similar to the APD, but with an additional layer of silicon that is lightly doped with arsenic (As).
+Owing to the presence of the As, a single photon absorption event always create an electrical signal that is always of the same magnitude.
+Thus, the output electrical signal is just proportional to the number of detected photons.
+Last, PNR detectors can be created by connecting many non-PNR detectors in parallel to one another, and summing the signals at the output.
+Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Afek09,bib:Chrapkiewicz14,bib:Chen17}.
+
 The dominant challenge facing the experimental implementation of both types of detectors is inefficiency due to loss, which results in higher photon-number being confused as having lower photon-number.
@@
 However, in most applications, including type-I fusion, this is highly problematic as photon-number confusion results in decoherence via projecting onto the wrong photon-number, unknown to the observer.
-Other common problems that plague these detectors are dark counts which add spurious counts from the background, and dead-time which causes the detector to lose counts during a period when it is inactive immediately after the detection of photons.
-
-\subsubsection{Non-photon-number-resolving (non-PNR) detectors}
-The first type of non-PNR detectors are photomultiplier tubes (PMTs).
-A PMT comprises of a vacuum tube with a photocathode for light absorption.
-The photoelectric effect then releases electrons in the photocathode, and this current is multiplied by a cascade of secondary electron emissions from a series of electrodes.
-This amplified signal can be picked up to indicate the presence of photons.
-
-In applications for quantum information processing, a well-established alternative to PMTs is the avalanche photodiode (APD).
-These are devices made up of semiconductor material, usually silicon, which is structured as a p-n junction and put into Geiger mode operation.
-When a photon is incident on the APD, electrons that are generated undergo an avalanche and the current that is generated can be measured.
-APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in wavelengths in the visible to near-infrared range.
-A downside to using APD is their deadtime.
-This is a period of time following an avalanche during which the avalanche is stopped by a quenching circuit to reset the APD.
-No photons can be detected during the deadtime and contributes to photon loss in an APD.
-
-The last type of non-PNR detectors we discuss is the superconducting nanowire single-photon detector (SNSPD) which have recently become commercially available.
-This detector uses a narrow superconducting wire that is carrying a current operating at just below the critical current density.
-Above this current density, the superconducting wire would undergo a phase change back to its normal resistance which happens when it absorbs an incident photon.
-The current in the wire would then by-pass it to go through the neighboring region which is still superconducting, and therefore at a lower resistance.
-This causes a voltage spike in the neighboring region which can be detected.
-
-\subsubsection{Photon-number-resolving detectors}
-
-Multiple technologies for realizing PNR detectors already exist and have been described by multiple reviews \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few notable examples here.
-One of these is the superconducting transition edge sensor (TES) .
-In TES, a layer of superconducting material is operated at a temperature in its transition between superconducting and normal resistance.
-Any small change in temperature will thus cause a large change in resistance of this layer which can be measured.
-This happens when photons are absorbed, and heats up the superconductor.
-Such detectors can be made so sensitive that the energy of single photons can be detected.
-Another advantage of the TES is its high efficiency which can be made very close to 100\% \cite{bib:Rosenberg05}, and low dark count rates.
-However, they are quite slow, have low maximum counting rates, and are costly to operate due to their very low operating temperatures.
-
-The visible light photon counter (VLPC) is another kind of PNR detector.
-The way VLPC works is in principle very similar to the APD.
-The top layer where the photon impinges is made of silicon, followed by another gain layer that is lightly doped with arsenic (As).
-When a photon is incident on this detector, it creates electrons which are then accelerated into the gain layer and ionize the As impurities, thereby exciting and scattering more electrons.
-An avalanche multiplication ensues just like in an APD.
-However, owing to the presence of the As gain later, the VLPC has a low multiplication noise which results in a single photon absorption event creating an electrical signal that is always of the same magnitude.
-Thus, the output electrical signal is just proportional to the number of detected photons.
-
-Last, we discuss an approach to creating PNR detectors from non-PNR detectors by connecting a bunch of the latter in parallel to one another, and summing the signals at the output to give a combined signal that is proportional to that of just one.
-Such an approach has been demonstrated with SNSPD connected in parallel \cite{bib:Divochiy08}, and APDs connected in an array that can be either on the same semiconductor substrate, or as an interferometric architecture \cite{bib:Afek09,bib:Chrapkiewicz14,bib:Chen17}.
-A drawback of the parallel-SNSPDs is their low quantum efficiency, while the spatially multiplexed APDs suffer from spurious counts known as crosstalk that arises from avalanches triggered by electrons launched from neighboring APDs \cite{bib:Eraerds07,bib:Afek09,bib:Kalashnikov12}.
+Other common problems that plague these detectors are dark counts which add spurious counts from the background.
+APDs suffer from dead-time which is a period of time following a detection event during which it is inactive.
+In applications requiring feedforwarding, this is problematic.
+Although TESs are great detectors, they are expensive because they require cryogenic equipment to function.
+The multiplexed SNSPDs suffer from the same constrain and also from low quantum efficiencies.
+While spatially multiplexed APDs are relatively cheap, they suffer from spurious counts known as crosstalk that arises from avalanches triggered by electrons launched from neighboring APDs \cite{bib:Eraerds07,bib:Afek09,bib:Kalashnikov12}.
+Given the important role of detectors in linear optical quantum computation (see Section \ref{sec:LOQC}), more could be done to improve them.
 
@@
 
-\subsection{Linear optics quantum computation (LOQC)}
+\subsection{Linear optics quantum computation (LOQC)}\label{sec:LOQC}
 With the advancement in single-photon state preparation, detectors and quantum interferometers, quantum computation using linear optics has become feasible. 
@@
  \centering
-\includegraphics[width=0.4\columnwidth]{phE}
+\includegraphics[width=0.3\columnwidth]{phE}
 \caption{A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.} \label{fig:MZ}	

### 2017-05-11 paper.tex
More clean up. Achieved 15 pages.

@@
 We discuss this, and an analogous decomposition for single photons with additional internal states, in Section \ref{sec:decomp}.
+For applying any linear optical circuit, one needs an accurate description of its unitary representation.
+A full quantum tomography is costly and time-consuming.
+Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction}.
 
@@
 
-\section{Reconstructing the linear optical network}
+\section{Reconstructing the linear optical network}\label{sec:reconstruction}
 
@@
 
-Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead of Fock states \cite{bib:Rahimi-Keshari13,bib:Heilmann15}.
+A similar method to that of Laing and O'Brien \cite{bib:Laing12} uses coherent states instead of Fock states \cite{bib:Rahimi-Keshari13,bib:Heilmann15} to probe the interferometer.
 Such states are produced by a standard laser source, thus reducing experimental resources.
@@
 
-\section{Experimental implementation}
+\section{Experimental implementation}\label{sec:expt}
 
@@
 
-\subsection{Linear optics quantum computation (LOQC)}\label{sec:LOQC}
-With the advancement in single-photon state preparation, detectors and quantum interferometers, quantum computation using linear optics has become feasible. 
-For universal quantum computation using linear optics and single photon inputs, nonlinear couplings between the different optical modes are needed.
-Photons, being bosons, do not interact with one another like the way fermions do.
-Hence, some careful engineering has to be done in order to achieve this nonlinear coupling between modes.
-Some of the methods used to introduce this nonlinearity include measurements and feedforwarding \cite{bib:KLM01}, and  photon-atom interactions \cite{bib:Brod16}.
-These nonlinearities have been used to construct entangling gates required for (approximate) universality in quantum computation using the circuit model.
-They have also been used to construct entangled graph states, like the cluster states covered in Section \ref{section:cluster}, that are used in MBQC.
-Comprehensive reviews have been written previously to cover this topic \cite{bib:Kok05,bib:JW12}, hence we will skip some basic information to focus on recent advances.
-There are multiple challenges to implementing a scalable, fully-optical quantum computer, and progress has been focused on overcoming these challenges.
-We will discuss a few of these challenges, and the advances that have been made to overcome them.
+\subsection{Linear optical quantum computation (LOQC)}\label{sec:LOQC}
+The advancements in linear optics discussed in Section \ref{sec:expt}, quantum computation using linear optics have opened up avenues for implementation.
+One of the key requirements is nonlinear couplings between the different optical modes.
+Photons do not naturally interact with one another so some careful engineering is needed to achieve this coupling.
+Methods used include measurements and feedforwarding \cite{bib:KLM01}, and photon-atom interactions \cite{bib:Brod16}.
+All models for LOQC also require non-deterministic operations, which succeeds only sometime and have to be repeated.
+This can be challenging given the limitations of the optical systems.
+Comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05}, hence we will focus on recent advances.
 
-To date, the quantum computation still requires the use of non-deterministic operations, each of which succeeds with less than unity probability and has to be run many times before a single try succeeds.
-Moreover extra qubits are needed for error correction.
-These requirements put an overhead on the computational cost, in particular at the single photon production stage where a high rate of production of multiple photons is desired for this purpose.
-Second, feed-forwarding requires detectors with very fast response time.
-In feedforward control, one mode is measured and then some operation that depend on the measurement outcome are effected on other modes.
-The readout from the measurement has to happen before the light beam in the target modes passes.
-The last challenge is that of loss.
-Loss can happen anywhere in the linear optical network, but is especially problematic in coupling between different mediums, and upon absorption of a photon in a detector.
-Loss causes computations to fail.
-In the case that this error is detectable, the computation would have to be repeated.
-If not, the computation returns a wrong result.
-
- Better single-photon sources that have been discussed in Section \ref{sec:singlephotons} are part of the solution to overcoming the above difficulties.
-Following the footsteps of implementing two-qubit gates using multiple degrees of freedom of single photons \cite{bib:Gasparoni04,bib:Zhao05,bib:Okamoto05,bib:Langford05,bib:Kiesel05,bib:Cernoch08,bib:Gao10,bib:Zhou11}, improvement in our theoretical understanding have also led to more efficient designs of circuits \cite{bib:Lanyon09,bib:Zhou11} that enabled the optical implementation of quantum teleportation of the state of a single photon \cite{bib:Wang15}.
-In this way, three-qubit \cite{bib:Lanyon09,bib:Micuda13,bib:Patel16} and four-qubit \cite{bib:Starek16} gates have also been implemented using LOQC.
-
- If one wishes to avoid the use of non-deterministic quantum gates, the most promising alternative is to use cross-Kerr nonlinearities which have Hamiltonians for two modes labelled by $a$ and $b$ that is proportional to the form
- \begin{align}
- a^\dag(\omega)a(\omega)b^\dag(\omega)b(\omega) \ .
- \end{align}
-
- Such Kerr nonlinearities are usually implemented on states of light via 
- atom-photon interactions. Whether such cross-Kerr nonlinearities on 
- single photon will help LOQC is a subject of debate. On one side, the 
- arguments in the negative come down to fundamental noise limits in atom-
- photon interactions using phenomenological model of a cross-Kerr medium 
- \cite{bib:Shapiro06,bib:Shapiro07,bib:Gea-Banacloche10}. On the other 
- hand, an example of a {\sc {\sc cphase}} gate using photons that 
- counterpropagate through multiple atom-mediated cross-Kerr interaction 
- sites has been constructed, and theoretically shown to work via a first 
- principle treatment of the multimode light field and atomic medium 
- \cite{bib:Brod16}. Regardless of who is right in this debate, increments 
- in the strength of Kerr nonlinearities have been achieved in the last 
- five years \cite{bib:Hoi13,bib:Venkataraman13,bib:Feizpour15,bib:Beck16}, 
- and this avenue remains a tantalizing possibility for deterministic 
- quantum gates.
-
- The advent of integrated photonic circuits has greatly improved the feasibility of LOQC.
-A small chip on silica can contain what used to be spread over large optical tables in bulk optics.
-They also offer greater interferometric stability so that the requisite quantum interference to happen is less affected by changes in path lengths.
-These have been discussed at lengths in another review \cite{bib:Meany15}.
-Recent breakthroughs with programmable circuits have made a single chip reusable for different applications \cite{bib:Metcalf14,bib:Carolan15}.
-Previously, a different chip has to be manufactured every time a new interferometer setup is desired which is a waste of resources and requires a lead time for production.
-
+ Integrated photonic circuits has greatly improved the feasibility of LOQC.
+Their small size and interferometric stability enable the requisite quantum interference to happen in certain LOQC settings.
+Programmable circuits that are reusable have also emerged \cite{bib:Metcalf14,bib:Carolan15}.
+This saves resources and lead time for producing new circuits.
 Combining these chips with existing higher-efficiency sources and detectors will expand their capabilities.
@@
 The bottleneck is in the speed of modulation in the feedforward circuitry.
-The successful implementations of feedforward require the use of a delay loop to slow down the target photons so that the modulator has time to catch up.
 
-  Although there has been tremendous progress in pushing for an all-optical universal quantum computer with single photons, it seems likely that an efficient, and fault-tolerant universal quantum computer will require a hybrid system of photonics and something else.
-Nonetheless, linear optics alone is still a fascinating platform for applications and foundational understanding of quantum mechanics.
+Better single-photon sources (see Section \ref{sec:singlephotons}) are part of the solution.
+Improvement in control of their degrees of freedom have also led to more efficient designs of circuits \cite{bib:Zhou11,bib:Lanyon09} that enabled the optical implementation of quantum teleportation of the state of a single photon \cite{bib:Wang15}.
+In this way, three-qubit \cite{bib:Lanyon09,bib:Micuda13,bib:Patel16} and four-qubit \cite{bib:Starek16} gates have also been implemented using LOQC.
+
+Cross-Kerr nonlinearity is a type of nonlinearity implemented through 
+ atom-photon interactions.
+It has been thought for some time that fundamental noise limits in atom-photon interactions will prevent any help for LOQC \cite{bib:Shapiro06,bib:Shapiro07,bib:Gea-Banacloche10}.
+However, this belief has been countered by the construction of a {\sc {\sc cphase}} gate using photons that undergo cross-Kerr interaction \cite{bib:Brod16}.
+Regardless of who is right in this debate, stronger Kerr nonlinearities have been achieved in the last
+ five years \cite{bib:Hoi13,bib:Venkataraman13,bib:Feizpour15,bib:Beck16}, 
+ and this avenue remains a tantalizing possibility for deterministic 
+ quantum gates.
+
+  Although there has been tremendous progress in linear optics, it seems likely that an efficient, and fault-tolerant universal quantum computer will require a hybrid system.
+Nonetheless, linear optics remains fascinating platform for applications and foundation work.
 
@@
 
- \begin{figure}[!htb]
- \centering
-\includegraphics[width=0.3\columnwidth]{phE}
-\caption{A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.} \label{fig:MZ}	
-\end{figure}
+% \begin{figure}[!htb]
+% \centering
+%\includegraphics[width=0.3\columnwidth]{phE}
+%\caption{A schematic diagram of the Mach-Zehnder interferometer comprising 
+%of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two 
+%paths.} \label{fig:MZ}	
+%\end{figure}
 

### 2017-05-12 paper.tex
Played around with bib file to remove doi but to no avail.
Added abstract

@@
 %%%
-Please Type your abstract here. Type your abstract here. Type your abstract
-here. Type your abstract here. Type your abstract here. Type your
-abstract here. Type your abstract here. Type your abstract here. Type
-your abstract here. Type your abstract here. Type your abstract here.
-Type your abstract here. Type your abstract here.Type your abstract here. 
-Type your abstract here. Type your abstract here. Type your abstract here. 
-Type your abstract here. Type your abstract here. Type your abstract here.
-
-Please Type your abstract here. Type your abstract here. Type your abstract
-Please Type your abstract here. Type your abstract here. Type your abstract
-here. Type your abstract here. Type your abstract here. Type your
-abstract here. Type your abstract here. Type your abstract here. Type
-your abstract here. Type your abstract here. Type your abstract here.
-Type your abstract here. Type your abstract here.
-Please Type your abstract here. Type your abstract here. 
-Type your abstract here.
+Linear optics has seen a resurgence owing to its miniaturisation on-chip, and increase in production efficiency and quality of single photons.
+Time-bin encodings have also become feasible owing to fresh architecture, and processing capabilities.
+Theoretical efforts to find useful application beyond a full universal quantum computation has also bore fruit.
+A sampling task, known as {\sc bosonsampling} that is easily implemented using linear optics but is strongly believed to be a hard for a classical computer, has emerged.
 %%%%
@@
 Any unitary transformation acting on the spatial label of single photons can be efficiently decomposed into a network of beamsplitters and phase-shifters.
-We discuss this, and an analogous decomposition for single photons with additional internal states, in Section \ref{sec:decomp}.
+We discuss this, and an extension to handle additional internal states, in Section \ref{sec:decomp}.
 For applying any linear optical circuit, one needs an accurate description of its unitary representation.
@@
 
-\section*{References}
-
 %% `Elsevier LaTeX' style

### 2017-05-12 paper.tex
More revisions
Section 6 (Experimental implementation) has been split into three
sections: state preparation, linear optical circuit, and
photodetection. This is mainly because I would like to discuss some
theory within those sections.

Figures 2 and 3 have been combined into a single figure, and so has
Figures 4 and 5.

@@
 \usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
 
@@
 This increases the scalability of optical implementations of quantum information protocols.
-Having all components on chip reduces coupling losses which would be crucial for fault-tolerant quantum computing.
-With the advantage of potentially piggybacking on existing communication infrastructure, and the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.
+Having all components on chip reduces coupling losses which would be crucial for fault-tolerance.
+An optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
+Combined withthe relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.
 
-In the last decade, single photons have been produced mainly through spontaneous parametric down-conversion (SPDC), a nonlinear optical process.
-SPDC produces single photons in correlated pairs that has been the workhorse for providing entanglement in quantum states of light.
-Through development and improvement in production schemes, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
-Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical labs, and in the last five years, three photons have become the standard benchmark.
-Experiments with up to ten photons have now been demonstrated.
+In the last decade, single photons have been produced mainly through a nonlinear optical process know as spontaneous parametric down-conversion (SPDC), a nonlinear optical process.
+SPDC produces single photons in correlated pairs that has been a staple source of entanglement.
+Through developments in production, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
+Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical labs, and three photons have become the standard benchmark.
+Experiments using up to ten photons have been demonstrated.
 We have also seen the meteoric rise of quantum dots in the role for producing single photons.
@@
 
-The degree of control over single photons has also improved.
-Using advanced techniques and equipment to manipulate their polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, new ways to engineer entangled quantum states and implement quantum operations have been discovered.
-These expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy, that is, the demonstration of a computational task with a quantum  device that is not possible with any known algorithm running on an existing classical supercomputer in a reasonable amount of time.
+Another approach to linear optics is to pack more features known as degrees of freedom onto a single photon, and to increase the degree of control over them.
+It is possible to manipulate degrees of freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}.
+Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.
 
@@
 
-\section{Experimental implementation}\label{sec:expt}
+%\section{Experimental implementation}\label{sec:expt}
 
-Significant progress has been made in the experimental realisation of linear optics protocols, and have become standard and widespread. We now discuss some of these advances.
+%Significant progress has been made in the experimental realisation of 
+%linear optics protocols, and have become standard and widespread. We now 
+%discuss some of these advances.
 
-\subsection{State preparation}
+\section{State preparation}
 
@@
 
-\subsubsection{Single-photons}\label{sec:singlephotons}
+\subsection{Fock states}\label{sec:singlephotons}
 
@@
 
-Some commonly used nonlinear crystals for SPDC are beta barium borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled  potassium titanyl phosphate (PPKTP).
-Recently, techniques using bismuth triborate (BiBO) have improved to the extent of becoming one of the record-holders in single-photon production \cite{bib:WangChen16}.
+%Some commonly used nonlinear crystals for SPDC are beta barium borate 
+%(BBO), periodically poled lithium niobate (PPLN), and periodically poled  
+%potassium titanyl phosphate (PPKTP). Recently, techniques using bismuth 
+%triborate (BiBO) have improved to the extent of becoming one of the record-
+%holders in single-photon production \cite{bib:WangChen16}.
 
@@
 bib:237403,bib:Sweeney14}.
-An architecture that embeds the quantum dot in a micropillar cavity with the same resonant frequency as the dot exploits the Purcell effect to achieve higher single-photon production efficiency€ \cite{bib:Ding16,bib:213601}.
-Such resonant excitation of quantum dots overcomes the homogenous broadening of the excited state that causes degradation of photon purity and improving indistinguishability.
-Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of single photons produced by such a quantum dot, the same group was able to demonstrate quantum interference between five indistinguishable photons \cite{bib:WangChen16}.
+An architecture that embeds the quantum dot in a micropillar cavity uses a resonant effect to achieve higher production efficiency€ and better photon purity \cite{bib:Ding16,bib:213601}.
+Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of such photons, quantum interference was demonstrated between five indistinguishable photons \cite{bib:WangHe16}.
 
-\subsubsection{Einstein-Podolsky-Rosen (EPR) pairs}
+\subsection{Einstein-Podolsky-Rosen (EPR) pairs}
 
@@
 
-\subsubsection{Greenberger-Horne-Zeilinger (GHZ) states}
+\subsection{Greenberger-Horne-Zeilinger (GHZ) states}
 
@@
 
-\subsubsection{Cluster states}\label{section:cluster}
+\subsection{Cluster states}\label{section:cluster}
 
@@
 
-\begin{figure}[!htb]
+\begin{figure}
 \centering
-\includegraphics[width=0.3\columnwidth]{cluster_state}
-\caption{The representation of cluster states as a graph.
-Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on {\sc cphase} gates, the ordering of which is irrelevant.} \label{fig:cluster}
+\begin{subfigure}{.5\columnwidth}
+  \centering
+  \includegraphics[width=.6\columnwidth]{cluster_state}
+  \caption{}
+  \label{fig:cluster}
+\end{subfigure}%
+\begin{subfigure}{.5\columnwidth}
+  \centering
+  \includegraphics[width=.8\columnwidth]{fusion}
+  \caption{}
+  \label{fig:fusion}
+\end{subfigure}
+\caption{(a) The representation of cluster states as a graph.
+Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on {\sc cphase} gates, the ordering of which is irrelevant.
+(b) Fusion gates for joining smaller cluster states into larger ones.
+Both require only a single polarising beamsplitter, and waveplates.
+The type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, creating an edge between the remaining graphs.
+The type-I gate consumes one fewer photon, but requires number-resolved detection on the detected mode.
+The type-II gate requires only on/off photodetection, but consumes an additional photon.
+Thus, the type-I gate can be employed to fuse two Bell pairs into a 3-qubit cluster state, whereas the type-II gate will only grow clusters when beginning with at least 3 qubits per cluster.
+}
+\label{fig:test}
 \end{figure}
 
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[width=0.3\columnwidth]{cluster_state}
+%\caption{The representation of cluster states as a graph. Vertices
+% represent qubits initialised into the $\ket{+}$ state, while edges 
+%represent the application on {\sc cphase} gates, the ordering of which is 
+%irrelevant.} \label{fig:cluster}	
+%\end{figure}
+
 Unfortunately, implementing {\sc cphase} gates using linear optics is complicated and highly non-deterministic.
-A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell basis.
+A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell states.
 These operations fuse smaller cluster states, represented using polarisation encoding, into larger ones, consuming one (type-I fusion) or two (type-II fusion) photons in the process.
@@
 
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.4\columnwidth]{fusion}
-\caption{Fusion gates for joining smaller cluster states into larger ones.
-Both require only a single polarising beamsplitter, and waveplates.
-The type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, creating an edge between the remaining graphs.
-The type-I gate consumes one fewer photon, but requires number-resolved detection on the detected mode.
-The type-II gate requires only on/off photodetection, but consumes an additional photon.
-Thus, the type-I gate can be employed to fuse two Bell pairs into a 3-qubit cluster state, whereas the type-II gate will only grow clusters when beginning with at least 3 qubits per cluster.} \label{fig:fusion}
-\end{figure}
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[width=0.4\columnwidth]{fusion}
+%\caption{Fusion gates for joining smaller cluster states into larger ones. 
+%Both require only a single polarising beamsplitter, and waveplates. The 
+%type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, 
+%creating an edge between the remaining graphs. The type-I gate consumes one 
+%fewer photon, but requires number-resolved detection on the detected mode. 
+%The type-II gate requires only on/off photodetection, but consumes an 
+%additional photon. Thus, the type-I gate can be employed to fuse two Bell 
+%pairs into a 3-qubit cluster state, whereas the type-II gate will only grow 
+%clusters when beginning with at least 3 qubits per cluster.} %
+%\label{fig:fusion}	
+%\end{figure}
 
-\subsection{Linear optics networks}
+\section{Linear optical networks}\label{sec:network}
 
@@
 
-\subsubsection{Bulk-optics}
+\subsection{Bulk-optics}
 
@@
 
-\subsubsection{Waveguides}
+\subsection{Waveguides}
 
@@
 
-\subsubsection{Time-bins}\label{sec:timebins}
+\subsection{Time-bins}\label{sec:timebins}
 
@@
 
-\begin{figure}[!htb]
+\begin{figure}
 \centering
-\includegraphics[width=0.4\columnwidth]{full_architecture}
-\caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train.
+\begin{subfigure}{.5\columnwidth}
+  \centering
+  \includegraphics[width=0.9\columnwidth]{full_architecture}
+  \caption{}
+  \label{fig:FL_arch}
+\end{subfigure}%
+\begin{subfigure}{0.5\columnwidth}
+  \centering
+  \includegraphics[width=\columnwidth]{PBS_TB}
+  \caption{}
+  \label{fig:fusion}
+\end{subfigure}
+\caption{(a) A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train.
+(b) Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train.
+The PBS completely reflects (transmits) the vertical (horizontal) polarisations.
+The evolution of the four logical basis states, and their respective outputs, are shown explicitly.
+Writing out this PBS transformation in matrix form yields a permutation.
+Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.}
+\label{fig:PBS_TB}
+\end{figure}
+
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[width=0.4\columnwidth]{full_architecture}
+%\caption{A fibre-loop architecture for implementing arbitrary linear optics 
+%operations upon a time-bin-encoded pulse-train.
 %The source prepares the temporally encoded pulse-train, with time-bin 
@@
 %controlled beamsplitter operations.
-} \label{fig:FL_arch}	
-\end{figure}
+%} \label{fig:FL_arch}	
+%\end{figure}
 
@@
 
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.6\columnwidth]{PBS_TB}
-\caption{Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train.
-The PBS completely reflects (transmits) the vertical (horizontal) polarisations.
-The evolution of the four logical basis states, and their respective outputs, are shown explicitly.
-Writing out this PBS transformation in matrix form yields a permutation.
-Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.} \label{fig:PBS_TB}
-\end{figure}
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[width=0.6\columnwidth]{PBS_TB}
+%\caption{Mapping between two polarisation-encoded qubits undergoing a 
+%polarising beamsplitter (PBS) operation, and its equivalent representation 
+%using 4 time-bins in a pulse-train. The PBS completely reflects (transmits) 
+%the vertical (horizontal) polarisations. The evolution of the four logical 
+%basis states, and their respective outputs, are shown explicitly. Writing 
+%out this PBS transformation in matrix form yields a permutation. Taking 
+%this 
+%permutation and relabelling the modes, we obtain the time-bin 
+%transformation 
+%shown underneath -- a simple swap of two of the four time-bins.} 
+%\label{fig:PBS_TB}	
+%\end{figure}
 
@@
 
-\subsection{Photodetection}
+\section{Photodetection}
 
@@
 \subsection{Linear optical quantum computation (LOQC)}\label{sec:LOQC}
-The advancements in linear optics discussed in Section \ref{sec:expt}, quantum computation using linear optics have opened up avenues for implementation.
+The advancements in linear optics have opened up avenues for implementation.
 One of the key requirements is nonlinear couplings between the different optical modes.
@@
 Methods used include measurements and feedforwarding \cite{bib:KLM01}, and photon-atom interactions \cite{bib:Brod16}.
-All models for LOQC also require non-deterministic operations, which succeeds only sometime and have to be repeated.
-This can be challenging given the limitations of the optical systems.
+The former requires non-deterministic operations, which succeed only part of the time and have to be repeated.
+This can be challenging given the limited resources to begin with.
 Comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05}, hence we will focus on recent advances.
@@
 This might pose the greatest challenge yet for universal LOQC.
-Only a handful of experiments have been able to implement adaptive feedforward for the purposes of LOQC \cite{bib:Prevedel07,bib:Xiao-Song12,bib:Mikova12,bib:Zhao14}.
-The bottleneck is in the speed of modulation in the feedforward circuitry.
+The bottleneck is in the speed of modulation in the feedforward circuitry; only a handful of experiments have been able to implement adaptive feedforward for the purposes of LOQC \cite{bib:Prevedel07,bib:Xiao-Song12,bib:Mikova12,bib:Zhao14}.
 
@@
 \centering
-\includegraphics[width=0.5\columnwidth]{MORDOR}
+\includegraphics[width=0.4\columnwidth]{MORDOR}
 \caption{Architecture of the quantum Fourier transform interferometer for metrology using single-photon states.

### 2017-05-13 paper.tex
Revised intro

@@
 %%%
-Linear optics has seen a resurgence owing to its miniaturisation on-chip, and increase in production efficiency and quality of single photons.
-Time-bin encodings have also become feasible owing to fresh architecture, and processing capabilities.
-Theoretical efforts to find useful application beyond a full universal quantum computation has also bore fruit.
-A sampling task, known as {\sc bosonsampling} that is easily implemented using linear optics but is strongly believed to be a hard for a classical computer, has emerged.
-%%%%
+Linear optics has seen a resurgence for applications in quantum information processing owing to its miniaturisation on-chip, and increase in production efficiency and quality of single photons.
+Time-bin encodings have also become feasible owing to architectural breakthroughs, and new processing capabilities.
+Theoretical efforts have found new ways to implement universal quantum computations with linear optics requiring less resources, and to demonstrate the capabilities of linear optics without requiring a universal optical quantum computer.%%%%
 \end{abstract}
@@
 
-Technical advancements in linear optics have been made on many fronts that make it increasingly attractive for quantum computing applications.
-It is possible now to put single-photon sources and detectors together with linear-optical networks on a silica chip.
+Linear optics play a prominent role in quantum information processing.
+Photons make fantastic ``flying" qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}.
+In 2001, Knill, Laflamme and Milburn showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting \cite{bib:KLM01}.
+Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
+Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.
+
+The promises offered by linear optics have spearheaded many technical advancements.
+One of the major successes for linear optics is the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}.
 The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized.
-This increases the scalability of optical implementations of quantum information protocols.
-Having all components on chip reduces coupling losses which would be crucial for fault-tolerance.
-An optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
-Combined withthe relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.
+This has increased the scalability of optical implementations of quantum information protocols.
+Furthermore, it is now possible to have single-photon sources and detectors together with linear-optical networks on a silica chip \cite{bib:Sprengers11, bib:Silverstone14}.
+Having all components on chip reduces coupling losses which would be crucial for fault-tolerance \cite{bib:Li15}.
 
@@
 which are all maximally entangled and locally equivalent to one another.
-These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing.
+These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing \cite{bib:Kim01}.
 %\cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
 In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.~}successfully prepared only under certain measurement outcomes of auxiliary modes.
+Because the EPR qubits are not measured directly, they can be used subsequently.
 Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}.
@@
 Combining these chips with existing higher-efficiency sources and detectors will expand their capabilities.
-Loss can be mitigated by moving all components onto the same chip as the linear optical circuit \cite{bib:Sprengers11, bib:Silverstone14}.
+Loss can be mitigated by moving all components, {\it i.e.~}sources and detectors, onto the same chip as the linear optical circuit \cite{bib:Sprengers11, bib:Silverstone14}.
 What remains is to have fast feedforward also on chip.

### 2017-05-13 paper.tex
Revised intro

@@
 Photons make fantastic ``flying" qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}.
-In 2001, Knill, Laflamme and Milburn showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting \cite{bib:KLM01}.
+In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting \cite{bib:KLM01}.
 Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
@@
 Through developments in production, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
-Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical labs, and three photons have become the standard benchmark.
-Experiments using up to ten photons have been demonstrated.
-We have also seen the meteoric rise of quantum dots in the role for producing single photons.
-It is now possible to use a quantum dot to produce multiple single photons which are highly indistinguishable.
-Quantum dots produce single photons on demand, a significant advantage over SPDC which is an inherently probabilistic process.
+Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical labs, and three or four photons have become commonplace \cite{bib:Spagnolo12, bib:Tillmann13, bib:Spring13,bib:Broome13}.
+Experiments using up to ten photons have been demonstrated \cite{bib:WangChen16, bib:Chen17}.
+We have also seen the meteoric rise of quantum dots in the role for producing single photons \cite{bib:Ding16,bib:WangHe16, bib:213601}.
+They are a scalable source of single photons which are highly indistinguishable, and are produced on demand--a significant advantage over SPDC which is an inherently probabilistic process.
 
@@
 It is possible to manipulate degrees of freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}.
+Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}.
+Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.
 Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.
@@
 Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction}.
+In Section \ref{sec:state}, we recap the experimental breakthroughs in state preparation of single photons, and some entangled quantum states.
+This is followed by advances in linear optical networks, and photodectors in Sections \ref{sec:network} and \ref{sec:detector} respectively.
+Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, and quantum metrology.
 
@@
 
-\section{State preparation}
+\section{State preparation}\label{sec:state}
 
@@
 
-\section{Photodetection}
+\section{Photodetection}\label{sec:detector}
 

### 2017-05-13 paper.tex
Revision of Sections 6

@@
 
-A similar method to that of Laing and O'Brien \cite{bib:Laing12} uses coherent states instead of Fock states \cite{bib:Rahimi-Keshari13,bib:Heilmann15} to probe the interferometer.
+An alternative method uses coherent states to probe the interferometer \cite{bib:Rahimi-Keshari13,bib:Heilmann15} instead of Fock states.
 Such states are produced by a standard laser source, thus reducing experimental resources.
@@
 By scanning the phase shift $\phi$ and locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$.
-An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase-shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$.
+An elegant modification of this scheme removes the need for precise control of the phase-shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$.
 In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure, whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.
@@
 Both categories have seen major development recently in photon-number, with high fidelities.
-To-date, SPDC has been able to produce up to ten entangled photons \cite{bib:WangChen16,bib:Chen17}, and five-photon quantum interference has been reported using a quantum dot emitter in a microcavity \cite{bib:WangHe16}.
+To-date, SPDC has been able to produce up to ten entangled photons \cite{bib:WangChen16,bib:Chen17} that can be converted into indistinguishable photons, and a quantum dot emitter in a microcavity has produced five photons \cite{bib:WangHe16}.
 
@@
 
-Solid-state single photon sources come from semiconducting nanostructures and nitrogen valencies (NV) centers in diamond.
-Both types are versatile and efficient sources of single photons, however, the photons they produce have suffered from the lack of indistinguishability that is necessary for typical quantum information processing applications.
-Recent developments in the former have been very promising.
-Notably, much progress has been made using resonant excitation of quantum dots.
-Here, laser pulses are used to excite their electronic resonance and trigger the emission of single photons \cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
-bib:237403,bib:Sweeney14}.
-An architecture that embeds the quantum dot in a micropillar cavity uses a resonant effect to achieve higher production efficiency€ and better photon purity \cite{bib:Ding16,bib:213601}.
-Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of such photons, quantum interference was demonstrated between five indistinguishable photons \cite{bib:WangHe16}.
+Solid-state single photon sources are versatile and efficient sources of single photons, however, the photons they produce have suffered from the lack of indistinguishability that is necessary for typical quantum information processing applications.
+Recent developments using resonant excitation of quantum dots were able to overcome these limitations.
+Laser pulses are used to excite the electronic resonance of the quantum dots and trigger the emission of high quality single photons \cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
+bib:237403,bib:Sweeney14,bib:Ding16,bib:213601}.
+Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of such photons, quantum interference was demonstrated between five photons \cite{bib:WangHe16}.
 
@@
 Cluster states form another class of multiparty entangled states, and were conceived in the context of arrays of qubits with an Ising-type interaction \cite{bib:Briegel01}.
-
 These states can be represented as a graph, in which vertices are qubits initialized into the superposition state $\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, with {\sc cphase} operation applied between edges, as shown in Fig.~\ref{fig:cluster}.
@@
 The {\sc cphase} operations generate entanglement between the qubits, and because they commute, are independent of ordering.
+
 Cluster states are a resource state for a model of quantum computation known as measurement-based quantum computation (MBQC).
 Here, having such a state as a resource enables universal quantum computation using only single-qubit measurements \cite{bib:Raussendorf03}.
+In fact, only (X,Y)-plane measurements are needed \cite{bib:Mantri17}.
 Therefore, the preparation of such states is highly valuable, generating much interest in their efficient preparation.
@@
   \centering
-  \includegraphics[width=.6\columnwidth]{cluster_state}
+  \includegraphics[width=.5\columnwidth]{cluster_state}
   \caption{}
@@
   \centering
-  \includegraphics[width=.8\columnwidth]{fusion}
+  \includegraphics[width=.7\columnwidth]{fusion}
   \caption{}
@@
 
-Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing {\sc cphase} gates.
+Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing {\sc cphase} gates \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}.
+Experimentally, small photonic cluster states have been demonstrated using both SPDC \cite{bib:Walther05a,bib:Lu06,bib:Prevedel07,bib:Tokunaga08} and quantum dot sources \cite{bib:Schwartz16}.
+To this end, continuous variable cluster states have fared better as large cluster states containing more than 10,000 entangled modes are possible  \cite{bib:Yokoyama13}, with the caveat that it is difficult to address modes individually for processing.
 

### 2017-05-13 paper.tex
Section 7 revised
Subsections on “Bulk optics” and “waveguides” have been removed to save
space. Moreover, the advantages of integrated circuits have been
repeated in the intro already, and later in the LOQC section. Section 7
is now just time-bin loop-based architecture.

@@
 In Section \ref{sec:state}, we recap the experimental breakthroughs in state preparation of single photons, and some entangled quantum states.
-This is followed by advances in linear optical networks, and photodectors in Sections \ref{sec:network} and \ref{sec:detector} respectively.
+This is followed by advances in time-bin based architecture for linear optical networks, and photodectors in Sections \ref{sec:timebins} and \ref{sec:detector} respectively.
 Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, and quantum metrology.
@@
 Recent developments using resonant excitation of quantum dots were able to overcome these limitations.
-Laser pulses are used to excite the electronic resonance of the quantum dots and trigger the emission of high quality single photons \cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
-bib:237403,bib:Sweeney14,bib:Ding16,bib:213601}.
-Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of such photons, quantum interference was demonstrated between five photons \cite{bib:WangHe16}.
+Laser pulses are used to excite the electronic resonance of the quantum dots and trigger the emission of high quality single photons \cite{bib:Ding16,bib:213601,bib:Ates09, bib:Dirk10,bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
+bib:237403,bib:Sweeney14}. Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of such photons, quantum interference was demonstrated between five photons \cite{bib:WangHe16}.
 
@@
 
-\section{Linear optical networks}\label{sec:network}
+%\section{Linear optical networks}\label{sec:network}
 
-Numerous experimental implementations of various linear optics protocols have been demonstrated, using a variety of architectures.
-The main contenders considered to date are: bulk-optics; waveguides; and time-bin encoding.
+%\subsection{Waveguides}
 
-\subsection{Bulk-optics}
+%Numerous experimental implementations of various linear optics protocols 
+%have been demonstrated, using a variety of architectures. 
+%The main contenders considered to date are: bulk-optics; waveguides; and 
+%time-bin encoding.
+%The early implementations of linear optics protocols relied on bulk-optics 
+%implementations, in which a circuit is decomposed into a discrete 
+%arrangement of optical components, specifically beamsplitters and phase-
+%shifters. This corresponds to a direct implementation of the Reck \emph{et 
+%al.~}decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate 
+%decompositions. Although this approach is effective and conceptually 
+%straightforward, it is highly impractical for large interferometers. For 
+%example, the implementation of a 100-mode interferometer requires on the 
+%order of 10,000 discrete optical elements, which must all be simultaneously 
+%aligned with interferometric stability, a highly experimentally challenging 
+%problem, not to mention incredibly physically large.
 
-The early implementations of linear optics protocols relied on bulk-optics implementations, in which a circuit is decomposed into a discrete arrangement of optical components, specifically beamsplitters and phase-shifters.
-This corresponds to a direct implementation of the Reck \emph{et al.~}decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate decompositions.
+%Alternately, integrated waveguide devices can be employed to implement 
+%identical decompositions by etching the modes into paths in an optical 
+%chip, where evanescent coupling between closely neighbouring modes 
+%implements beamsplitter operations. Such devices are extremely compact, 
+%allowing the miniaturisation of large numbers of optical elements. 
+%Importantly, such devices are extremely optically stable, mitigating the 
+%need for any kind of dynamic stabilisation
 
-Although this approach is effective and conceptually straightforward, it is highly impractical for large interferometers.
-For example, the implementation of a 100-mode interferometer requires on the order of 10,000 discrete optical elements, which must all be simultaneously aligned with interferometric stability, a highly experimentally challenging problem, not to mention incredibly physically large.
-
-\subsection{Waveguides}
-
-Alternately, integrated waveguide devices can be employed to implement identical decompositions by etching the modes into paths in an optical chip, where evanescent coupling between closely neighbouring modes implements beamsplitter operations.
-Such devices are extremely compact, allowing the miniaturisation of large numbers of optical elements.
-Importantly, such devices are extremely optically stable, mitigating the need for any kind of dynamic stabilisation
-
-\subsection{Time-bins}\label{sec:timebins}
+\section{Time-bin loop-based architecture for linear optical networks}\label{sec:timebins}
 
@@
 
-\begin{figure}[!htb]
+%\begin{figure}[!htb]
+%\centering
+%\includegraphics[width=0.4\columnwidth]{MORDOR}
+%\caption{Architecture of the quantum Fourier transform interferometer for 
+%metrology using single-photon states. QFT: Quantum Fourier transform 
+%circuit, and $\varphi_k=(k-1)\varphi$. Single photons are injected into the 
+%input modes on the left-hand-side, and a $N$-fold coincidence measurement 
+%is conducted at the output on the right-hand-side.} \label{fig:MORDOR}	
+%\end{figure}
+
+\begin{figure}
 \centering
-\includegraphics[width=0.4\columnwidth]{MORDOR}
-\caption{Architecture of the quantum Fourier transform interferometer for metrology using single-photon states.
+\begin{subfigure}{.5\columnwidth}
+  \centering
+  \includegraphics[width=0.5\columnwidth]{phE}
+  \caption{}
+   \label{fig:MZ}
+\end{subfigure}%
+\begin{subfigure}{0.5\columnwidth}
+  \centering
+  \includegraphics[width=0.8\columnwidth]{MORDOR}
+  \caption{}
+  \label{fig:fusion}
+\end{subfigure}
+\caption{(a) A schematic diagram of the Mach-Zehnder interferometer comprising of two 50/50 beamsplitters with a phase shift $\varphi$ in one of its two paths.	(b) Architecture of the quantum Fourier transform interferometer for metrology using single-photon states.
 QFT: Quantum Fourier transform circuit, and $\varphi_k=(k-1)\varphi$.
-Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.} \label{fig:MORDOR}
+Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.}
+\label{fig:MORDOR}
 \end{figure}

### 2017-05-14 paper.tex
Revised subsections 6.3 and 9.3.

@@
 This has been a subject matter covered in detail by another review \cite{bib:JW12}.
+To date, six- \cite{bib:Lu06,bib:Zhang15}, eight- \cite{bib:Huang11,bib:Yao12}, and ten-photons \cite{bib:WangChen16,bib:Chen17} GHZ states have been produced.
+
+The GHZ state is also known as the NOON state, because it is written as
+\begin{align}
+\ket{\psi^{\rm (NOON)}_n}=\frac{1}{\sqrt{2}}(\ket{N,0}+\ket{0,N})\ ,
+\end{align}
+in the second quantization representation. This is the notation adopted by the community working in quantum metrology (see Section \ref{subsec:metrology}).
 
@@
 
-\subsection{Quantum metrology}
+\subsection{Quantum metrology}\label{subsec:metrology}
 An archetypal task for quantum metrology is the following: Given a Mach-Zedner interferometer, with an unknown phase shift of magnitude $\varphi$ inserted in one of the two paths (see Fig.
 \ref{fig:MZ}), can one deduce $\varphi$ via a judicious use of quantum states and measurements with a higher sensitivity than that of a completely classical interferometer?
-It is well-known that one indeed can, and the standard deviation, $\Delta\varphi$, after $N$ trials using quantum estimation is
-\begin{align}
-\Delta\varphi=\frac{1}{N} \ ,	
-\end{align}
-which gets a $\sqrt{N}$ improvement over classical phase estimation.
+Indeed, one can, and the standard deviation, $\Delta\varphi$, after $N$ trials using quantum estimation is $\Delta\varphi=1/N$, which gets a $\sqrt{N}$ improvement over classical phase estimation.
 As this sensitivity is also a fundamental limit arising from Heisenberg's uncertainty principle; we cannot measure definitively the phase, it is known as the Heisenberg limit.
-Most famously, a family of entangled states known as NOON states achieve this limit using $N$ photons in a single trial.
-A NOON state is a superposition state in which $N$ photons are either in the first or second path:
-\begin{align}
-\ket{\psi^{\rm (NOON)}_n}=\frac{1}{\sqrt{2}}(\ket{N,0}+\ket{0,N})\ .	
-\end{align}
+Most famously, NOON states achieve this limit using $N$ photons in a single trial.
 Many reviews have been written for quantum metrology and Heisenberg-limited quantum phase estimation \cite{bib:Giovannetti04,bib:Dowling08,bib:Giovannetti11} so we will not dwell on the history of this application.

### 2017-05-14 paper.tex
more revisions

@@
 \ref{fig:MORDOR}).
-By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve
-\begin{align}
-\Delta \varphi=\mathcal{O}\left(\frac{1}{N^{3/2}}\right) \ ,	
-\end{align}
-with just a string of $N$ single photons, one photon per mode, for up to at least $N=25$ modes.
+By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve $\Delta \varphi=\mathcal{O}(N^{-3/2})$ with just a string of $N$ single photons, one photon per mode, for up to at least $N=25$ modes.
 

### 2017-05-14 paper.tex
Added section on bosonsampling, and overall revisions.

@@
 \centering
-\includegraphics[width=0.5\columnwidth]{reck}
+\includegraphics[width=0.4\columnwidth]{reck}
 \caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
@@
 However, owing to manufacturing imperfections, a precise characterization of these devices may still be needed post-production.
-One approach for achieving this is via quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
+One approach for achieving this is via quantum process tomography.
+%\cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
 However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterize the network, with exponential overhead, becoming impractical for large optical networks which can contain hundreds of modes using present-day technology \cite{bib:Harris16}.
-To mitigate this problem, alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.
+To mitigate this problem, alternative characterization protocols have been developed.
 
@@
 To characterize these numbers, one can do so by injecting one- and two-photon states into the network with correlated photon detection \cite{bib:Laing12}.
-With some mathematical simplifications, the first row and first column elements can be reduced to real numbers, and then found via one-photon transmissions.
-The remaining $r_{ij}$ and $\theta_{ij}$ parameters can then be written in terms of these real parameters, and the visibility of two-photon inputs.
-%
+With some mathematical simplifications, the parameters can be solved for using the one-photon transmissions, and the visibility of two-photon inputs.
 %
@@
 Such states are produced by a standard laser source, thus reducing experimental resources.
-The $r_{jk}$ terms are found by the square root of the ratios of output intensities at the $k$th port to the input intensity at the $j$th port.
-The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha_1}\ket{\alpha_2}$ created by splitting a single coherent state on a 50-50 beamsplitter, and then imparting a relative phase, $\phi$, between them.
-The states $\ket{\alpha_1}$ and $\ket{\alpha_2}$ are input into port 1, and $j$ respectively.
-The output intensity at the $k$th port is then
+The $r_{jk}$ terms can be calculated from the ratios of output intensities at the $k$th port to the input intensity at the $j$th port.
+The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha}\ket{\alpha e^{\phi}}$.
+When the states are injected into ports 1, and $j$ respectively, the output intensity at the $k$th port is
 \begin{align}
@@
 By scanning the phase shift $\phi$ and locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$.
-An elegant modification of this scheme removes the need for precise control of the phase-shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$.
+An elegant modification of this scheme removes the need for precise control of the phase-shift $\phi$ by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$ \cite{bib:Heilmann15}.
 In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure, whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.
@@
 Sources of single photons for applications in quantum information processing can be separated into two main categories: those produced by spontaneous parametric down-conversion (SPDC), and those by solid-state emitters in a cavity.
-Both categories have seen major development recently in photon-number, with high fidelities.
-To-date, SPDC has been able to produce up to ten entangled photons \cite{bib:WangChen16,bib:Chen17} that can be converted into indistinguishable photons, and a quantum dot emitter in a microcavity has produced five photons \cite{bib:WangHe16}.
+To-date, SPDC has been able to produce up to ten entangled photons \cite{bib:WangChen16,bib:Chen17} that can in turn be converted into indistinguishable photons, and a quantum dot emitter in a microcavity has produced five photons \cite{bib:WangHe16}.
 
-In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ non-linearity is pumped with a strong coherent state (i.e laser source) and with a small probability, the pump beam is absorbed by the crystal to produce two beams of lower energy known as the signal and idler.
+In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ non-linearity is pumped with a laser source and with a small probability, the pump beam is absorbed by the crystal to produce two beams of lower energy known as the signal and idler.
 Owing to conservation of energy and momentum, the two beams have spatio-temporal correlations that can be engineered to produce twin-beam states with perfect  photon number correlation, of the form
@@
 Recent developments using resonant excitation of quantum dots were able to overcome these limitations.
-Laser pulses are used to excite the electronic resonance of the quantum dots and trigger the emission of high quality single photons \cite{bib:Ding16,bib:213601,bib:Ates09, bib:Dirk10,bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
-bib:237403,bib:Sweeney14}. Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of such photons, quantum interference was demonstrated between five photons \cite{bib:WangHe16}.
+Laser pulses are used to excite the electronic resonance of the quantum dots and trigger the emission of high quality single photons \cite{bib:WangHe16}
+%\cite{bib:Ding16,bib:213601,bib:Ates09, bib:Dirk10,bib:
+%1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
+%bib:237403,bib:Sweeney14,bib:WangHe16}.
 
@@
 \begin{align}
-\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \ {\rm and} \\
-\ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
+\ket{0}_A\ket{0}_B \pm \ket{1}_A\ket{1}_B, \ {\rm and} \ \ket{1}_A\ket{0}_B \pm \ket{0}_A\ket{1}_B \ ,
 \end{align}
@@
 \begin{align}
-\ket{\psi^{\rm (NOON)}_n}=\frac{1}{\sqrt{2}}(\ket{N,0}+\ket{0,N})\ ,
+\ket{\psi^{\rm (NOON)}_n}=\frac{1}{\sqrt{2}}(\ket{n,0}+\ket{0,n})\ ,
 \end{align}
-in the second quantization representation. This is the notation adopted by the community working in quantum metrology (see Section \ref{subsec:metrology}).
+in the second quantization representation. This notation is commonly used in quantum metrological applications.
 
@@
 Unfortunately, implementing {\sc cphase} gates using linear optics is complicated and highly non-deterministic.
-A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell states.
+A major improvement upon this is to use fusion gates-rotated polarising beamsplitters, which implement projections onto the Bell states.
 These operations fuse smaller cluster states, represented using polarisation encoding, into larger ones, consuming one (type-I fusion) or two (type-II fusion) photons in the process.
@@
   \centering
-  \includegraphics[width=0.9\columnwidth]{full_architecture}
+  \includegraphics[width=0.7\columnwidth]{full_architecture}
   \caption{}
@@
   \centering
-  \includegraphics[width=\columnwidth]{PBS_TB}
+  \includegraphics[width=0.8\columnwidth]{PBS_TB}
   \caption{}
@@
 \begin{align}
-\hat\Pi_\text{off} &= \hat\Pi_0, \nonumber \\
-\hat\Pi_\text{on} &= \hat{I} - \hat\Pi_\text{on}\ .
+\hat\Pi_\text{off} = \hat\Pi_0, \ {\rm and} \ \hat\Pi_\text{on} = \hat{I} - \hat\Pi_\text{on}\ .
 \end{align}
-Detailed reviews have been written about these detectors \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few notable examples here.
+Detailed reviews have been written about these detectors \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few important examples.
 
@@
 This avalanche of electrons generate a current that can be measured.
-APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in a broad spectrum of wavelengths; from the visible to near-infrared range
+APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in a broad spectrum of wavelengths.
 % A downside to using APD is their deadtime. This is a period of time 
@@
 %deadtime and contributes to photon loss in an APD.
-Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector that has recently become commercially available.
-This detector uses a narrow superconducting wire that carries a current just below the critical current density, above which the superconducting wire would undergo a phase change back to its normal resistance.
-This happens when the SNSPD absorbs an incident photon, and the current in the wire would then by-pass it to go through the neighboring region which is at a lower resistance.
-The voltage spike that ensues is measured to give a photon number count.
+Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector.
+This detector operates in its superconducting phase just below the critical density, and it phase changes back to normal when a photon is absorbed.
+This causes a spike in current around it, which, when detected, would indicate the absorption of the photon.
 
@@
 Last, PNR detectors can be created by connecting many non-PNR detectors in parallel to one another, and summing the signals at the output.
-Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Afek09,bib:Chrapkiewicz14,bib:Chen17}.
+For instance, like in the theoretical proposal of \cite{bib:Sperling12}.
+Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Eraerds07,bib:Afek09,bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Chen17}.
 
-The dominant challenge facing the experimental implementation of both types of detectors is inefficiency due to loss, which results in higher photon-number being confused as having lower photon-number.
-In some protocols, such as type-II fusion, which relies on coincidence detection, inefficiency is not problematic.
-However, in most applications, including type-I fusion, this is highly problematic as photon-number confusion results in decoherence via projecting onto the wrong photon-number, unknown to the observer.
-Other common problems that plague these detectors are dark counts which add spurious counts from the background.
-APDs suffer from dead-time which is a period of time following a detection event during which it is inactive.
-In applications requiring feedforwarding, this is problematic.
-Although TESs are great detectors, they are expensive because they require cryogenic equipment to function.
-The multiplexed SNSPDs suffer from the same constrain and also from low quantum efficiencies.
-While spatially multiplexed APDs are relatively cheap, they suffer from spurious counts known as crosstalk that arises from avalanches triggered by electrons launched from neighboring APDs \cite{bib:Eraerds07,bib:Afek09,bib:Kalashnikov12}.
-Given the important role of detectors in linear optical quantum computation (see Section \ref{sec:LOQC}), more could be done to improve them.
+%The dominant challenge facing the experimental implementation of both 
+%types of detectors is inefficiency due to loss, which results in 
+%higher photon-number being confused as having lower photon-number. In 
+%some protocols, such as type-II fusion, which relies on coincidence 
+%detection, inefficiency is not problematic. However, in most 
+%applications, including type-I fusion, this is highly problematic as 
+%photon-number confusion results in decoherence via projecting onto 
+%the wrong photon-number, unknown to the observer. Other common 
+%problems that plague these detectors are dark counts which add 
+%spurious counts from the background. APDs suffer from dead-time which 
+%is a period of time following a detection event during which it is 
+%inactive. In applications requiring feedforwarding, this is 
+%problematic. Although TESs are great detectors, they are expensive 
+%because they require cryogenic equipment to function. The multiplexed 
+%SNSPDs suffer from the same constrain and also from low quantum 
+%efficiencies. While spatially multiplexed APDs are relatively cheap, 
+%they suffer from spurious counts known as crosstalk that arises from 
+%avalanches triggered by electrons launched from neighboring APDs 
+%\cite{bib:Eraerds07,bib:Afek09,bib:Kalashnikov12}. Given the 
+%important role of detectors in linear optical quantum computation 
+%(see Section \ref{sec:LOQC}), more could be done to improve them.
 
@@
 \subsection{Boson-sampling}\label{sec:bosonsampling}
-\sihui{Peter to do this.}
+
+The difficulty in producing nonlinear operations required for universal LOQC led researchers to seek out alternative ways for demonstrating its power in the near term.
+{\sc Bosonsampling} is the result of such an effort.
+It is a restricted model of non-universal quantum computation \cite{bib:Aaronson11} that constitutes sampling the photocounts from the probability distribution of identical bosons scattered by a passive linear optical interferometer.
+While not universal, the {\sc bosonsampling} scheme is strongly believed to implement a classically hard task.
+Consider such a circuit of $m$ input (and output) modes that is injected with $n$ indistinguishable single photons such that $m\sim \mathcal{O}(n^2)$.
+Then, the boson sampling task consists of generating a sample from the probability distribution of single-photon measurements at the output of the circuit.
+The probability of detecting a $s_j$ photons at the $j$th output mode is
+\begin{align}
+p(s_1,\ldots,s_m)=\frac{{\rm Per}(U_S)}{s_1!\ldots s_n!} \ ,	
+\end{align}
+where ${\rm Per}$ denotes the permanent of a matrix, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times.
+The appearance of the permanent, which is of \#P complexity, in this statistics contributes to the hardness of the boson sampling problem.
+It is also known to be as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.3\columnwidth]{BS_model}
+\caption{The Boson-Sampling model. A string of n single
+photons is prepared in m optical modes. They are evolved
+via a passive interferometer $U$. Finally the photon-statistics
+are sampled from the distribution $p(s_1,\ldots,s_m)$.
+} \label{fig:FL_arch}	
+\end{figure}
+
+ Owing to the simplicity of {\sc BosonSampling} and its overarching implications for computer science, multiple experiments were reported shortly after its theoretical conception \cite{bib:Tillmann13,bib:Spring13, bib:Broome13,bib:Crespi13}.
+A recent experiment showed a {\sc bosonsampling} machine beating an early computer \cite{bib:WangHe16}.
+{\sc BosonSampling} has piqued so much interest, that a complete discussion would make up its own review, so we shall only outline some main developments here.
+One variant, known as scattershot {\sc bosonsampling}, proposes using pumped SPDC heralded photon sources to increase the rate of generating input photons \cite{bib:Lund14,bib:Bentivegna15}.
+Others varied the source input to cat-states \cite{bib:Rohde15} and thermal states \cite{bib:Tamma14_thermal} .
+An exciting modification allows the determination of molecular vibronic spectra \cite{bib:Huh15}, a task that goes beyond demonstrating a computationally hard task.
+
+Certifying that a {\sc bosonsampling} task has been correctly performed is non-trivial.
+Some efforts look into discriminating between a valid {\sc bosonsampling} and a uniform distributions \cite{bib:Gogolin13,bib:Aaronson13}.
+Another shows how to discriminate data arising from either indistinguishable or distinguishable photons \cite{bib:Spagnolo14,bib:Carolan14}.
+More general benchmark standards have also been instituted \cite{bib:Walschaeprs16}.
+Another approach to verify that the interferometer is behaving as expected is to make use of suppression laws \cite{bib:Tichy14} together with fully reconfigurable optical circuits.
+When the circuits are tuned to implement certain unitary matrices, specific input and output combinations are suppressed \cite{bib:Crespi16}.
+Last but not least, a bound for the transition amplitudes for {\sc bosonsampling} indicates that an approximation algorithm for the permanent is possible \cite{bib:Yung16}.
+Such an algorithm can help with verifying the sampling distribution, but their proof does not construct the algorithm needed for this to happen.
+
+As experimental imperfections threaten the scalability of {\sc bosonsampling}, there have been efforts to look into its error tolerance \cite{bib:Rohde12_tol}, fault-tolerance \cite{bib:Leverrier15}, and experimental artefacts \cite{bib:Shchesnobich14,bib:Tamma16}.
+Some works have resulted in interesting connections to exotic mathematical entities like immanants \cite{bib:Tan2013,bib:deGuise2014} and the multi-dimensional permanent \cite{bib:Tichy15}.
+A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14} seems particularly attractive in terms of robustness \cite{bib:Motes15}.
 
@@
 \ref{fig:MZ}), can one deduce $\varphi$ via a judicious use of quantum states and measurements with a higher sensitivity than that of a completely classical interferometer?
-Indeed, one can, and the standard deviation, $\Delta\varphi$, after $N$ trials using quantum estimation is $\Delta\varphi=1/N$, which gets a $\sqrt{N}$ improvement over classical phase estimation.
-As this sensitivity is also a fundamental limit arising from Heisenberg's uncertainty principle; we cannot measure definitively the phase, it is known as the Heisenberg limit.
+Indeed, one can, and the standard deviation, $\Delta\varphi$, after $N$ trials using quantum estimation is $\Delta\varphi=1/N$, which gets a factor of $\sqrt{N}$ improvement over classical phase estimation.
+As this sensitivity is also a fundamental limit arising from Heisenberg's uncertainty principle, {\it i.e.} we cannot measure definitively the phase, it is known as the Heisenberg limit.
 Most famously, NOON states achieve this limit using $N$ photons in a single trial.
 Many reviews have been written for quantum metrology and Heisenberg-limited quantum phase estimation \cite{bib:Giovannetti04,bib:Dowling08,bib:Giovannetti11} so we will not dwell on the history of this application.
-Instead, we will discuss a new paradigm for quantum metrology that has arisen from our understanding of Boson-sampling.
+Instead, we will discuss new paradigms for quantum metrology that have been made possible by the aforementioned advancements in linear optics.
 
@@
  As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling is readily available, but executes a task that is believed to be hard classically.
-Surprisingly, an entanglement between a large number of spatial modes is possible with single photons in a passive linear optical device.
-This so-called number-path entanglement can be harnessed for quantum metrology without the use of entangled states like the NOON state \cite{bib:Motes15}.
+Surprisingly, an entanglement between a large number of path labels is possible with single photons in a passive linear optical device.
+Motes {\it et al.~} harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15}.
 Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig.
 \ref{fig:MORDOR}).
-By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve $\Delta \varphi=\mathcal{O}(N^{-3/2})$ with just a string of $N$ single photons, one photon per mode, for up to at least $N=25$ modes.
+By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve $\Delta \varphi=\mathcal{O}(N^{-3/2})$ using a coincidence measurement with just a string of $N$ single photons, for up to at least $N=25$ modes.
+
+ Quantum multi-parameter estimation is the extension of quantum phase estimation to sense multiple phases in a multi-arm inetrferometer \cite{bib:Szczykulska16}.
+Theoretical work has shown that it is favorable to probe all phases simultaneously rather than individually \cite{bib:Baumgratz16,bib:Ciampini16}, and it remains to realize existing proposals for implememtation \cite{bib:Spagnolo12}.
+Nonetheless, for a Heisenberg-limited sensitivity, entangled states and joint measurements across modes are likely to be required.
 

### 2017-05-17 (PR final edits) linear_optics_review/paper.tex
peter final edits

--- 2017-05-14 paper.tex
@@
 \begin{align}
-p(s_1,\ldots,s_m)=\frac{{\rm Per}(U_S)}{s_1!\ldots s_n!} \ ,	
+p(s_1,\ldots,s_m)=\frac{|{\rm Per}(U_S)|^2}{s_1!\ldots s_n!} \ ,	
 \end{align}
-where ${\rm Per}$ denotes the permanent of a matrix, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times.
-The appearance of the permanent, which is of \#P complexity, in this statistics contributes to the hardness of the boson sampling problem.
-It is also known to be as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
+where ${\rm Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times.
+The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson sampling problem.
+Note that the number of configurations $|S|=\binom{n+m-1}{n}$ in the output superposition scales exponentially with $m$.
+For this reason, the boson sampler does not let us \emph{calculate} matrix permanents, as this would require knowing individual amplitudes with high precision, which would require an exponential number of samples.
+Rather, the boson sampler samples across a distribution of permanents without actually revealing any of them to the experimenter.
+Nonetheless, this is a classically intractable problem.
+It is also known that boson sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
 
@@
 {\sc BosonSampling} has piqued so much interest, that a complete discussion would make up its own review, so we shall only outline some main developments here.
-One variant, known as scattershot {\sc bosonsampling}, proposes using pumped SPDC heralded photon sources to increase the rate of generating input photons \cite{bib:Lund14,bib:Bentivegna15}.
+One variant, known as scattershot {\sc bosonsampling}, proposes using pumped SPDC heralded photon sources to increase the rate of generating input photons \cite{bib:Lund14,bib:Bentivegna15}, by inputting an SPDC source into \emph{every} mode rather than just the first $n$, thereby boosting the probability of preparing the desired $n$ photons.
 Others varied the source input to cat-states \cite{bib:Rohde15} and thermal states \cite{bib:Tamma14_thermal} .

### 2017-06-29 paper.tex
Created new folder for reports.

@@
 %ddress]{revtex4}
+
 \documentclass[times,final]{elsarticle}
@@
 \usepackage{hyperref,mathrsfs,amsmath,amssymb,latexsym}
-
 \newcommand{\bra}[1]{\langle#1|}
@@
 Linear optics play a prominent role in quantum information processing.
-Photons make fantastic ``flying" qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}.
+Photons make fantastic `flying' qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}.
 In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting \cite{bib:KLM01}.
@@
 Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}.
-Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.
+\sihui {Some of them support new functionalities like secure delegated quantum computations \cite{bib:Barz12,bib:Fisher14}}.
+Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.
 Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.
@@
 
-If the linear optical transformations can be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
+If the linear optical transformations \sihui{is to} be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
 This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.
@@
 
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[width=0.3\columnwidth]{cluster_state}
-%\caption{The representation of cluster states as a graph. Vertices
-% represent qubits initialised into the $\ket{+}$ state, while edges 
-%represent the application on {\sc cphase} gates, the ordering of which is 
-%irrelevant.} \label{fig:cluster}	
-%\end{figure}
-
 Unfortunately, implementing {\sc cphase} gates using linear optics is complicated and highly non-deterministic.
@@
 To this end, continuous variable cluster states have fared better as large cluster states containing more than 10,000 entangled modes are possible  \cite{bib:Yokoyama13}, with the caveat that it is difficult to address modes individually for processing.
-
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[width=0.4\columnwidth]{fusion}
-%\caption{Fusion gates for joining smaller cluster states into larger ones. 
-%Both require only a single polarising beamsplitter, and waveplates. The 
-%type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, 
-%creating an edge between the remaining graphs. The type-I gate consumes one 
-%fewer photon, but requires number-resolved detection on the detected mode. 
-%The type-II gate requires only on/off photodetection, but consumes an 
-%additional photon. Thus, the type-I gate can be employed to fuse two Bell 
-%pairs into a 3-qubit cluster state, whereas the type-II gate will only grow 
-%clusters when beginning with at least 3 qubits per cluster.} %
-%\label{fig:fusion}	
-%\end{figure}
-
-%\section{Linear optical networks}\label{sec:network}
-
-%\subsection{Waveguides}
-
-%Numerous experimental implementations of various linear optics protocols 
-%have been demonstrated, using a variety of architectures. 
-%The main contenders considered to date are: bulk-optics; waveguides; and 
-%time-bin encoding.
-%The early implementations of linear optics protocols relied on bulk-optics 
-%implementations, in which a circuit is decomposed into a discrete 
-%arrangement of optical components, specifically beamsplitters and phase-
-%shifters. This corresponds to a direct implementation of the Reck \emph{et 
-%al.~}decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate 
-%decompositions. Although this approach is effective and conceptually 
-%straightforward, it is highly impractical for large interferometers. For 
-%example, the implementation of a 100-mode interferometer requires on the 
-%order of 10,000 discrete optical elements, which must all be simultaneously 
-%aligned with interferometric stability, a highly experimentally challenging 
-%problem, not to mention incredibly physically large.
-
-%Alternately, integrated waveguide devices can be employed to implement 
-%identical decompositions by etching the modes into paths in an optical 
-%chip, where evanescent coupling between closely neighbouring modes 
-%implements beamsplitter operations. Such devices are extremely compact, 
-%allowing the miniaturisation of large numbers of optical elements. 
-%Importantly, such devices are extremely optically stable, mitigating the 
-%need for any kind of dynamic stabilisation
 
@@
   \caption{}
-  \label{fig:fusion}
+  \label{fig:PBS_TB}
 \end{subfigure}
@@
 Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.}
-\label{fig:PBS_TB}
 \end{figure}
-
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[width=0.4\columnwidth]{full_architecture}
-%\caption{A fibre-loop architecture for implementing arbitrary linear optics 
-%operations upon a time-bin-encoded pulse-train.
-%The source prepares the temporally encoded pulse-train, with time-bin 
-%separation $\tau$.
-%The pulse-train then enters a dual-loop configuration. The inner loop has 
-%%length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is 
-%the number of optical modes). The architecture is controlled via three 
-%dynamically controlled beamsplitters. The first and last need only be on/
-%off switches, whose sole purpose is to couple in the prepared pulse-
-%train, keep it within the outer loop for the required duration, and then 
-%couple out of the outer loop, yielding the transformed pulse-train. The 
-%central beamsplitter must be able to implement arbitrary classically-
-%controlled beamsplitter operations.
-%} \label{fig:FL_arch}	
-%\end{figure}
 
@@
 
-PNR detectors are a wonderful addition to the toolbox of linear optics.
+PNR detectors are a wonderful addition to the \sihui{linear optical} toolbox.
 A notable example is the superconducting transition edge sensor (TES) which has an extremely high quantum efficiency.
@@
 For instance, like in the theoretical proposal of \cite{bib:Sperling12}.
-Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Eraerds07,bib:Afek09,bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Chen17}.
+Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Heilmanndc15}.
 
@@
 Consider such a circuit of $m$ input (and output) modes that is injected with $n$ indistinguishable single photons such that $m\sim \mathcal{O}(n^2)$.
-Then, the boson sampling task consists of generating a sample from the probability distribution of single-photon measurements at the output of the circuit.
-The probability of detecting a $s_j$ photons at the $j$th output mode is
+Then, the boson-sampling task consists of generating a sample from the probability distribution of single-photon measurements at the output of the circuit.
+The probability of detecting $s_j$ photons at the $j$th output mode is
 \begin{align}
-p(s_1,\ldots,s_m)=\frac{{\rm Per}(U_S)}{s_1!\ldots s_n!} \ ,	
+p(s_1,\ldots,s_m)=\frac{|{\rm Per}(U_S)|^2}{s_1!\ldots s_n!} \ ,	
 \end{align}
-where ${\rm Per}$ denotes the permanent of a matrix, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times.
-The appearance of the permanent, which is of \#P complexity, in this statistics contributes to the hardness of the boson sampling problem.
-It is also known to be as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
+where ${\rm Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first $n$ columns and repeating its $j$th row $s_j$ times.
+The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson-sampling problem.
+Note that the number of configurations $|S|=\binom{n+m-1}{n}$ in the output superposition scales exponentially with $m$.
+For this reason, the boson sampler does not let us \emph{calculate} matrix permanents, as this would require knowing individual amplitudes with high precision, which would require an exponential number of samples.
+Rather, the boson sampler samples across a distribution of permanents without actually revealing any of them to the experimenter.
+Nonetheless, this is a classically intractable problem.
+It is also known that boson-sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
 
@@
 are sampled from the distribution $p(s_1,\ldots,s_m)$.
-} \label{fig:FL_arch}	
+} \label{fig:BosonSampling}	
 \end{figure}
@@
 Some works have resulted in interesting connections to exotic mathematical entities like immanants \cite{bib:Tan2013,bib:deGuise2014} and the multi-dimensional permanent \cite{bib:Tichy15}.
-A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14} seems particularly attractive in terms of robustness \cite{bib:Motes15}.
+A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14} seems particularly attractive in terms of robustness \cite{bib:Motes15_timebin}.
 
@@
 Surprisingly, an entanglement between a large number of path labels is possible with single photons in a passive linear optical device.
-Motes {\it et al.~} harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15}.
+Motes {\it et al.~}harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15_LOQM}.
 Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig.
@@
 
- Quantum multi-parameter estimation is the extension of quantum phase estimation to sense multiple phases in a multi-arm inetrferometer \cite{bib:Szczykulska16}.
-Theoretical work has shown that it is favorable to probe all phases simultaneously rather than individually \cite{bib:Baumgratz16,bib:Ciampini16}, and it remains to realize existing proposals for implememtation \cite{bib:Spagnolo12}.
+ Quantum multi-parameter estimation is the extension of quantum phase estimation to sense multiple phases in a multi-arm interferometer \cite{bib:Szczykulska16}.
+Theoretical work has shown that it is favorable to probe all phases simultaneously rather than individually \cite{bib:Baumgratz16,bib:Ciampini16}, and it remains to realize existing proposals for implementation \cite{bib:Spagnolo12}.
 Nonetheless, for a Heisenberg-limited sensitivity, entangled states and joint measurements across modes are likely to be required.
-
- %\begin{figure}[!htb]
-%\centering
-%\includegraphics[width=0.4\columnwidth]{MORDOR}
-%\caption{Architecture of the quantum Fourier transform interferometer for 
-%metrology using single-photon states. QFT: Quantum Fourier transform 
-%circuit, and $\varphi_k=(k-1)\varphi$. Single photons are injected into the 
-%input modes on the left-hand-side, and a $N$-fold coincidence measurement 
-%is conducted at the output on the right-hand-side.} \label{fig:MORDOR}	
-%\end{figure}
 
@@
   \caption{}
-  \label{fig:fusion}
+  \label{fig:MORDOR}
 \end{subfigure}
@@
 Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.}
-\label{fig:MORDOR}
 \end{figure}
@@
 
-Linear optics interferometry has become a leading contender for the implementation of quantum information processing protocols.
+Linear optical interferometry has become a leading contender for the implementation of quantum information processing protocols.
 The preparation, manipulation and measurement of photonic quantum information has become mainstream and widely employed, with impressive experimental accuracies.
 
-We have discussed the various ways in which quantum information can be represented photonically, how they can be manipulated and detected, and some of their leading applications.
+We have discussed the various ways in which quantum information can be represented \sihui{in photonics}, how they can be manipulated and detected, and some of their leading applications.
 

### 2017-06-29 submitted/paper.tex
Created new folder for reports.

--- 2017-06-29 paper.tex
@@
 Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}.
-\sihui {Some of them support new functionalities like secure delegated quantum computations \cite{bib:Barz12,bib:Fisher14}}.
-Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.
+Some of them support new functionalities like secure delegated quantum computations \cite{bib:Barz12,bib:Fisher14}.
+Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, encrypted quantum walks \cite{bib:Rohde_qw12}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.
 Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.
@@
 
-If the linear optical transformations \sihui{is to} be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
+If the linear optical transformations is to be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
 This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.
@@
 
-PNR detectors are a wonderful addition to the \sihui{linear optical} toolbox.
+PNR detectors are a wonderful addition to the linear optical toolbox.
 A notable example is the superconducting transition edge sensor (TES) which has an extremely high quantum efficiency.
@@
 
-We have discussed the various ways in which quantum information can be represented \sihui{in photonics}, how they can be manipulated and detected, and some of their leading applications.
+We have discussed the various ways in which quantum information can be represented in photonics, how they can be manipulated and detected, and some of their leading applications.
 

### 2017-06-29 Review merged 01-5-2017/paper.tex

\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscriptaddress]{revtex4}

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage[pdftex]{graphicx}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}
\usepackage[dvipsnames]{xcolor}

\newcommand{\sihui}[1]{{\color{Orchid}{#1}}}
\newcommand{\peter}[1]{{\color{YellowGreen}{#1}}}
\newcommand{\comment}[1]{{\color{blue}{#1}}}
\newcommand{\ah}{\hat{a}}
\newcommand{\adagh}{\hat{a}^\dag}

\begin{document}

\bibliographystyle{apsrev}

%
% Title
%

\title{The Resurgence of the Linear Optics Interferometer --- Recent Advances \& Applications}

%
% Authors
%

\author{Si-Hui Tan}
\email[]{sihui\_tan@sutd.edu.sg}
\affiliation{Singapore University of Technology and Design, 8 Somapah Road, Singapore}

\author{Peter P. Rohde}
\email[]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Software \& Information (CQSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

\date{\today}

\frenchspacing

%
% Abstract
%

\begin{abstract}
\end{abstract}

\maketitle

\tableofcontents

\section{Introduction}

\comment{To do}

Technical advancements have been made on many fronts. It is possible now to put single-photon sources and linear-optical networks on a silica chip. The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized. This increases the scalability of optical implementations of quantum information protocols.

\section{Mathematical background}

A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer. The creation and annihilation operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$. A similar commutation relationship can be written when additional degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present. When multiple photons are present, they experience quantum interference when all quantum labels are the same.

The action of a $2d$-port linear optical interferometer (with an equal number of input and output ports) is expressed as an application of unitary operations on the creation operators,

\begin{align}
b_i^{\dag}=\sum_{j=1}^d U_{ij}a_j^\dag \ ,
\end{align}
where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in SU(d)$. All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994}. In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons as a sequence of beamsplitters and internal transformations. Toolkits using group theory are being developed to deal with partial distinguishabilities among interfering photons \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}. Others use quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}. \sihui{Experimental implementation [Walmsley, Jennewein]}

\section{Optical encoding of quantum information on single-photons}

Using quantum states of light, there are a multitude of approaches to encoding quantum information. Beginning with a logical qubit,
\begin{align}
\ket\psi_L = \alpha \ket{0}_L + \beta\ket{1}_L,
\end{align}
we now discuss the most prominent such encodings, which have been widely employed. We will specifically focus on single-photon encodings, as opposed to, for example, continuous variable encodings.

These encodings are all isomorphic to one another, but nonetheless, because they are represented using entirely different physical systems, they each exhibit their own unique advantages and disadvantages, and methods by which to implement operations upon them.

%\subsection{Single-photons}

\subsubsection{Polarisation}

In polarisation encoding, the polarisation of a single photon in a single spatial mode encodes a logical qubit. Specifically, we represent the logical qubit as,
\begin{align}
\ket\psi_L = \alpha\ket{H} + \beta\ket{V},	
\end{align}
where $H$ ($V$) denotes a horizontally (vertically) polarised single photon.

Polarisation encoding has the elegance that the most common optical error mechanisms, such as loss or path-length mismatch, affect the two logical basis states equally. Furthermore, single-qubit operations may be directly implemented using wave-plates, which implement a rotation in polarisation space. Relevant to the preparation of large entangled states, such as cluster states, polarising beamsplitters can be employed to perform non-deterministic Bell state projections.

When physically constructing protocols based on polarisation-encoding, for obvious reasons it is extremely important that optical components be polarisation-preserving. Not doing so would obviously corrupt the logical state. Some waveguide technologies, for example, exhibit different refractive indices for the two polarisations.

\subsubsection{Dual-rail}

In dual-rail encoding, a single photon encodes a logical qubit as a superposition across two spatial modes,
\begin{align}
\ket\psi_L = \alpha\ket{1,0} + \beta\ket{0,1},
\end{align}
where $\ket{i,j}$ is a two-mode state with $i$ ($j$) photons in the first (second) spatial mode. Using this encoding, phase-shifters and beamsplitters between the two spatial modes implement arbitrary single-qubit operations. Unfortunately, because the two basis states evolve via independent paths, our dual-rail qubits are susceptible to path-length-mismatch, a problem that does not affect polarisation encoding.

Converting between polarisation- and dual-rail-encoding is trivial using polarising beamsplitters, which separate horizontal and vertical components into distinct spatial modes, or vice-versa.

\subsubsection{Time-bins}

Time-bin qubits encode quantum information into the time-of-arrival of single photons, which have fixed polarisation and reside in a single spatial mode. Effectively, we discretise the direction of propagation of photons into discrete bins, which are treated as orthogonal basis states. Specifically, we are employing the encoding,
\begin{align}
\ket\psi_L = \alpha\ket{1}_{t}\ket{0}_{t+\tau} + \beta \ket{0}_{t}\ket{1}_{t+\tau},
\end{align}
where $\ket{0}_t$ ($\ket{1}_t$) denotes the vacuum (single-photon) state with arrival time $t$. Here $\tau$ is the time-bin separation, which must be sufficiently large that the temporal envelopes of neighbouring photons do not overlap, thereby ensuring orthogonality of the logical basis states.

This encoding is particularly resource-savvy, since a single spatial mode (e.g length of optical fibre) can encapsulate many time-bin qubits as a `time-bin-train'. The amount of quantum information that can be encoded into the train is limited only by its physical length.

Unlike polarisation or dual-rail encoding, time-bin encoding does not lend itself to `native' single-qubit operations. Rather, fast switching can be used to spatially separate neighbouring time-bins, implement a beamsplitter operation between them, before converting back to time-bin encoding.

Time-bin encoding was first conceived via a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}. If the photon passes through the shorter (longer) path, it will arrive at the output port in an `early' (`later') time-bin labelled $\ket{e}$ ($\ket{\ell}$). Thus, the photon will exit the interferometer in a state that is a superposition of these two states. Owing to difficulties in implementing qubit operations in this basis, it was at the time mostly used for demonstrating quantum communication over long distances \cite{bib:Thew02,bib:Marcikic04}. With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operation, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}. These gates form an universal set for quantum computing. At the same time, an ultrafast measurement technique for recovering time-bin qubits was also demonstrated \cite{bib:Donohue2013}.

In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin qubits have a polarization register which is used to toggle between the mode in which qubits are stored and transmitted, {\it i.e.} the `register' mode, and the mode in which qubits are manipulated, {\it i.e.} the `processing' mode using a polarization rotation. Other operations needed are a displacement operation, that moves a time-bin qubit in the processing polarization in time relative to other qubits, a partial polarization rotation between the register and processing polarizations to couple them, and a photon number measurement in a bin. The polarization rotation and polarization coupling operations were implemented using a fast integrated optical switch based on polarization-sensitive cross-phase modulation with a switching time of less than 10ps. The displacement was implemented using a calcite crystal of a size that is of a path-length difference equal to an integer multiple of the time-bin separation. Using these operations and post-selection using a single-photon detectors, the authors were able to perform a heralded CPHASE gate \cite{bib:KLM01}.

In Donohue {\it et al.} \cite{bib:Donohue2013}, time-bins were converted into frequency bins using a nonlinear optical process known as sum-frequency generation (SFG) by pumping them on a crystal with a laser beam. The waveforms of the input photons and the pump beam are chirped in opposite directions in frequency, so that the output is a set of two peaks separated in frequency by an amount proportional to the time separation of the time bins. The output can then be measured with detectors that are slow compared to this separation. This is unlike conventional time-bin measurements which involve sending a time-bin state through an unbalanced Mach-Zedner interferometer matched to the time-bin separation to produce three output pulses that are separated by the time delay, and then having to resolve the middle pulse in time.

Apart from these promising advances in implementing time-bin qubit gates and ultrafast time-bin measurements, scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}. This is discussed in more detail in Section \ref{sec:timebins}.

%\subsection{Continuous-variables}

%\subsubsection{Coherent states}

%\subsubsection{Squeezed states}

\section{Efficient circuit decompositions of linear optics networks}

The task of implementing an arbitrary quantum computation on linear optics comes down to implementing an arbitrary $n\times n$ unitary matrix. If a non-unitary transformation is desired, it can be embedded within a unitary matrix with larger dimensions. An algorithm for expressing an arbitrary unitary matrix {\it exactly} in terms of a sequence of beamsplitters and phase-shifters was described by Reck \emph{et al.} \cite{bib:Reck1994}. This decomposition requires $\mathcal{O}(n^2)$ linear optical elements, and the algorithm for finding the decomposition has polynomial runtime. Thus, such decompositions can always be determined and implemented efficiently. The layout for the original Reck \emph{et al.} decomposition is shown in Fig.~\ref{fig:Reck}. However, since then a multitude of alternate decompositions have been found. A notable downside of the original decomposition is that different photons experience different circuit depth, i.e pass through different numbers of optical elements, resulting in asymmetry in losses and the accumulation of errors.

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{reck}
\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
\end{figure}

Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Reck1994, bib:Englert2001}. Later, it has been shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}. However, they do not provide an explicit construction for arbitrary unitaries.

If the linear optical transformations can be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}. Their approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.

\section{Reconstructing the linear optical network}

In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built. However, owing to manufacturing imperfections, a precise characterization of these devices is still needed post-production. One approach for achieving this is via quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}. However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterize the network, with exponential overhead, becoming impractical for large optical networks which can be as large as $n=900$ modes using present-day technology \comment{(check citations for number of modes)}. However, alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.

Generally, the unitary matrices of $d\times d$ linear optical devices are complex $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$. The scheme in \cite{bib:Laing12} relies on injecting one- and two-photon states into the network with correlated photon detection. First, they note some equivalencies: two unitaries $U$ and $U'$ are equivalent if there exist two diagonal unitary matrices $D_1^U$ and $D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are regarded as unknown and trivial phases on the input and output ports of the network, to which the one- and two-photon data are insensitive to. This reduces the first row and column elements to real numbers, i.e. $\theta_{1j}=\theta_{i1}=0$. Second, the photo-statistics remain invariant under complex conjugation by $U$. Thus, the imaginary part of $M_{2,2}$ must be non-negative. Then, assuming the first two rows and columns are non-vanishing, and there is no total loss in the interferometer, the matrix to be recovered is
\begin{align}
U=\left (\begin{array}{cccc}
r_{11} & r_{12} & \ldots & r_{1m} \\
r_{21} & r_{22}e^{i\theta_{22}} &\ldots & r_{2m}e^{i\theta_{2m}}\\
\vdots & \vdots & \ddots & \vdots \\
r_{m1} & r_{m2}e^{i\theta_{m2}} & \ldots & r_{mm}e^{i\theta_{mm}}
 \end{array}\right ) \ .
\end{align}
They showed it is possible to write the parameters $r_{ij}$, and $\theta_{ij}$ for $i,j\geq 2$ in terms of the $2m-1$ real parameters of the first column and row, and the visibility of two-photon inputs. The remaining $2m-1$ real parameters can be found via one-photon 
transmissions. An increased accuracy in the characterization is possible by estimating and correcting systematic errors that arise due to mode mismatch \cite{Dhand16}. Others have used numerical methods to find the closest parameters that yield the observed visibilities \cite{bib:Spagnolo16,bib:Tillmann16}.

Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead of Fock states \cite{bib:Rahimi-Keshari13,bib:Heilmann15}. Such states are produced by a standard laser source, thus reducing experimental resources. The $r_{jk}$ terms are found by the square root of the ratios of output intensities at the $k$th port to the input intensity at the $j$th port. The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha_1}\ket{\alpha_2}$ created by splitting a single coherent state on a 50-50 beamsplitter, and then imparting a relative phase, $\phi$, between them. The states $\ket{\alpha_1}$ and $\ket{\alpha_2}$ are input into port 1, and $j$ respectively. The output intensity at the $j$th port is then
\begin{align}
I_k=I(r_{1k}^2+r_{jk}^2+2 r_{1k}r_{kj}\cos(\phi+\theta_{jk})) \ ,
\end{align}
where $\theta_{jk}=0$ for $k=1$. By scanning the phase shift $\phi$ and locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$. An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase-shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$. In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure, whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.

\section{Experimental implementation}

Significant progress has been made in the experimental realisation of linear optics protocols, and have become standard and widespread. We now discuss some of these advances.

\subsection{State preparation}

The photonic states that are most commonly employed in linear optics protocols can be divided into Fock states (e.g single-photon), and entangled states, such as EPR, GHZ and cluster states. We will consider advances in each of these.

\subsubsection{Single-photons}

Sources of single photons for applications in quantum information processing can be separated into two main categories \cite{bib:Kok05}; those produced by spontaneous parametric down-conversion (SPDC), and those by solid-state emitters in a cavity. Both categories have seen major development recently in photon-number, with high fidelities. To-date, SPDC has been able to produce up to ten entangled photons \cite{bib:WangChen16,bib:Chen17}, and five-photon quantum interference has been reported using a quantum dot emitter in a microcavity \cite{bib:WangHe16}.

In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ non-linearity is pumped with a strong coherent state (i.e laser source) and with a small probability, the pump beam is absorbed by the crystal to produce two beams of lower energy known as the signal and idler. Owing to conservation of energy and momentum, the two beams have spatio-temporal correlations that can be engineered to produce twin-beam states with perfect  photon number correlation, of the form
\begin{align}
\ket\psi_\mathrm{SPDC} = \sqrt{1-\chi^2} \sum_{n=0}^\infty \chi^n \ket{n,n},	
\end{align}
where $\chi$ is the squeezing parameter. If a single photon were to be detected in one of the modes, it is certain that the other mode would similarly contain a single photon.

Some commonly used nonlinear crystals for SPDC are beta barium borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled  potassium titanyl phosphate (PPKTP). Recently, techniques using bismuth triborate (BiBO) have improved to the extent of becoming one of the record-holders in single-photon production \cite{bib:WangChen16}.

Solid-state single photon sources come from semiconducting nanostructures and nitrogen valencies (NV) centers in diamond. Both types are versatile and efficient sources of single photons, however, the photons they produce have suffered from the lack of indistinguishability that is necessary for typical quantum information processing applications. Recent developments in the former have been very promising. Notably, much progress has been made using resonant excitation of quantum dots. Here, laser pulses are used to excite their electronic resonance and trigger the emission of single photons \cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
bib:237403,bib:Sweeney14}. An architecture that embeds the quantum dot in a micropillar cavity with the same resonant frequency as the dot exploits the Purcell effect to achieve higher single-photon production efficiency€ \cite{bib:Ding16,bib:213601}. Such resonant excitation of quantum dots overcomes the homogenous broadening of the excited state that causes degradation of photon purity and improving indistinguishability. Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of single photons produced by such a quantum dot, the same group was able to demonstrate quantum interference between five indistinguishable photons \cite{bib:WangChen16}.

\subsubsection{Einstein-Podolsky-Rosen (EPR) pairs}

An EPR pair, or Bell pair, is one of the four states,
\begin{align}
\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \\
\ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
\end{align}
which are all maximally entangled and locally equivalent to one another. These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing \cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}. In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.} successfully prepared only under certain measurement outcomes of auxiliary modes. Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}. They are often used as a building block for preparing other multipartite entangled states.

\subsubsection{Greenberger-Horne-Zeilinger (GHZ) states}

GHZ states form a class of entangled quantum states on multiple subsystems with at least three parties \cite{bib:GHZ89}. For qubit encodings with $n$ subsystems, a GHZ state is of the form
\begin{align}
\ket{\Psi_{n}^{\rm (GHZ)}}=\frac{\ket{0}^{\otimes n}+\ket{1}^{\otimes n}}{\sqrt{2}} \ .
\end{align}
These states are also non-local, and have been used extensively in experimental test for non-locality \cite{bib:JW00,bib:Zhang15}. This has been a subject matter covered in detail by another review \cite{bib:JW12}.

\subsubsection{Cluster states}

Cluster states form another class of multiparty entangled states, and were conceived in the context of arrays of qubits with an Ising-type interaction \cite{bib:Briegel01}.

These states can be represented as a graph, in which vertices are qubits initialized into the superposition state $\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, with CPHASE operation applied between edges, as shown in Fig.~\ref{fig:cluster}. For this reason, such states are also referred to as graph states. The CPHASE operations generate entanglement between the qubits, and because they commute, are independent of ordering. Cluster states are a resource state for a model of quantum computation known as measurement-based quantum computation (MBQC). Here, having such a state as a resource enables universal quantum computation using only single-qubit measurements \cite{bib:Raussendorf03}. Therefore, the preparation of such states is highly valuable, generating much interest in their efficient preparation.

\begin{figure}[!htb]
\includegraphics[width=0.6\columnwidth]{cluster_state}
\caption{The representation of cluster states as a graph. Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on CPHASE gates, the ordering of which is irrelevant.} \label{fig:cluster}	
\end{figure}

Unfortunately, implementing CPHASE gates using linear optics is complicated and highly non-deterministic. A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell basis. These operations fuse smaller cluster states, represented using polarisation encoding, into larger ones, consuming one (type-I fusion) or two (type-II fusion) photons in the process. These operations are shown in Fig.~\ref{fig:fusion}. Although these operations are non-deterministic with a success probability of $1/2$, they require only a single beamsplitter, already a major improvement over directly implementing CPHASE gates. Furthermore, unlike CPHASE gates, fusion operations require only high Hong-Ou-Mandel visibility, rather than the Mach-Zehnder stability required within existing CPHASE gate implementations, a major experimental simplification.

Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing CPHASE gates.

\begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{fusion}
\caption{Fusion gates for joining smaller cluster states into larger ones. Both require only a single polarising beamsplitter, and waveplates. The type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, creating an edge between the remaining graphs. The type-I gate consumes one fewer photon, but requires number-resolved detection on the detected mode. The type-II gate requires only on/off photodetection, but consumes an additional photon. Thus, the type-I gate can be employed to fuse two Bell pairs into a 3-qubit cluster state, whereas the type-II gate will only grow clusters when beginning with at least 3 qubits per cluster.} \label{fig:fusion}	
\end{figure}

\subsection{Linear optics networks}

Numerous experimental implementations of various linear optics protocols have been demonstrated, using a variety of architectures. The main contenders considered to date are: bulk-optics; waveguides; and time-bin encoding.

\subsubsection{Bulk-optics}

The early implementations of linear optics protocols relied on bulk-optics implementations, in which a circuit is decomposed into a discrete arrangement of optical components, specifically beamsplitters and phase-shifters. This corresponds to a direct implementation of the Reck \emph{et al.} decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate decompositions.

Although this approach is effective and conceptually straightforward, it is highly impractical for large interferometers. For example, the implementation of a 100-mode interferometer requires on the order of 10,000 discrete optical elements, which must all be simultaneously aligned with interferometric stability, a highly experimentally challenging problem, not to mention incredibly physically large.

\subsubsection{Waveguides}

Alternately, integrated waveguide devices can be employed to implement identical decompositions by etching the modes into paths in an optical chip, where evanescent coupling between closely neighbouring modes implements beamsplitter operations. Such devices are extremely compact, allowing the miniaturisation of large numbers of optical elements. Importantly, such devices are extremely optically stable, mitigating the need for any kind of dynamic stabilisation

\subsubsection{Time-bins}\label{sec:timebins}

Using time-bin encoding of optical qubits, the obvious question is how to perform operations upon them. In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains, shown in Fig.~\ref{fig:FL_arch}.

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{full_architecture}
\caption{A fibre-loop architecture for implementing arbitrary linear optics operations upon a time-bin-encoded pulse-train. The source prepares the temporally encoded pulse-train, with time-bin separation $\tau$. The pulse-train then enters a dual-loop configuration. The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the number of optical modes). The architecture is controlled via three dynamically controlled beamsplitters. The first and last need only be on/off switches, whose sole purpose is to couple in the prepared pulse-train, keep it within the outer loop for the required duration, and then couple out of the outer loop, yielding the transformed pulse-train. The central beamsplitter must be able to implement arbitrary classically-controlled beamsplitter operations.} \label{fig:FL_arch}	
\end{figure}

The architecture is frugal in its use of optical components, requiring only three dynamic beamsplitters, and several lengths of fibre. The beauty of this architecture is that the experimental requirements do not increase with the number of optical modes. The only parameter that scales with the number of optical modes is the outer loop, which must be at least long enough to house the entire time-bin-encoded pulse-train. Note, however, that the central beamsplitter must be controllable at sub-$\tau$ time-scales, so as to enable each temporal mode to be addressed individually, which is technically challenging.

The workings of the scheme can be thought of as follows: the inner loop allows arbitrary beamsplitter operations between neighbouring time-bins; the outer loop does nothing interferometric, but rather enables the pulse-train to undergo as many applications of the inner loops as necessary. It then follows that this scheme is universal for linear optics, as a sufficient number of beamsplitter operations between neighbouring modes enables universal decompositions, using for example, the Reck \emph{et al.} decomposition described earlier.

As a simple example of how such time-bin encoding maps to other encodings, in Fig.~\ref{fig:PBS_TB} we show the isomorphism between the polarising beamsplitter operation and a pairwise temporal beamsplitter operation. This implies a direct mapping for implementing cluster state preparation within the time-bin scheme.

\begin{figure}[!htb]
\includegraphics[width=0.7\columnwidth]{PBS_TB}
\caption{Mapping between two polarisation-encoded qubits undergoing a polarising beamsplitter (PBS) operation, and its equivalent representation using 4 time-bins in a pulse-train. The PBS completely reflects (transmits) the vertical (horizontal) polarisations. The evolution of the four logical basis states, and their respective outputs, are shown explicitly. Writing out this PBS transformation in matrix form yields a permutation. Taking this permutation and relabelling the modes, we obtain the time-bin transformation shown underneath -- a simple swap of two of the four time-bins.} \label{fig:PBS_TB}	
\end{figure}

The above description applies to passive linear optics, which is sufficient for protocols such as {\sc BosonSampling}, but insufficient for universal optical quantum computation, which requires the addition of ancillary states, and measurement with fast-feedforward. To address this, it was shown in \cite{Rohde} that by dynamically preparing ancillary pulse-trains (from the already-existing source), classically controlled by time-resolved measurements at the output, and changing the switching sequence, we can effectively couple in and out arbitrary subsets of the optical modes, enabling partial measurements to be implemented.

\subsection{Photodetection}

Broadly speaking, there are two main classes of photodetectors: number resolved, and non-number-resolved (also referred to as bucket, or on/off) detectors. As the names suggest, these detectors are able to measure photon-number, or merely the presence or absence of photons. They are described by the measurement projectors,
\begin{align}
\hat\Pi_n &= \ket{n}\bra{n}, \nonumber \\
\hat\Pi_\text{off} &= \hat\Pi_0, \nonumber \\
\hat\Pi_\text{on} &= \hat{I} - \hat\Pi_\text{on},	
\end{align}
respectively.

The dominant challenge facing the experimental implementation of both types of detectors is inefficiency, which results in higher photon-number being confused as having lower photon-number. In some protocols, such as type-II fusion, which relies on coincidence detection, inefficiency is not problematic. However, in most applications, including type-I fusion, this is highly problematic as photon-number confusion results in decoherence via projecting onto the wrong photon-number, unknown to the observer.

\comment{What are the different technologies}

\section{Applications for linear optics interferometry}

\subsection{Linear optics quantum computation}

\subsection{Boson-sampling}

\subsection{Quantum metrology}

\comment{Discuss NOON states - Heisenberg limited}

\comment{Discuss MORDOR scheme}

\section{Conclusion}

Linear optics interferometry has become a leading contender for the implementation of quantum information processing protocols. The preparation, manipulation and measurement of photonic quantum information has become mainstream and widely employed, with impressive experimental accuracies.

We have discussed the various ways in which quantum information can be represented photonically, how they can be manipulated and detected, and some of their leading applications.

Although there are countless physical architectures for the implementation of quantum information processing, and it is far from certain which will win `the quantum race for supremacy', optics will always find a home as the only contender for applications involving quantum communication. For this reason, the future of linear optics interferometry is a bright one, which will find inevitable applicability in the future quantum world.

%
% Acknowledgments
%

\begin{acknowledgments}
P.P.R. is funded by an ARC Future Fellowship (project FT160100397).
\end{acknowledgments}

%
% Bibliography
%

\bibliography{paper}

\end{document}

### 2017-06-29 Review merged 30-4-2017/paper.tex

--- 2017-06-29 Review merged 01-5-2017/paper.tex
@@
 
-\comment{To do}
+\sihui{Si-Hui can colour code things she adds like this}
+
+\peter{And Peter can do it like this}
+
+\comment{Let's add comments and questions like this}
 
@@
 \section{Mathematical background}
+\comment{Mathematical representation for LO networks, and very basic background on quantum optics}\\
 
 A idealized single photon in a quantum interferometer is described by its creation operator $\adagh_{j}$, where $j$ is the label of the mode the photon is in  within the interferometer.
-The creation and annihilation operators satisfy the bosonic comutation relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.
-A similar commutation relationship can be written when additional degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present.
+The creation and annihilation operators satisfy the bosonic comutator relationship $[\ah_{j},\adagh_{k}]=\delta_{j,k}$.
+A similar commutator relationship can be  written up when more degrees of freedom, such as polarization, orbital angular momentum, and time-bins \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}, are present.
 When multiple photons are present, they experience quantum interference when all quantum labels are the same.
@@
 where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in SU(d)$.
-All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994}.
-In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons as a sequence of beamsplitters and internal transformations.
+All such transformation can be expressed as sequence of beamsplitters and waveplates \cite{bib:Reck1994}.
+In the case when photons have additional labels, for instance, if they have internal labels on top of spatial labels, it is also possible to derive an analogous decomposition, known as a cosine-sine decomposition \cite{bib:Dhand2015}, that realizes the unitary transformation on the photons into a sequence of beamsplitters and internal transformations.
 Toolkits using group theory are being developed to deal with partial distinguishabilities among interfering photons \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}.
-Others use quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}.
-\sihui{Experimental implementation [Walmsley, Jennewein]}
+Others use
+quantum-to-classical transitions to explain multiparticle interference \cite{bib:Ra2013}. \sihui{Experimental implementation [Walmsley, Jennewein]}
+
+\section{Optical encoding of quantum information on single-photons}
 
@@
 
-Time-bin encoding was first conceived via a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}.
-If the photon passes through the shorter (longer) path, it will arrive at the output port in an `early' (`later') time-bin labelled $\ket{e}$ ($\ket{\ell}$).
-Thus, the photon will exit the interferometer in a state that is a superposition of these two states.
-Owing to difficulties in implementing qubit operations in this basis, it was at the time mostly used for demonstrating quantum communication over long distances \cite{bib:Thew02,bib:Marcikic04}.
-With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operation, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}.
+\textbf{Need to edit the above together with what follows...}
+
+It was first conceived for a single-photon passing through a Mach-Zedner interferometer with its two paths having different lengths \cite{bib:Brendel99}.
+If the photon passes through the shorter (longer) path, then it will arrive at the output port in an ``early" (``late") time bin labelled $\ket{e}$ ($\ket{\ell}$).
+Thus, photon will exit the interferometer in a state that is a superposition of these two states.
+Owing to difficulties in implementing qubit operations in this basis, it was at that time mostly used for demonstrating quantum communication over long distance \cite{bib:Thew02,bib:Marcikic04}.
+With the advent of faster optical components, and single-photon detectors, it has become feasible to perform any single qubit operations, and a post-selected CPHASE gate on time-bin qubits \cite{bib:Humphreys2013}.
 These gates form an universal set for quantum computing.
@@
 
-In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin qubits have a polarization register which is used to toggle between the mode in which qubits are stored and transmitted, {\it i.e.} the `register' mode, and the mode in which qubits are manipulated, {\it i.e.} the `processing' mode using a polarization rotation.
-Other operations needed are a displacement operation, that moves a time-bin qubit in the processing polarization in time relative to other qubits, a partial polarization rotation between the register and processing polarizations to couple them, and a photon number measurement in a bin.
-The polarization rotation and polarization coupling operations were implemented using a fast integrated optical switch based on polarization-sensitive cross-phase modulation with a switching time of less than 10ps.
+In Humphrey {\it et al.} \cite{bib:Humphreys2013}, the time-bin qubits have a polarization register which is used to toggle between the mode in which qubits are stored and transmitted, {\it i.e.} the ``register" mode, and the mode in which qubits are manipulated, {\it i.e.} the ``processing" mode using a polarization rotation.
+Other operations needed are a displacement operation moves a time-bin qubit in the processing polarization in time relative to other qubits, a partial polarization rotation between the register and processing polarizations to couple them, and a photon number measurement in a bin.
+The polarization rotation and polarization coupling operations were implemented using a fast integrated optical switch based on polarization-sensitive cross-phase modulation with a switching time of less than 10 ps.
 The displacement was implemented using a calcite crystal of a size that is of a path-length difference equal to an integer multiple of the time-bin separation.
@@
 
-In Donohue {\it et al.} \cite{bib:Donohue2013}, time-bins were converted into frequency bins using a nonlinear optical process known as sum-frequency generation (SFG) by pumping them on a crystal with a laser beam.
+In Donohue {\it et al.} \cite{bib:Donohue2013}, time bins were converted into frequency bins using a nonlinear optical process known as sum-frequency generation (SFG) by pumping them on a crystal with a laser beam.
 The waveforms of the input photons and the pump beam are chirped in opposite directions in frequency, so that the output is a set of two peaks separated in frequency by an amount proportional to the time separation of the time bins.
 The output can then be measured with detectors that are slow compared to this separation.
-This is unlike conventional time-bin measurements which involve sending a time-bin state through an unbalanced Mach-Zedner interferometer matched to the time-bin separation to produce three output pulses that are separated by the time delay, and then having to resolve the middle pulse in time.
+This is unlike conventional time-bin measurements which involves sending a time-bin state through an unbalanced Mach-Zedner interferometer matched to a bin separation to produce three output pulses that are separated by the time delay, and then having to resolve the middle pulse in time.
 
-Apart from these promising advances in implementing time-bin qubit gates and ultrafast time-bin measurements, scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}.
+Apart from these promising advances in produce time-bin qubit gates and ultrafast time-bin measurements, scalable networks using time-bin encoding are also possible using a loop-based architecture \cite{bib:Motes14}.
 This is discussed in more detail in Section \ref{sec:timebins}.
@@
 If a non-unitary transformation is desired, it can be embedded within a unitary matrix with larger dimensions.
-An algorithm for expressing an arbitrary unitary matrix {\it exactly} in terms of a sequence of beamsplitters and phase-shifters was described by Reck \emph{et al.} \cite{bib:Reck1994}.
-This decomposition requires $\mathcal{O}(n^2)$ linear optical elements, and the algorithm for finding the decomposition has polynomial runtime.
-Thus, such decompositions can always be determined and implemented efficiently.
-The layout for the original Reck \emph{et al.} decomposition is shown in Fig.~\ref{fig:Reck}.
-However, since then a multitude of alternate decompositions have been found.
-A notable downside of the original decomposition is that different photons experience different circuit depth, i.e pass through different numbers of optical elements, resulting in asymmetry in losses and the accumulation of errors.
-
-\begin{figure}[!htb]
-\includegraphics[width=\columnwidth]{reck}
-\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
-\end{figure}
-
-Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Reck1994, bib:Englert2001}.
-Later, it has been shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
-However, they do not provide an explicit construction for arbitrary unitaries.
+An algorithm for expressing an arbitrary unitary matrix {\it exactly} in terms of a sequence of $\mathcal{O}(n^2)$ beamsplitters and phase-shifters exists \cite{bib:Reck1994}.
+Alternatively, Mach-Zedner interferometer can also be used as building blocks instead of beamsplitters and phase shifters \cite{bib:Reck1994, bib:Englert2001}.
+Later, it has been shown that any nontrivial beam splitter, that does more than swapping modes around or add phases to them, is universal for linear optics \cite{bib:Bouland2014}.
+However, they do not provide a construction for arbitrary unitaries.
 
 If the linear optical transformations can be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
-Their approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.
+Their approach reduces the required number of beamsplitters but increases the total number of optical elements needed increases by a factor of 2.
 
@@
 
-In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built.
+In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase shifters is known once it is built.
 However, owing to manufacturing imperfections, a precise characterization of these devices is still needed post-production.
-One approach for achieving this is via quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
-However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterize the network, with exponential overhead, becoming impractical for large optical networks which can be as large as $n=900$ modes using present-day technology \comment{(check citations for number of modes)}.
-However, alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.
+One of the ways, this can be done is via a quantum process tomography \cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11} .
+However, quantum process tomography is an expensive method in terms of number of measurements required to characterize the network, and it becomes impractical for large optical networks which can now be as large as 900 modes (check citations for number of modes).
+Alternative characterization protocols have been developed using quantum interference of various quantum light sources \cite{bib:Laing12,bib:Rahimi-Keshari13} in the linear optical device.
 
-Generally, the unitary matrices of $d\times d$ linear optical devices are complex $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$.
-The scheme in \cite{bib:Laing12} relies on injecting one- and two-photon states into the network with correlated photon detection.
-First, they note some equivalencies: two unitaries $U$ and $U'$ are equivalent if there exist two diagonal unitary matrices $D_1^U$ and $D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are regarded as unknown and trivial phases on the input and output ports of the network, to which the one- and two-photon data are insensitive to.
-This reduces the first row and column elements to real numbers, i.e.
+Generally, the unitary matrix of the $d\times d$ linear optical device are complex numbers $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$.
+The scheme in \cite{bib:Laing12} relies on injecting one-photon and two-photon states into the linear optical network with correlated photon detection.
+First, they note some equivalencies: two unitaries $U$ and $U'$ are equivalent if there exist two diagonal unitary matrices $D_1^U$ and $D_2^U$ such that $U'=D^U_1 U D^U_2$, because these diagonal matrices are regarded as unknown and trivial phases on the input and output ports of the network, to which the one-photon and two-photon data are insensitive to.
+This reduces the first row and first column elements to real numbers, i.e.
 $\theta_{1j}=\theta_{i1}=0$.
-Second, the photo-statistics remain invariant under complex conjugation by $U$.
+Second, the photon statistics remain unchanged under the complex conjugation of $U$.
 Thus, the imaginary part of $M_{2,2}$ must be non-negative.
-Then, assuming the first two rows and columns are non-vanishing, and there is no total loss in the interferometer, the matrix to be recovered is
+Then assuming that the first two rows and columns are non-vanishing, and that there is no total loss in the interferometer, the matrix to be recovered is
 \begin{align}
@@
 \end{align}
-They showed it is possible to write the parameters $r_{ij}$, and $\theta_{ij}$ for $i,j\geq 2$ in terms of the $2m-1$ real parameters of the first column and row, and the visibility of two-photon inputs.
+In the paper, they showed that it is possible to write the paramaters $r_{ij}$, and $\theta_{ij}$ for $i,j\geq 2$ in terms of the $2m-1$ real parameters of the first column and row, and the visibility of two-photon inputs.
 The remaining $2m-1$ real parameters can be found via one-photon
 transmissions.
-An increased accuracy in the characterization is possible by estimating and correcting systematic errors that arise due to mode mismatch \cite{Dhand16}.
+An increased accuracy of the characterization is possible by estimating and correcting systematic errors that arise due to mode mismatch \cite{Dhand16}.
 Others have used numerical methods to find the closest parameters that yield the observed visibilities \cite{bib:Spagnolo16,bib:Tillmann16}.
 
-Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead of Fock states \cite{bib:Rahimi-Keshari13,bib:Heilmann15}.
-Such states are produced by a standard laser source, thus reducing experimental resources.
-The $r_{jk}$ terms are found by the square root of the ratios of output intensities at the $k$th port to the input intensity at the $j$th port.
+Another characterization method was presented that is similar to \cite{bib:Laing12} with the important exception that coherent states are to be used instead \cite{bib:Rahimi-Keshari13,bib:Heilmann15}.
+Such states are produced by a standard laser source, thus reducing the resource needed.
+The $r_{jk}$ terms are found by the square root of the ratios of output intensity at the $k$th port to the input intensity at the $j$th port.
 The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha_1}\ket{\alpha_2}$ created by splitting a single coherent state on a 50-50 beamsplitter, and then imparting a relative phase, $\phi$, between them.
 The states $\ket{\alpha_1}$ and $\ket{\alpha_2}$ are input into port 1, and $j$ respectively.
-The output intensity at the $j$th port is then
+The output intensity at the $j$th port is
 \begin{align}
@@
 where $\theta_{jk}=0$ for $k=1$.
-By scanning the phase shift $\phi$ and locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$.
-An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase-shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$.
-In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure, whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.
+By scanning the phase shift $\phi$ and then locating the maximum value of $I_k$ for $j=2,\ldots, m$, all unknown phases can be found via $\theta_{jk}=2\pi-\phi$.
+An elegant extension of the scheme of Rahimi-Keshari {\it et al.} removes the need for precise control of the phase shift $\phi$ \cite{bib:Heilmann15} by suggesting instead to plot the output intensity $I_k$ with respect to the input intensity $I$.
+In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure.
+whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.
 
@@
 
-Significant progress has been made in the experimental realisation of linear optics protocols, and have become standard and widespread. We now discuss some of these advances.
-
 \subsection{State preparation}
-
-The photonic states that are most commonly employed in linear optics protocols can be divided into Fock states (e.g single-photon), and entangled states, such as EPR, GHZ and cluster states.
-We will consider advances in each of these.
 
@@
 
-Sources of single photons for applications in quantum information processing can be separated into two main categories \cite{bib:Kok05}; those produced by spontaneous parametric down-conversion (SPDC), and those by solid-state emitters in a cavity.
-Both categories have seen major development recently in photon-number, with high fidelities.
-To-date, SPDC has been able to produce up to ten entangled photons \cite{bib:WangChen16,bib:Chen17}, and five-photon quantum interference has been reported using a quantum dot emitter in a microcavity \cite{bib:WangHe16}.
+Sources of single photons for applications of quantum information processing are 
+separated into two main categories \cite{bib:Kok05}; those produced by spontaneous 
+parametric down-conversion (SPDC), and those by solid-state emitters in a cavity. 
+Both categories have seen some leaps recently in their record production of numbers 
+of single photons while preserving good qualities in their single photons. To 
+date, SPDC has been able to produce up to ten entangled photons 
+\cite{bib:WangChen16,bib:Chen17}, and five-photon quantum interference has been 
+reported using a quantum dot emitter in a microcavity \cite{bib:WangHe16}.
 
-In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ non-linearity is pumped with a strong coherent state (i.e laser source) and with a small probability, the pump beam is absorbed by the crystal to produce two beams of lower energy known as the signal and idler.
-Owing to conservation of energy and momentum, the two beams have spatio-temporal correlations that can be engineered to produce twin-beam states with perfect  photon number correlation, of the form
-\begin{align}
-\ket\psi_\mathrm{SPDC} = \sqrt{1-\chi^2} \sum_{n=0}^\infty \chi^n \ket{n,n},	
-\end{align}
-where $\chi$ is the squeezing parameter. If a single photon were to be detected in one of the modes, it is certain that the other mode would similarly contain a single photon.
+In SPDC, a nonlinear crystal with a large $\chi^{(2)}$ is pumped with a strong 
+laser and with a small probability, the pump beam is absorbed by the crystal to 
+produce two beams of lower energy known as the signal and idler beams. Owing to 
+conservation of energy and momentum, the two beams have spatio-temporal 
+correlations that can be engineered to produce twin-beam states which have 
+perfectly correlated photon numbers. If a single photon were to be detected in one 
+of the beams, and then it is certain that the other beam would be in the state of a 
+single photon. Some commonly used nonlinear crystals for SPDC are beta barium 
+borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled 
+potassium titanyl phosphate (PPKTP). Recently, techniques using bismuth triborate 
+(BiBO) have improved to the extent of becoming one of the record-holders of single-
+photon production \cite{bib:WangChen16}.
 
-Some commonly used nonlinear crystals for SPDC are beta barium borate (BBO), periodically poled lithium niobate (PPLN), and periodically poled  potassium titanyl phosphate (PPKTP).
-Recently, techniques using bismuth triborate (BiBO) have improved to the extent of becoming one of the record-holders in single-photon production \cite{bib:WangChen16}.
-
-Solid-state single photon sources come from semiconducting nanostructures and nitrogen valencies (NV) centers in diamond.
-Both types are versatile and efficient sources of single photons, however, the photons they produce have suffered from the lack of indistinguishability that is necessary for typical quantum information processing applications.
-Recent developments in the former have been very promising.
-Notably, much progress has been made using resonant excitation of quantum dots.
-Here, laser pulses are used to excite their electronic resonance and trigger the emission of single photons \cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
-bib:237403,bib:Sweeney14}.
-An architecture that embeds the quantum dot in a micropillar cavity with the same resonant frequency as the dot exploits the Purcell effect to achieve higher single-photon production efficiency€ \cite{bib:Ding16,bib:213601}.
-Such resonant excitation of quantum dots overcomes the homogenous broadening of the excited state that causes degradation of photon purity and improving indistinguishability.
-Using a time-bin loop-based architecture \cite{bib:Motes14} on a stream of single photons produced by such a quantum dot, the same group was able to demonstrate quantum interference between five indistinguishable photons \cite{bib:WangChen16}.
+Solid-state single photon sources come from semiconducting nanostructures and 
+nitrogen valencies (NV) centers in diamond. Both types are versatile and efficient 
+sources of single photons, however, the photons they produce have suffered from 
+lack of indistinguishability that is necessary for quantum information processing.
+Recent developments in the former show promising developments. Notably, much 
+progress has been made using resonant excitation of quantum dots. Laser pulses are 
+used to excite their electronic resonance and trigger the emission of single 
+photons \cite{bib:Muller07,bib:Vamivakas09, bib:Flagg09,bib:Ates09, bib:Dirk10,
+bib:1748,bib:Jayakumar13,bib:Wei14,bib:Muller14,bib:Unsleber15,
+bib:237403,bib:Sweeney14}. An architecture that embeds the quantum dot in a 
+micropillar cavity with the same resonant frequency as the dot exploits the 
+Purcell effect to achieve higher single-photon production efficiency 
+†\cite{bib:Ding16,bib:213601}. 
+Such resonant excitation of quantum dots overcome the homogenous broadening of the 
+excited state that causes degradation of photon purity and hence improves
+indistinguishability. Using a time-bin loop-based architecture \cite{bib:Motes14} 
+on a stream of single photons produced by such a quantum dot, the same group was 
+able to demonstrate quantum interference between five indistinguishable photons 
+\cite{bib:WangChen16}.
 
@@
 
-An EPR pair, or Bell pair, is one of the four states,
-\begin{align}
-\ket{0}_A\ket{0}_B &\pm \ket{1}_A\ket{1}_B, \nonumber \\
-\ket{1}_A\ket{0}_B &\pm \ket{0}_A\ket{1}_B,
-\end{align}
-which are all maximally entangled and locally equivalent to one another.
-These are the simplest examples of entangled states, and their preparation via SPDC has been the mainstay of entangled state preparation for quantum optical processing \cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
+\sihui{ Discuss producing Bell pairs using SPDC, and transforming them into GHZ and cluster states.}
+
+An EPR pair is a pair of qubits that are in a Bell state together, that is, one of the following states: $\{\ket{0}_A\ket{0}_B\pm\ket{1}_A\ket{1}_B,\{\ket{1}_A\ket{0}_B\pm\ket{1}_A\ket{0}_B\}$.
+Such a pair of qubits forms the simplest example of entangled states, and its production from spontaneous parametric down-conversion (SPDC) have been the mainstay of entanglement source for quantum optical processing \cite{bib:Kim01,bib:Kim03,bib:Brida07,bib:Dayan07}.
 In some applications, it may be desired to have the EPR pairs conditionally prepared, {\it i.e.} successfully prepared only under certain measurement outcomes of auxiliary modes.
-Several theoretical approaches have been proposed for this purpose \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and demonstrated \cite{bib:Wagenknecht10,bib:Barz10}.
-They are often used as a building block for preparing other multipartite entangled states.
+Some theoretical proposals have been proposed \cite{bib:Pittman03,bib:Sliwa03,bib:Walther07}, and in some cases demonstrated \cite{bib:Wagenknecht10,bib:Barz10}.
 
@@
 
-GHZ states form a class of entangled quantum states on multiple subsystems with at least three parties \cite{bib:GHZ89}. For qubit encodings with $n$ subsystems, a GHZ state is of the form
-\begin{align}
-\ket{\Psi_{n}^{\rm (GHZ)}}=\frac{\ket{0}^{\otimes n}+\ket{1}^{\otimes n}}{\sqrt{2}} \ .
-\end{align}
-These states are also non-local, and have been used extensively in experimental test for non-locality \cite{bib:JW00,bib:Zhang15}.
-This has been a subject matter covered in detail by another review \cite{bib:JW12}.
-
 \subsubsection{Cluster states}
-
-Cluster states form another class of multiparty entangled states, and were conceived in the context of arrays of qubits with an Ising-type interaction \cite{bib:Briegel01}.
-
-These states can be represented as a graph, in which vertices are qubits initialized into the superposition state $\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, with CPHASE operation applied between edges, as shown in Fig.~\ref{fig:cluster}.
-For this reason, such states are also referred to as graph states.
-The CPHASE operations generate entanglement between the qubits, and because they commute, are independent of ordering.
-Cluster states are a resource state for a model of quantum computation known as measurement-based quantum computation (MBQC).
-Here, having such a state as a resource enables universal quantum computation using only single-qubit measurements \cite{bib:Raussendorf03}.
-Therefore, the preparation of such states is highly valuable, generating much interest in their efficient preparation.
-
-\begin{figure}[!htb]
-\includegraphics[width=0.6\columnwidth]{cluster_state}
-\caption{The representation of cluster states as a graph.
-Vertices represent qubits initialised into the $\ket{+}$ state, while edges represent the application on CPHASE gates, the ordering of which is irrelevant.} \label{fig:cluster}
-\end{figure}
-
-Unfortunately, implementing CPHASE gates using linear optics is complicated and highly non-deterministic.
-A major improvement upon this is to use fusion gates - rotated polarising beamsplitters, which implement projections onto the Bell basis.
-These operations fuse smaller cluster states, represented using polarisation encoding, into larger ones, consuming one (type-I fusion) or two (type-II fusion) photons in the process.
-These operations are shown in Fig.~\ref{fig:fusion}.
-Although these operations are non-deterministic with a success probability of $1/2$, they require only a single beamsplitter, already a major improvement over directly implementing CPHASE gates.
-Furthermore, unlike CPHASE gates, fusion operations require only high Hong-Ou-Mandel visibility, rather than the Mach-Zehnder stability required within existing CPHASE gate implementations, a major experimental simplification.
-
-Although these gates are non-deterministic and consume qubits, strategies have been described for efficiently preparing arbitrarily large cluster states of arbitrary topology, and using far fewer optical elements than by directly employing CPHASE gates.
-
-\begin{figure}[!htb]
-\includegraphics[width=0.7\columnwidth]{fusion}
-\caption{Fusion gates for joining smaller cluster states into larger ones.
-Both require only a single polarising beamsplitter, and waveplates.
-The type-I and -II fusion gates consume 1 or 2 qubits (photons) respectively, creating an edge between the remaining graphs.
-The type-I gate consumes one fewer photon, but requires number-resolved detection on the detected mode.
-The type-II gate requires only on/off photodetection, but consumes an additional photon.
-Thus, the type-I gate can be employed to fuse two Bell pairs into a 3-qubit cluster state, whereas the type-II gate will only grow clusters when beginning with at least 3 qubits per cluster.} \label{fig:fusion}
-\end{figure}
 
@@
 
-Numerous experimental implementations of various linear optics protocols have been demonstrated, using a variety of architectures.
-The main contenders considered to date are: bulk-optics; waveguides; and time-bin encoding.
-
 \subsubsection{Bulk-optics}
-
-The early implementations of linear optics protocols relied on bulk-optics implementations, in which a circuit is decomposed into a discrete arrangement of optical components, specifically beamsplitters and phase-shifters.
-This corresponds to a direct implementation of the Reck \emph{et al.} decomposition shown in Fig.~\ref{fig:Reck}, or subsequent alternate decompositions.
-
-Although this approach is effective and conceptually straightforward, it is highly impractical for large interferometers.
-For example, the implementation of a 100-mode interferometer requires on the order of 10,000 discrete optical elements, which must all be simultaneously aligned with interferometric stability, a highly experimentally challenging problem, not to mention incredibly physically large.
 
@@
 
-Alternately, integrated waveguide devices can be employed to implement identical decompositions by etching the modes into paths in an optical chip, where evanescent coupling between closely neighbouring modes implements beamsplitter operations.
-Such devices are extremely compact, allowing the miniaturisation of large numbers of optical elements.
-Importantly, such devices are extremely optically stable, mitigating the need for any kind of dynamic stabilisation
+\subsubsection{Time-bins}\label{sec:timebins}
 
-\subsubsection{Time-bins}\label{sec:timebins}
+\cite{bib:Motes14}
 
@@
 The workings of the scheme can be thought of as follows: the inner loop allows arbitrary beamsplitter operations between neighbouring time-bins; the outer loop does nothing interferometric, but rather enables the pulse-train to undergo as many applications of the inner loops as necessary.
-It then follows that this scheme is universal for linear optics, as a sufficient number of beamsplitter operations between neighbouring modes enables universal decompositions, using for example, the Reck \emph{et al.} decomposition described earlier.
+It then follows that this scheme is universal for linear optics, as a sufficient number of beamsplitter operations between neighbouring modes enables universal decompositions, such as that by \cite{Reck}.
 
 As a simple example of how such time-bin encoding maps to other encodings, in Fig.~\ref{fig:PBS_TB} we show the isomorphism between the polarising beamsplitter operation and a pairwise temporal beamsplitter operation.
-This implies a direct mapping for implementing cluster state preparation within the time-bin scheme.
 
@@
 
-\subsection{Photodetection}
+\subsection{Measurement}
 
-Broadly speaking, there are two main classes of photodetectors: number resolved, and non-number-resolved (also referred to as bucket, or on/off) detectors.
-As the names suggest, these detectors are able to measure photon-number, or merely the presence or absence of photons.
-They are described by the measurement projectors,
-\begin{align}
-\hat\Pi_n &= \ket{n}\bra{n}, \nonumber \\
-\hat\Pi_\text{off} &= \hat\Pi_0, \nonumber \\
-\hat\Pi_\text{on} &= \hat{I} - \hat\Pi_\text{on},	
-\end{align}
-respectively.
+\subsubsection{Photodetection}
 
-The dominant challenge facing the experimental implementation of both types of detectors is inefficiency, which results in higher photon-number being confused as having lower photon-number.
-In some protocols, such as type-II fusion, which relies on coincidence detection, inefficiency is not problematic.
-However, in most applications, including type-I fusion, this is highly problematic as photon-number confusion results in decoherence via projecting onto the wrong photon-number, unknown to the observer.
+\comment{Discuss number-resolved and bucket detectors, multiplexed detection, APDs, current micropillar detectors}
 
-\comment{What are the different technologies}
+\subsubsection{Homodyning}
 
@@
 
+\subsection{Encrypted quantum computation}
+
+\section{State of the art}
+
+\comment{Discuss where experiments are at at the moment}
+
 \section{Conclusion}
-
-Linear optics interferometry has become a leading contender for the implementation of quantum information processing protocols.
-The preparation, manipulation and measurement of photonic quantum information has become mainstream and widely employed, with impressive experimental accuracies.
-
-We have discussed the various ways in which quantum information can be represented photonically, how they can be manipulated and detected, and some of their leading applications.
-
-Although there are countless physical architectures for the implementation of quantum information processing, and it is far from certain which will win `the quantum race for supremacy', optics will always find a home as the only contender for applications involving quantum communication.
-For this reason, the future of linear optics interferometry is a bright one, which will find inevitable applicability in the future quantum world.
 

### 2017-09-03 (PR final edits) linear_optics_review/paper.tex
Added Peter's additions in July

@@
 \newcommand{\sihui}[1]{{\color{Orchid}{#1}}}
-\newcommand{\peter}[1]{{\color{YellowGreen}{#1}}}
-\newcommand{\comment}[1]{{\color{blue}{#1}}}
+\newcommand{\peter}[1]{{\color{blue}{#1}}}
+\newcommand{\comment}[1]{{\color{YellowGreen}{#1}}}
 \newcommand{\ah}{\hat{a}}
@@
 \author[1,2]{Si-Hui \snm{Tan}}
+\cortext[cor1]{\peter{sihui\_tan@sutd.edu.sg}}
 
 \author[3]{Peter P. \snm{Rohde}\corref{cor1}}
-\cortext[cor1]{Corresponding author: dr.rohde@gmail.com ;http://
-www.peterrohde.org}
 
@@
 
-If the linear optical transformations can be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
+If the linear optical transformations \sihui{is to} be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
 This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.
 
-\section{Reconstructing the linear optical network}\label{sec:reconstruction}
+\section{Reconstructing linear optics networks}\label{sec:reconstruction}
 
+\peter{
 In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built.
 However, owing to manufacturing imperfections, a precise characterization of these devices may still be needed post-production.
-One approach for achieving this is via quantum process tomography.
-%\cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
-However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterize the network, with exponential overhead, becoming impractical for large optical networks which can contain hundreds of modes using present-day technology \cite{bib:Harris16}.
-To mitigate this problem, alternative characterization protocols have been developed.
+One approach for achieving this is via quantum process tomography, discussed in the next section.
+
+However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterise the network, with exponential overhead, becoming impractical for large optical networks which can contain hundreds of modes using present-day technology \cite{bib:Harris16}.
+To mitigate this problem, alternative characterisation protocols have been developed.
 
 Generally, the unitary matrices of $d\times d$ linear optical devices are complex $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$.
-To characterize these numbers, one can do so by injecting one- and two-photon states into the network with correlated photon detection \cite{bib:Laing12}.
+To characterise these numbers, one can do so by injecting one- and two-photon states into the network with correlated photon detection \cite{bib:Laing12}.
 With some mathematical simplifications, the parameters can be solved for using the one-photon transmissions, and the visibility of two-photon inputs.
@@
 
-An alternative method uses coherent states to probe the interferometer \cite{bib:Rahimi-Keshari13,bib:Heilmann15} instead of Fock states.
+An alternative method to process tomography is feeding coherent states to probe the interferometer \cite{bib:Rahimi-Keshari13,bib:Heilmann15} instead of Fock states.
 Such states are produced by a standard laser source, thus reducing experimental resources.
@@
 In time, the natural drift in the laser source will cause this plot to trace out an ellipse, known as a Lissajous figure, whose orientation and direction of evolution will give the phase $\theta_{jk}$ and its sign respectively.
+
+While the input-to-output amplitudes of a linear optics network may be efficiently determined (in terms of number of measurements), it does not characterise the full quantum process it implements, which may contain errors in other degrees of freedom.
+}
+
+\section{Quantum state and process tomography}\label{secQPT}
+
+\peter{When demonstrating quantum protocols experimentally it is generally absolutely critical to characterise the device prior to actual protocol execution.
+Tomography can be used to reconstruct the full density operator of an output state, and quantum process tomography to reconstruct the full process matrix implemented by a device.
+While various other measurement schemes can partially reconstruct quantum states or processes, or simply reconstruct certain parameters quantifying them, tomography is complete -- fully and uniquely reconstructing state and process matrices, from which any other measure can be determined.
+Importantly, state and process tomography require no interference or multi-qubit gates -- just separable single-qubit measurements in different bases.
+But unfortunately they require a number of measurements growing exponentially with the size of the system.
+
+State tomography is achieved by measuring expectation values in a complete basis for the state Hilbert space.
+For one qubit, for example, a complete basis is the Pauli basis, which wields the completeness relation,}
+\begin{align}
+\hat\rho = \text{tr}({\hat\rho}) + \text{tr}(\hat{X}\hat{\rho})\hat{X} + \text{tr}({\hat{Y}\hat\rho})\hat{Y} + \text{tr}(\hat{Z}{\hat\rho})\hat{Z}.
+\end{align}
+\peter{These traces correspond exactly to the expectation values in the respective bases, which are easily determined using separable measurements.
+Process tomography employs state tomography as a primitive, applying an equivalent completeness relation, but across the space of quantum processes, which may be decomposed into a basis input to output states.
+For a single qubit process this may be represented as,}
+\begin{align} \label{eq:process_matrix}
+\mathcal{E}(\hat\rho) = \sum_{i,j=1}^4 \chi_{i,j} \hat{\sigma}_i\hat\rho\,\hat{\sigma}_j^\dag.
+\end{align}
+\peter{which generalises to an arbitrary number of qubits.Here $\chi$ is the process matrix in the Pauli basis.}
+%\cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
 
@@
 Consider such a circuit of $m$ input (and output) modes that is injected with $n$ indistinguishable single photons such that $m\sim \mathcal{O}(n^2)$.
-Then, the boson sampling task consists of generating a sample from the probability distribution of single-photon measurements at the output of the circuit.
-The probability of detecting a $s_j$ photons at the $j$th output mode is
+Then, the boson-sampling task consists of generating a sample from the probability distribution of single-photon measurements at the output of the circuit.
+The probability of detecting $s_j$ photons at the $j$th output mode is
 \begin{align}
@@
 \end{align}
-where ${\rm Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times.
+%<<<<<<< HEAD:paper.tex
+where $\text{Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first $n$ columns and repeating its $j$th row $s_j$ times.
+The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson-sampling problem.
+Note that the number of configurations $|S|=\binom{n+m-1}{n}$ in the output superposition scales exponentially with $m$.
+For this reason, the boson sampler does not let us \emph{calculate} matrix permanents, as this would require knowing individual amplitudes with high precision, which would require an exponential number of samples.
+Rather, the boson sampler samples across a distribution of permanents without actually revealing any of them to the experimenter.
+Nonetheless, this is a classically intractable problem.
+It is also known that boson-sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
+
+where ${\textbf Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times.
 The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson sampling problem.
@@
 It is also known that boson sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
+%>>>>>>> origin/master:(PR final edits) linear_optics_review/paper.tex
 
@@
 Some works have resulted in interesting connections to exotic mathematical entities like immanants \cite{bib:Tan2013,bib:deGuise2014} and the multi-dimensional permanent \cite{bib:Tichy15}.
-A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14} seems particularly attractive in terms of robustness \cite{bib:Motes15}.
+A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14} seems particularly attractive in terms of robustness \cite{bib:Motes15_timebin}.
+
+\subsection{Other sampling problems -- hard \& easy}
+
+\peter{
+Numerous other sampling problems have since been described, using, for example,
+\begin{enumerate}
+	\item Cat states (superpositions of coherent states)
+	\item Photon-added coherent states .
+	\item Photon-added or -subtracted squeezed vacuum states.
+	\item Two-mode squeezed vacuum states (SPDC states).
+	\item Gaussian states.
+	\item Positive P-function states.
+\end{enumerate}
+}
+
+\peter{
+Of these, 1-4 have been shown to yield hard sampling problems under photodetection, assuming certain reasonable complexity assumptions.
+And 5-6 have been shown to implement polynomial-time classical algorithms, under Gaussian measurements.}
 
@@
 
- As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling is readily available, but executes a task that is believed to be hard classically.
+ As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling \peter{are} readily available, but executes a task that is believed to be hard classically.
 Surprisingly, an entanglement between a large number of path labels is possible with single photons in a passive linear optical device.
-Motes {\it et al.~} harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15}.
+Motes {\it et al.~}harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15_LOQM}.
 Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig.
@@
 Single photons are injected into the input modes on the left-hand-side, and a $N$-fold coincidence measurement is conducted at the output on the right-hand-side.}
-\label{fig:MORDOR}
 \end{figure}
+
+\section{Optical switching}
+
+\peter{
+Some of the protocols thus far require switching between different optical modes.
+This is achieved experimentally via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path.
+The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.
+With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.
+This is shown in Fig.
+\ref{figMZ}.
+}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.55\columnwidth]{MZ}	
+\caption{} \label{figMZ}
+\end{figure}
+
+\peter{
+This concept for switching is widely used in current labs, however it is very slow using present-day technology.
+For the purposes of fast-feedforward -- required for universal optical quantum computing for example -- we would require switching times on the order of nanoseconds, which requires the switching time to be faster than the time to the destination of the light it needs to switch.
+Presently this remains a daunting challenge, requiring much further research, with quantum memories being a candidate for loosening the switching time limitations.
+}
 
@@
 \section*{Acknowledgments}
-P.P.R.
-is funded by an ARC Future Fellowship (project FT160100397).
+PPR is funded by an ARC Future Fellowship (project FT160100397).
 This research was supported in part by the Singapore National Research Foundation under NRF Award No.

### 2017-09-10 paper.tex
Added a section on quantum simulation

@@
 
-\section{Reconstructing the linear optical network}\label{sec:reconstruction}
+\section{Reconstructing linear optics networks}\label{sec:reconstruction}
 
+\peter{
 In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built.
 However, owing to manufacturing imperfections, a precise characterization of these devices may still be needed post-production.
-One approach for achieving this is via quantum process tomography.
-%\cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
-However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterize the network, with exponential overhead, becoming impractical for large optical networks which can contain hundreds of modes using present-day technology \cite{bib:Harris16}.
-To mitigate this problem, alternative characterization protocols have been developed.
+One approach for achieving this is via quantum process tomography, discussed in the next section.
+
+However, quantum process tomography is an expensive approach in terms of the number of measurements required to characterise the network, with exponential overhead, becoming impractical for large optical networks which can contain hundreds of modes using present-day technology \cite{bib:Harris16}.
+To mitigate this problem, alternative characterisation protocols have been developed.
 
 Generally, the unitary matrices of $d\times d$ linear optical devices are complex $U_{ij}=r_{ij}e^{i\theta_{ij}}$, where $0 \leq r_{ij}\leq 1$, and $0\leq \theta_{ij}\leq 2\pi$.
-To characterize these numbers, one can do so by injecting one- and two-photon states into the network with correlated photon detection \cite{bib:Laing12}.
+To characterise these numbers, one can do so by injecting one- and two-photon states into the network with correlated photon detection \cite{bib:Laing12}.
 With some mathematical simplifications, the parameters can be solved for using the one-photon transmissions, and the visibility of two-photon inputs.
@@
 \end{align}
-where ${\rm Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first $n$ columns and repeating its $j$th row $s_j$ times.
+%<<<<<<< HEAD:paper.tex
+where $\text{Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first $n$ columns and repeating its $j$th row $s_j$ times.
 The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson-sampling problem.
@@
 It is also known that boson-sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
+
+where ${\textbf Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times.
+The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson sampling problem.
+Note that the number of configurations $|S|=\binom{n+m-1}{n}$ in the output superposition scales exponentially with $m$.
+For this reason, the boson sampler does not let us \emph{calculate} matrix permanents, as this would require knowing individual amplitudes with high precision, which would require an exponential number of samples.
+Rather, the boson sampler samples across a distribution of permanents without actually revealing any of them to the experimenter.
+Nonetheless, this is a classically intractable problem.
+It is also known that boson sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
+%>>>>>>> origin/master:(PR final edits) linear_optics_review/paper.tex
 
@@
 
+\subsection{Other sampling problems -- hard \& easy}
+
+\peter{
+Numerous other sampling problems have since been described, using, for example,
+\begin{enumerate}
+	\item Cat states (superpositions of coherent states)
+	\item Photon-added coherent states .
+	\item Photon-added or -subtracted squeezed vacuum states.
+	\item Two-mode squeezed vacuum states (SPDC states).
+	\item Gaussian states.
+	\item Positive P-function states.
+\end{enumerate}
+}
+
+\peter{
+Of these, 1-4 have been shown to yield hard sampling problems under photodetection, assuming certain reasonable complexity assumptions.
+And 5-6 have been shown to implement polynomial-time classical algorithms, under Gaussian measurements.}
+
+\sihui{
+\subsection{Quantum simulations}
+Quantum simulations is about simulating a quantum system by quantum mechanical means \cite{bib:Georgescu14}, and there are generally two approaches to achieving this.
+The first approach is known as digital quantum simulation and achieved by building a quantum computer from unitary gate components that are generated by a Hamiltonians of quantum processes.
+Progress using this approach has already been discussed in Section \ref{sec:LOQC}.The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems.
+We focus on discussing analog quantum simulation in this section.
+
+ Quantum interferometers have been proposed and in some cases implemented as quantum simulators.
+In quantum chemistry, the energy spectrum of the hydrogen molecule has been calculated using a quantum simulator comprising of a pair of entangled photons in a polarization-dependent interferometer \cite{bib:Lanyon10}.
+With two entangled photon pairs, valence-bond states have been simulated and a fiber-based tunable directional coupler gives analogue control over superpositions of different valence-bond states \cite{bib:Ma2011}.
+The model of {\sc Bosonsampling}, when coupled with two-level systems that are coupled to the ports of the quantum interferometer, simulates a general spin XY Hamiltonian \cite{bib:Olivares16}.
+Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate tight-binding Hamiltonians,  bosonic-to-fermionic behavior transitions, and even anyonic behavior.
+  }
+
 \subsection{Quantum metrology}\label{subsec:metrology}
@@
 
- As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling is readily available, but executes a task that is believed to be hard classically.
+ As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling \peter{are} readily available, but executes a task that is believed to be hard classically.
 Surprisingly, an entanglement between a large number of path labels is possible with single photons in a passive linear optical device.
@@
 
+\section{Optical switching}
+
+\peter{
+Some of the protocols thus far require switching between different optical modes.
+This is achieved experimentally via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path.
+The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.
+With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.
+This is shown in Fig.
+\ref{figMZ}.
+}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.55\columnwidth]{MZ}	
+\caption{} \label{figMZ}
+\end{figure}
+
+\peter{
+This concept for switching is widely used in current labs, however it is very slow using present-day technology.
+For the purposes of fast-feedforward -- required for universal optical quantum computing for example -- we would require switching times on the order of nanoseconds, which requires the switching time to be faster than the time to the destination of the light it needs to switch.
+Presently this remains a daunting challenge, requiring much further research, with quantum memories being a candidate for loosening the switching time limitations.
+}
+
 \section{Conclusion}

### 2017-09-11 paper.tex
Added to quantum simulations.

@@
 
-Another approach to linear optics is to pack more features known as degrees of freedom onto a single photon, and to increase the degree of control over them.
-It is possible to manipulate degrees of freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}.
-Since KLM, new proposals for linear optical quantum computations (LOQC) have surfaced \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}.
-\sihui {Some of them support new functionalities like secure delegated quantum computations \cite{bib:Barz12,bib:Fisher14}}.
-Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, and secure quantum computations \cite{bib:Tan16} that might be hard or impossible with a classical system.
-Such methods open up new ways to engineer quantum states and quantum operations, and expand the toolbox of baseline resources we have for implementing quantum computations, which could prove crucial in the race to achieve quantum supremacy.
+Another approach to linear optics is to pack more features known as degrees of 
+freedom onto a single photon, and to increase the degree of control over them. 
+It is possible to manipulate degrees of freedom like polarization, time-of-
+arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, 
+bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals 
+for linear optical quantum computations (LOQC) have surfaced 
+\cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. 
+\sihui {Some of them support new functionalities like secure delegated quantum 
+computations \cite{bib:Barz12,bib:Fisher14}}. Others do not promise 
+universality in their processing, but still performs tasks such as sampling 
+\cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, 
+and secure quantum computations \cite{bib:Tan16} that might be hard or 
+impossible with a classical system.  Such methods open up new ways to engineer 
+quantum states and quantum operations, and expand the toolbox of baseline 
+resources we have for implementing quantum computations, which could prove 
+crucial in the race to achieve quantum supremacy.
 
@@
 The first approach is known as digital quantum simulation and achieved by building a quantum computer from unitary gate components that are generated by a Hamiltonians of quantum processes.
-Progress using this approach has already been discussed in Section \ref{sec:LOQC}.The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems.
+Progress using this approach has already been discussed in Section \ref{sec:LOQC}.
+`The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems.
 We focus on discussing analog quantum simulation in this section.
@@
 The model of {\sc Bosonsampling}, when coupled with two-level systems that are coupled to the ports of the quantum interferometer, simulates a general spin XY Hamiltonian \cite{bib:Olivares16}.
-Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate tight-binding Hamiltonians,  bosonic-to-fermionic behavior transitions, and even anyonic behavior.
+Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate topological phases \cite{bib:Kitagawa12}, and behavior transitions in tight-binding Hamiltonians \cite{bib:Schreiber11, bib:Sansoni12,bib:Matthews13}.
   }

### 2017-09-13 paper.tex
Revise section on Quantum Simulation

@@
 Progress using this approach has already been discussed in Section \ref{sec:LOQC}.
-`The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems.
+The second approach is known as analog quantum simulation and involves building simpler analog devices that mimic other, perhaps less accessible, quantum systems.
 We focus on discussing analog quantum simulation in this section.
+Further discussions can be found in reviews written on quantum simulations \cite{bib:Buluta108, bib:Georgescu14}, including one specifically for optical quantum simulations \cite{bib:Aspuru-Guzik12}.
 
@@
 The model of {\sc Bosonsampling}, when coupled with two-level systems that are coupled to the ports of the quantum interferometer, simulates a general spin XY Hamiltonian \cite{bib:Olivares16}.
-Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate topological phases \cite{bib:Kitagawa12}, and behavior transitions in tight-binding Hamiltonians \cite{bib:Schreiber11, bib:Sansoni12,bib:Matthews13}.
+Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate topological phases \cite{bib:Kitagawa12}, transitions between fermionic and bosonic behavior \cite{bib:Schreiber11, bib:Sansoni12,bib:Matthews13,bib:Keil16}, fractional statistics of anyons \cite{bib:Han07,bib:Pachos09, bib:Chao-Yang09}, and excitation transfer in biological systems \cite{bib:Caruso11,bib:Viciani16}.
   }

### 2017-09-25 paper.tex
Added Section on "Repeater Networks" and added sentence on QKD not requiring interferometry

@@
 
-Another approach to linear optics is to pack more features known as degrees of 
-freedom onto a single photon, and to increase the degree of control over them. 
-It is possible to manipulate degrees of freedom like polarization, time-of-
-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, 
+Another approach to linear optics is to pack more features known as 
+degrees of freedom onto a single photon, and to increase the degree 
+of control over them. It is possible to manipulate degrees of
+freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, 
 bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals 
@@
 crucial in the race to achieve quantum supremacy.
+\sihui{Quantum key distribution (QKD) fundamentally does not require interferometry, but sound QKD protocols using Mach-Zehnder interferometer have been proposed \cite{bib:Sasaki14}, and in some cases realized \cite{bib:Takesue15}.}
 
@@
 
+\sihui{
+\subsection{Repeater networks}
+}
+
 \section{Optical switching}

### 2017-09-27 paper.tex
Added QKD review references to LOQC subsection (Section 10.1)

@@
 crucial in the race to achieve quantum supremacy.
-\sihui{Quantum key distribution (QKD) fundamentally does not require interferometry, but sound QKD protocols using Mach-Zehnder interferometer have been proposed \cite{bib:Sasaki14}, and in some cases realized \cite{bib:Takesue15}.}
 
@@
 This is followed by advances in time-bin based architecture for linear optical networks, and photodectors in Sections \ref{sec:timebins} and \ref{sec:detector} respectively.
-Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, and quantum metrology.
+Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, \sihui{ quantum metrology, and quantum repeat networks}.
 
@@
 In this way, three-qubit \cite{bib:Lanyon09,bib:Micuda13,bib:Patel16} and four-qubit \cite{bib:Starek16} gates have also been implemented using LOQC.
+\sihui{We also briefly mention here that single photons and waveplates are used in a related application, namely, quantum key distribution (QKD).
+While QKD fundamentally does not require interferometry \cite{bib:BennetBrassard84,bib:Ekert91}, some QKD protocols rely on the Mach-Zehnder \cite{Bennett92, bib:Hughes2000,bib:Sasaki14,bib:Takesue15} and Franson interferometers \cite{bib:Ali-Khan07,bib:Brougham13}.
+Practical quantum key distribution relying on photonic technology is reviewed in \cite{bib:Scarani09,bib:Hoi-Kwong14}.
+}
 

### 2017-09-29 paper.tex
Additions
Added a sentence on typical switching times in Section 3.3, and added a
new section on quantum state engineering using MZ interferometers.

@@
 Rather, fast switching can be used to spatially separate neighbouring time-bins, implement a beamsplitter operation between them, before converting back to time-bin encoding.
-An experiment has built on this idea to implement a two-qubit gate by fast switching to a polarization basis \cite{bib:Humphreys2013}.
+\sihui{Typical switch times that can be achieved are in the picoseconds range \cite{bib:Dietrich16}.} An experiment has built on this idea to implement a two-qubit gate by fast switching to a polarization basis \cite{bib:Humphreys2013}.
 Another promising advance is an ultrafast measurement technique for time bins based on converting into frequency bins \cite{bib:Donohue2013}.
@@
 To this end, continuous variable cluster states have fared better as large cluster states containing more than 10,000 entangled modes are possible  \cite{bib:Yokoyama13}, with the caveat that it is difficult to address modes individually for processing.
+
+\sihui{
+\section{Quantum state engineering based on the multi-port Mach-Zehnder interferometer}
+}
 

### 2017-10-11 paper.tex
Added new subsection on state engineering.

@@
 We will consider advances in each of these.
+\sihui{Quantum state engineering using quantum interferometers has also attracted some interest, and is discussed at the end of this section.}
 
@@
 \sihui{
-\section{Quantum state engineering based on the multi-port Mach-Zehnder interferometer}
+\subsection{Quantum state engineering based on the multi-port Mach-Zehnder interferometer}
+Linear optical inteferometers have been used for quantum state engineering.
+One well-known example is that of optical state truncation, sometimes also referred to as quantum scissors, and it happens by way of a process known as projection synthesis [figure for this?].
+Projection synthesis works by projecting an input state onto an output state by putting the former through a multiport interferometer, and then postselecting on a certain photon number output.
+Optical state truncation is a use of projection synthesis to use a continuous variable state represented in the Fock-state basis, $\ket{\phi}=\sum_{n=0}^\infty c_n\ket{n}$, to produce the normalized form of $\sum_{n=0}^d c_n\ket{n}$.
+The idea of projection synthesis was first conceived for the special case of $d=2$ \cite{bib:Pegg98, bib:Barnett99}, and later extended to $d=3$ \cite{bib:Koniorczyk2000}, and arbitrarily large $d$ \cite{bib:Miranowicz07, bib:Goyal13}.
+Notably, the scheme proposed in \cite{bib:Goyal13} uses multimode single photons and repeated uses of $d=2$ quantum scissors to extend the depth of truncation.
 }
@@
 In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains with time-bin separation $\tau$, shown in Fig.~\ref{fig:FL_arch}.
-The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the
+The inner loop has lengtxh exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the
 number of optical modes). The architecture is controlled via three 

### 2017-10-14 paper.tex
Added to Chapter on repeater networks.

@@
 \subsection{Repeater networks}
+Quantum repeaters are devices that distribute entanglement across a network, or teleport quantum states between nodes of a network.
+The purpose of such a quantum network is to communicate and process quantum information over long distances.
+While photons serve as great medium for such information transfer, many implementations of photonic repeat network require some kind of nonlinear interactions involving cavities.
+[talk about DLCZ, requiring quantum memories or feedforwarding \cite{bib:Azuma15} (not require memories but...)\cite{bib:Ewert17}]
 }

### 2017-11-20 paper.tex
Additions to Section on Repeater Network

--- 2017-10-11 paper.tex
@@
 \subsection{Repeater networks}
-}
+Quantum repeaters are devices that distribute entanglement across a network, or teleport quantum states between nodes of a network.
+The purpose of such a quantum network is to communicate and process quantum information over long distances.
+While photons serve as great medium for information transfer, many implementations of photonic repeat network require some kind of nonlinear interactions involving cavities for entanglement distillation \cite{Briegel98} [BDCZ], quantum memories \cite{Duan01}, or feedforwarding \cite{bib:Azuma15}.
+The seminal work of Duan et al.~ \cite{Duan01}, in particular, uses atomic ensemble as quantum memories.
+Single photon interference then facilitates creation of entanglement between them.
+However, this makes the repeater node susceptible to interferometric instability which later schemes improve upon it by using two-photon interference instead \cite{Zhao07,YCZCS08,CZCS07}.
+Efforts in fault-tolerant quantum communication have led to error correction codes for photon loss and dark counts, that are common errors in repeaters \cite{bib:Muralidhara14,bib:Ewert16,bib:Ewert17,bib:Muralidharan17}]
+}. These schemes can boost distances across which repeaters can act, or form tradeoffs by multiplexing, etc...
 

### 2017-12-31 paper.tex
Added a referee response file.

--- 2017-10-11 paper.tex
@@
 \subsection{Repeater networks}
+
+Quantum repeaters are devices that distribute entanglement across a network, or teleport quantum states between nodes of a network.
+The purpose of such a quantum network is to communicate and process quantum information over long distances.
+While photons serve as great medium for information transfer, many implementations of photonic repeater network require some kind of nonlinear interactions involving cavities for entanglement distillation \cite{Briegel98}, quantum memories \cite{Duan01}, or feedforwarding \cite{bib:Azuma15}.
+The seminal work of Duan et al.~ \cite{Duan01}, in particular, uses atomic ensemble as quantum memories.
+Single photon interference then facilitates creation of entanglement between them.
+However, this makes the repeater node susceptible to interferometric instability which later schemes improve upon by using two-photon interference instead \cite{Zhao07,YCZCS08,CZCS07}.
+Error correction codes for photon loss and dark counts \cite{bib:RHG05} have also been applied for use in repeaters \cite{bib:MHSDN10,bib:Muralidhara14,bib:Ewert16,bib:Ewert17}.
+Another scheme combines the use of two-photon interference and spectral multiplexing to boost high entanglement distribution rates \cite{bib:Sinclair14}.
+
+Without the use of repeaters, it has been shown that the rate transmission of a channel with loss without entanglement assistance has a linear fallout \cite{bib:TGW14}, and its bound is known as the Takeoka-Guha-Wilde (TGW) bound.
+The minimal resources required to exceed the TGW bound is a subject of active research, and so far it has been shown that the performance of the repeater schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al.
+\cite{bib:Sinclair14} are able to exceed the TGW bound.
+Other benchmarking tools have also been used to analyze many of these repeater schemes in detail \cite{bib:Muralidhara16}.
+More details about repeaters and long-distance quantum communication can be found in review papers on these subjects \cite{bib:Kimble08,bib:Sangouard11, bib:MATN15}.
+
 }
-
 \section{Optical switching}

### 2017-12-31 paper.tex
Revised section on repeater networks.

@@
 This is followed by advances in time-bin based architecture for linear optical networks, and photodectors in Sections \ref{sec:timebins} and \ref{sec:detector} respectively.
-Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, \sihui{ quantum metrology, and quantum repeat networks}.
+Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, \sihui{ quantum metrology, and quantum repeater networks}.
 
@@
 Other benchmarking tools have also been used to analyze many of these repeater schemes in detail \cite{bib:Muralidhara16}.
-More details about repeaters and long-distance quantum communication can be found in review papers on these subjects \cite{bib:Kimble08,bib:Sangouard11, bib:MATN15}.
+In terms of implementation, the greatest distance that a quantum state has been teleported to-date is 1400 km \cite{bib:Ren17}, and is demonstrated between an earth-based source with a detection unit on a satellite in space.
+This is a culmination of many decades of research from many groups in extending this distance.
+If it could be made to work with other basic units of quantum repeater networks that have been implemented \cite{bib:Kimble08,bib:Sangouard11, bib:MATN15}, a large-scale, long-distance repeater network could soon be possible.
 

### 2018-01-03 paper.tex
Revised QKD paragraph in Section 10.1.

@@
 Photons make fantastic `flying' qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}.
-In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting \cite{bib:KLM01}.
-Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
+In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting  \sihui{for spatially encoded qubits \cite{bib:KLM01}.
+At about the same time, Koashi, Yamamoto, and Imoto essentially came to the same result for polarization-encoded qubits \cite{Koashi01}.} Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
 Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.
@@
 In this way, three-qubit \cite{bib:Lanyon09,bib:Micuda13,bib:Patel16} and four-qubit \cite{bib:Starek16} gates have also been implemented using LOQC.
-\sihui{We also briefly mention here that single photons and waveplates are used in a related application, namely, quantum key distribution (QKD).
-While QKD fundamentally does not require interferometry \cite{bib:BennetBrassard84,bib:Ekert91}, some QKD protocols rely on the Mach-Zehnder \cite{Bennett92, bib:Hughes2000,bib:Sasaki14,bib:Takesue15} and Franson interferometers \cite{bib:Ali-Khan07,bib:Brougham13}.
-Practical quantum key distribution relying on photonic technology is reviewed in \cite{bib:Scarani09,bib:Hoi-Kwong14}.
-}
 
@@
   Although there has been tremendous progress in linear optics, it seems likely that an efficient, and fault-tolerant universal quantum computer will require a hybrid system.
-Nonetheless, linear optics remains fascinating platform for applications and foundation work.
+\sihui{We also briefly mention here that single photons and waveplates are used in a related application, namely, quantum key distribution (QKD).
+While QKD fundamentally does not require interferometry \cite{bib:BennetBrassard84,bib:Ekert91}, some QKD protocols rely on the Mach-Zehnder \cite{Bennett92, bib:Hughes2000,bib:Sasaki14,bib:Takesue15} and Franson interferometers \cite{bib:Ali-Khan07,bib:Brougham13}.
+Practical quantum key distribution relying on photonic technology is reviewed in \cite{bib:Scarani09,bib:Hoi-Kwong14}, and incredibly has been implemented at a distance of 1200 km by Earth-satellite transmissions \cite{bib:Liao17}.
+On the other hand, optimal quantum-optical cloning implementations \cite{bib:Fan2014} based on Mach-Zehnder interferometers have been applied to perform attacks on known quantum cryptographic schemes \cite{bib:Bartkiewicz2013,bib:Bartkiewicz2017}.
+Thus, linear optics remains fascinating platform for applications and foundation work.
+}
 
@@
 
-where ${\textbf Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first n columns and repeating its $j$th row $s_j$ times.
-The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson sampling problem.
-Note that the number of configurations $|S|=\binom{n+m-1}{n}$ in the output superposition scales exponentially with $m$.
-For this reason, the boson sampler does not let us \emph{calculate} matrix permanents, as this would require knowing individual amplitudes with high precision, which would require an exponential number of samples.
-Rather, the boson sampler samples across a distribution of permanents without actually revealing any of them to the experimenter.
-Nonetheless, this is a classically intractable problem.
-It is also known that boson sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
 %>>>>>>> origin/master:(PR final edits) linear_optics_review/paper.tex
@@
 Some of the protocols thus far require switching between different optical modes.
-This is achieved experimentally via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path.
+\sihui{One way to achieve this experimentally for time-bin qubits is} via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path.
 The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.

### 2018-01-06 paper.tex
Revision to Section 9.

@@
 
-\title{The resurgence of the linear optics interferometer --- recent advances \& applications}
+\title{The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications}
 
@@
 
-The promises offered by linear optics have spearheaded many technical advancements.
-One of the major successes for linear optics is the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}.
+The promises offered by linear optics have spearheaded many \sihui{scientific and} technical advancements.
+One of the major successes for linear optics is \sihui{the detection of gravitational waves by the LIGO experiments based on the Michelson interferometer \cite{bib:LIGO2015}.
+Another is} the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}.
 The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized.
@@
 \includegraphics[width=0.4\columnwidth]{reck}
-\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.} \label{fig:Reck}	
+\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.
+\sihui{This setup describes a generalized multi-port Mach-Zehnder interferometer}} \label{fig:Reck}
 \end{figure}
@@
 \end{align}
-Detailed reviews have been written about these detectors \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few important examples.
+\sihui{Theoretical modeling of these photodetectors can be made to include realistic effects such as detector finite efficiency, finite-number resolution, dark counts, and crosstalk.
+These effects are typically described as projections onto mixed states \cite{bib:BARNETT1998}, and their outcomes are represented by positive-operator valued measures.
+Such modeling allows us to analyze these realistic effects on various quantum information protocols, see for {\it e.g.~}\cite{bib:Ozdemir2001,bib:Sperling2014,bib:Tan2016}.}
 
-A common example of a non-PNR detector is the avalanche photodiode (APD).
+\sihui{There are many different types of photodetectors.
+Detailed reviews have been written about \sihui{them} \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few important examples.
+}A common example of a non-PNR detector is the avalanche photodiode (APD).
 These devices are made up of semiconductor material, usually silicon, which generate an electron that quickly generates a cascade of electrons.
@@
 Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Heilmanndc15}.
+
+\section{Optical switching}
+
+\peter{
+Some of the protocols thus far require switching between different optical modes.
+\sihui{One way to achieve this experimentally for time-bin qubits is} via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path.
+The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.
+With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.
+This is shown in Fig.
+\ref{figMZ}.
+}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.55\columnwidth]{MZ}	
+\caption{} \label{figMZ}
+\end{figure}
+
+\peter{
+This concept for switching is widely used in current labs, however it is very slow using present-day technology.
+For the purposes of fast-feedforward -- required for universal optical quantum computing for example -- we would require switching times on the order of nanoseconds, which requires the switching time to be faster than the time to the destination of the light it needs to switch.
+Presently this remains a daunting challenge, requiring much further research, with quantum memories being a candidate for loosening the switching time limitations.
+}
 
@@
 This can be challenging given the limited resources to begin with.
-Comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05}, hence we will focus on recent advances.
+\sihui{Various linear-optical implementations of two-qubit gates important for approximately universal quantum computation are listed in Ref.~\cite{bib:Bartkowiak2010}, and comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05}, hence we will focus on recent advances.}
 
@@
 }
-\section{Optical switching}
-
-\peter{
-Some of the protocols thus far require switching between different optical modes.
-\sihui{One way to achieve this experimentally for time-bin qubits is} via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path.
-The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.
-With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.
-This is shown in Fig.
-\ref{figMZ}.
-}
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=0.55\columnwidth]{MZ}	
-\caption{} \label{figMZ}
-\end{figure}
-
-\peter{
-This concept for switching is widely used in current labs, however it is very slow using present-day technology.
-For the purposes of fast-feedforward -- required for universal optical quantum computing for example -- we would require switching times on the order of nanoseconds, which requires the switching time to be faster than the time to the destination of the light it needs to switch.
-Presently this remains a daunting challenge, requiring much further research, with quantum memories being a candidate for loosening the switching time limitations.
-}
 
@@
 \bibliographystyle{elsarticle-num}
+
 %%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-08 paper.tex
Added the experiment of Carolan et al. to Sec. 4 as Fig. 2.

@@
 
-Linear optics play a prominent role in quantum information processing.
+Linear optics play a prominent role in quantum information processing \cite{bib:LovettKok}.
 Photons make fantastic `flying' qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}.
@@
 \includegraphics[width=0.4\columnwidth]{reck}
-\caption{Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters.
-\sihui{This setup describes a generalized multi-port Mach-Zehnder interferometer}} \label{fig:Reck}
+\caption{Efficient decomposition of arbitrary linear optics 
+networks into a sequence of beamsplitters and phase-shifters. 
+\sihui{This setup describes a generalized multi-port Mach-
+Zehnder interferometer}} \label{fig:Reck}	
+\end{figure}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=\columnwidth]{configMZI}
+\caption{ \sihui{(a) Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters represented as subunitaries, $D_i$.
+These subunitaries are controlled via their photon amplitudes ($\alpha_{i,j}$) and phases ($\phi_{i,j}$).
+This setup describes a generalized multi-port Mach-Zehnder interferometer, and is a universal linear-optical processing unit.
+(b) A state-of-art implementation of a universal linear-optical processing unit is shown.
+The processor has 6 inputs entering from the left, and 6 outputs leaving to the right, and is constructed from a cascade of 15 Mach-Zehnder interferometers.
+The classical control and processing unit sets the parameters for the interferometer, and actively cools it.
+Adapted from \cite{bib:Carolan15}.}} \label{fig:Carolan}
 \end{figure}
@@
 Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}.
-Later, it was shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
+\sihui{Such a decomposition and its implementation on an integrated photonic chip are shown in Fig.~\ref{fig:Carolan}.
+} Later, it was shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
 However, they do not provide an explicit construction for arbitrary unitaries.

### 2018-01-12 paper.tex
Added sparsity concepts to Section 6.

@@
 
-In the last decade, single photons have been produced mainly through a nonlinear optical process know as spontaneous parametric down-conversion (SPDC), a nonlinear optical process.
-SPDC produces single photons in correlated pairs that has been a staple source of entanglement.
-Through developments in production, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
+In the last decade, single photons have been produced mainly through \sihui{nonlinear optical processes know as spontaneous parametric down-conversion (SPDC) and spontaneous four-wave mixing (SFWM) \cite{bib:Eisaman11,bib:Xiong16,bib:Solntsev17}.} \sihui{Both SPDC and SFWM produce} single photons in correlated pairs that has been a staple source of entanglement.
+\sihui{However, SPDC uses up one pump photons per pair, while SFWM requires two.} Through developments in production, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
 Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical labs, and three or four photons have become commonplace \cite{bib:Spagnolo12, bib:Tillmann13, bib:Spring13,bib:Broome13}.
@@
 \includegraphics[width=\columnwidth]{configMZI}
-\caption{ \sihui{(a) Efficient decomposition of arbitrary linear optics networks into a sequence of beamsplitters and phase-shifters represented as subunitaries, $D_i$.
+\caption{ \sihui{(a) A decomposition of arbitrary linear optics networks into a sequence of subunitaries, $D_i$, made up of Mach-Zehnder interferometers, and is a universal linear-optical processing unit.
 These subunitaries are controlled via their photon amplitudes ($\alpha_{i,j}$) and phases ($\phi_{i,j}$).
-This setup describes a generalized multi-port Mach-Zehnder interferometer, and is a universal linear-optical processing unit.
 (b) A state-of-art implementation of a universal linear-optical processing unit is shown.
@@
 
-Alternatively, Mach-Zedner interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}.
+Alternatively, \sihui{Mach-Zehnder} interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}.
 \sihui{Such a decomposition and its implementation on an integrated photonic chip are shown in Fig.~\ref{fig:Carolan}.
@@
 \peter{These traces correspond exactly to the expectation values in the respective bases, which are easily determined using separable measurements.
-Process tomography employs state tomography as a primitive, applying an equivalent completeness relation, but across the space of quantum processes, which may be decomposed into a basis input to output states.
+\sihui{Sometimes, it is possible to be able to do a tomography from an incomplete number of measurements, {\it i.e.} a number that is less than the number of expectation values, and it is possible using compressed sensing provided some sparsity conditions are met \cite{bib:GLFBE2010,bib:Titchener16,bib:Oren16}.} Process tomography employs state tomography as a primitive, applying an equivalent completeness relation, but across the space of quantum processes, which may be decomposed into a basis input to output states.
 For a single qubit process this may be represented as,}
@@
 \end{align}
-\peter{which generalises to an arbitrary number of qubits.Here $\chi$ is the process matrix in the Pauli basis.}
+\peter{which generalises to an arbitrary number of qubits. Here $\chi$ is the process matrix in the Pauli basis.}
 %\cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.

### 2018-01-24 paper.tex
Revised the section on photodetection
Added Table comparing experimental values for PNR detectors.

@@
 \usepackage{framed,multirow}
-\usepackage{hyperref,mathrsfs,amsmath,amssymb,latexsym}
+\usepackage{hyperref,mathrsfs,amsmath,amssymb,latexsym,array,hhline}
 \newcommand{\bra}[1]{\langle#1|}
@@
 APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in a broad spectrum of wavelengths.
-% A downside to using APD is their deadtime. This is a period of time 
-%following an avalanche during which the avalanche is stopped by a 
-%quenching circuit to reset the APD. No photons can be detected during the 
-%deadtime and contributes to photon loss in an APD.
-Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector.
-This detector operates in its superconducting phase just below the critical density, and it phase changes back to normal when a photon is absorbed.
+\sihui{It is the preferred detection method in quantum information protocols as they are widely available, and do not require special environments to run like some of the other detectors, as we discuss later in this section.
+Nonetheless, they have their limitations.
+A downside to using APD is their deadtime, which is a period of time following an avalanche during which the avalanche is stopped by a quenching circuit to reset the APD.
+No photons can be detected during the
+deadtime and contributes to photon loss in an APD.
+Deadtime delays for APDs range from tens of nanoseconds to $\mu$s.} Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector.
+This detector operates in its superconducting phase just below the critical density, and it\sihui{s} phase changes back to normal when a photon is absorbed.
 This causes a spike in current around it, which, when detected, would indicate the absorption of the photon.
+\sihui{This SNSPD detector tends to be faster than the APD detector with lower dark count rates.
+However, they require low operating temperatures of 4K maintained by special cryogenic equipment that are expensive and bulky.}
 
@@
 The principle it operates on is very similar to the SNSPD, but with a much higher sensitivity that allows it to detect the energy of single photons.
-%low dark count rates. However, they are quite slow, have low maximum 
-%counting rates, and are costly to operate due to their very low operating 
-%temperatures. 
-The visible light photon counter (VLPC) is another kind of PNR detector.
+\sihui{They have low dark count rates, however, they are also quite slow, have low maximum counting rates, and, like the SNSPD detectors, are costly to operate due to their very low operating temperatures.} The visible light photon counter (VLPC) is another kind of PNR detector.
 The way VLPC works is in principle very similar to the APD, but with an additional layer of silicon that is lightly doped with arsenic (As).
@@
 Thus, the output electrical signal is just proportional to the number of detected photons.
+\sihui{The VLPC can achieve a high quantum efficiency, in fact almost as high as that of the TES, and has a distinct advantage over the TES of not requiring superconducting temperatures.
+However, they do suffer from high dark count rate, and low speeds.}
 Last, PNR detectors can be created by connecting many non-PNR detectors in parallel to one another, and summing the signals at the output.
@@
 Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Heilmanndc15}.
+\sihui{Some characteristic experimental values for the detector efficiency, timing jitter, dark count rates, and maximum photon number of different PNR detectors are given in Table \ref{table:PNR}.}
+
+\begin{table}[t]
+\centering
+\begin{tabular}{| >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{3cm} | >{\centering\arraybackslash}m{2cm} |>{\centering\arraybackslash}m{2cm} |>{\centering\arraybackslash}m{2cm} |}
+ \hline 
+\vspace{0.8mm} PNR & detector efficiency (\%) & timing jitter ($ns$) & dark counts ($1/s$) & maximum photon number \\ \hhline{|=|=|=|=|=|}
+&&&& \\
+  VLPC \cite{bib:Waks03}   & 85@543$nm$  & 2 & 20000 & 5 \\
+  & & & & \\
+  TES \cite{bib:Lita08} & 95@1556 & 100 & - & 7\\
+ TES \cite{bib:MillerNam03} & 20@1310$nm$  & 100 & $<10^{-3}$ & 15 \\
+  & 20@1550$nm$ & & & \\
+  TES \cite{bib:Gerrits12} & 89@1550$nm$ & - & - & 1000 \\
+  &&&& \\
+ Parallel SNSPD \cite{bib:Divochiy08} & 2@1300 & 0.05 & 0.15 & 4 \\
+ &&&&\\
+ Series SNSPD \cite{bib:Mattioli16} & 0.5@1310 & 0.116 & - & 24\\
+&&&& \\
+ \hline
+\end{tabular}
+\caption{Comparison of performance between some PNR detectors.}\label{table:PNR}
+\end{table}
 
@@
 Some of the protocols thus far require switching between different optical modes.
-\sihui{One way to achieve this experimentally for time-bin qubits is} via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path.
+\sihui{One way to achieve this experimentally for time-bin qubits is} via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path \cite{bib:Takesue14}.
 The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.
@@
 \ref{figMZ}.
+\sihui{Ref.~\cite{bib:Takesue14} reports a switching time of 100 picoseconds for this type of switch.}
 }
@@
 
-\peter{
-This concept for switching is widely used in current labs, however it is very slow using present-day technology.
-For the purposes of fast-feedforward -- required for universal optical quantum computing for example -- we would require switching times on the order of nanoseconds, which requires the switching time to be faster than the time to the destination of the light it needs to switch.
+ \sihui{It is also possible to perform switching of photons by first converting temporal and spatial labels of the photon to a polarization one, and then perform a fast polarization switch before converting it back \cite{bib:HAK11,bib:Humphreys13}.
+Such switches are able to achieve a polarization switch within a 10 picoseconds time window.
+Other ways rely on conditional scattering of signal photons on ultrafast timescales, usually involving coupling between field modes and strongly correlated systems \cite{bib:Volz2012, bib:Bose2012, bib:Dietrich16}.
+The typical speed for this type of switching is of order of picoseconds \cite{bib:Dietrich16}.
+ }
+
+\sihui{This concept for switching is widely used in current labs, however it is very slow using present-day technology.
+Although switching on its own can be completed in a timespan of the order of picoseconds, the process is slowed by the time needed for its control electronic.
+This is especially crucial in switching for the purposes of fast-feedforward that is required, for example, for universal optical quantum computing.
+In this application, we would require total switching times, including time for control electronics to respond, on the order of nanoseconds, {\it i.e.~}faster than the time to the destination of the light it needs to switch, and this is still not possible.
 Presently this remains a daunting challenge, requiring much further research, with quantum memories being a candidate for loosening the switching time limitations.
 }
+
+%\peter{
+%This concept for switching is widely used in current 
+%labs, however it is very slow using present-day 
+%technology. For the purposes of fast-feedforward -- 
+%required for universal optical quantum computing for 
+%example -- we would require switching times on the order 
+%of nanoseconds, which requires the switching time to be 
+%faster than the time to the destination of the light it 
+%needs to switch. Presently this remains a daunting 
+%challenge, requiring much further research, with quantum 
+%memories being a candidate for loosening the switching 
+%time limitations.
+%}
 
@@
 \subsection{Quantum metrology}\label{subsec:metrology}
-An archetypal task for quantum metrology is the following: Given a Mach-Zedner interferometer, with an unknown phase shift of magnitude $\varphi$ inserted in one of the two paths (see Fig.
+An archetypal task for quantum metrology is the following: Given a Mach-\sihui{Zehnder} interferometer, with an unknown phase shift of magnitude $\varphi$ inserted in one of the two paths (see Fig.
 \ref{fig:MZ}), can one deduce $\varphi$ via a judicious use of quantum states and measurements with a higher sensitivity than that of a completely classical interferometer?

### 2018-02-04 paper.tex
Updated, and cleaned up the bibliography.

@@
 \usepackage{revip}
-\usepackage{framed,multirow}
+\usepackage{framed,multirow,threeparttable}
 \usepackage{hyperref,mathrsfs,amsmath,amssymb,latexsym,array,hhline}
@@
 Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Heilmanndc15}.
-\sihui{Some characteristic experimental values for the detector efficiency, timing jitter, dark count rates, and maximum photon number of different PNR detectors are given in Table \ref{table:PNR}.}
+\sihui{Some characteristic experimental values for the detector efficiency, timing jitter, dark count rates, and maximum photon number of different photodetectors are given in Table \ref{table:PNR}.}
 
-\begin{table}[t]
+\begin{table}[t]\label{table:PNR}
 \centering
+\begin{threeparttable}
+\caption{Comparison of performance between some photodetectors. In part adapted from \cite{bib:Eisaman11}.}\label{table:PNR}
 \begin{tabular}{| >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{3cm} | >{\centering\arraybackslash}m{2cm} |>{\centering\arraybackslash}m{2cm} |>{\centering\arraybackslash}m{2cm} |}
  \hline 
-\vspace{0.8mm} PNR & detector efficiency (\%) & timing jitter ($ns$) & dark counts ($1/s$) & maximum photon number \\ \hhline{|=|=|=|=|=|}
+\vspace{0.8mm} Detector type & detector efficiency (\%) & timing jitter ($ns$) & dark counts ($1/s$) & maximum photon number \\ \hhline{|=|=|=|=|=|}
 &&&& \\
+APD \cite{bib:Webster2012} & 72@560$nm$ & 0.09 & 18 & 1\tnote{a} \\
+&&&& \\
+SNSPD \cite{bib:Takesue07} & 0.7@1550$nm$ & 0.06 & 10 & 1\tnote{a} \\
+&&&&\\
   VLPC \cite{bib:Waks03}   & 85@543$nm$  & 2 & 20000 & 5 \\
@@
 \end{tabular}
-\caption{Comparison of performance between some PNR detectors.}\label{table:PNR}
+\begin{tablenotes}
+\item[a] Has no photon-number-resolving capabilities.
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
-
+%\footnote{Has no photon-number-resolving capabilities.}
 \section{Optical switching}

### 2018-02-07 paper.tex
Touch up
Grammar check, style check, added figure for quantum scissors, bib
check.

@@
 In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting  \sihui{for spatially encoded qubits \cite{bib:KLM01}.
-At about the same time, Koashi, Yamamoto, and Imoto essentially came to the same result for polarization-encoded qubits \cite{Koashi01}.} Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
+At about the same time, Koashi, Yamamoto, and Imoto (KYI) essentially came to the same result for polarization-encoded qubits \cite{Koashi01}.} Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
 Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.
@@
 \sihui{However, SPDC uses up one pump photons per pair, while SFWM requires two.} Through developments in production, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
-Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical labs, and three or four photons have become commonplace \cite{bib:Spagnolo12, bib:Tillmann13, bib:Spring13,bib:Broome13}.
+Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical \sihui{laboratories}, and three or four photons have become commonplace \cite{bib:Spagnolo12, bib:Tillmann13, bib:Spring13,bib:Broome13, bib:Crespi13}.
 Experiments using up to ten photons have been demonstrated \cite{bib:WangChen16, bib:Chen17}.
 We have also seen the meteoric rise of quantum dots in the role for producing single photons \cite{bib:Ding16,bib:WangHe16, bib:213601}.
-They are a scalable source of single photons which are highly indistinguishable, and are produced on demand--a significant advantage over SPDC which is an inherently probabilistic process.
+They are a scalable source of single photons which are highly indistinguishable, and are produced on demand--a significant advantage over \sihui{nonlinear optical processes which are inherently probabilistic.}
 
@@
 freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, 
-bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM, new proposals 
+bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM \sihui{and KYI}, new proposals 
 for linear optical quantum computations (LOQC) have surfaced 
@@
 \sihui {Some of them support new functionalities like secure delegated quantum 
-computations \cite{bib:Barz12,bib:Fisher14}}. Others do not promise 
-universality in their processing, but still performs tasks such as sampling 
-\cite{bib:Aaronson11}, \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}}, 
-and secure quantum computations \cite{bib:Tan16} that might be hard or 
+computations \cite{bib:Barz12,bib:Fisher14, bib:Tan16}}.
+Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, and \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}} that might be hard or
 impossible with a classical system.  Such methods open up new ways to engineer 
@@
 A full quantum tomography is costly and time-consuming.
-Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction}.
+Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction} \sihui{while quantum tomography is briefly discussed in Section \ref{secQPT}}.
 In Section \ref{sec:state}, we recap the experimental breakthroughs in state preparation of single photons, and some entangled quantum states.
-This is followed by advances in time-bin based architecture for linear optical networks, and photodectors in Sections \ref{sec:timebins} and \ref{sec:detector} respectively.
-Last, but not least, we review applications for linear optical interferometry in LOQC, {\sc bosonsampling}, \sihui{ quantum metrology, and quantum repeater networks}.
+This is followed by advances in time-bin based architecture for linear optical networks, \sihui{photodectors, and optical switches in Sections \ref{sec:timebins}, \ref{sec:detector}, and \ref{sec:switch} respectively}.
+Last, but not least, we review applications for linear optical interferometry in \sihui{Section \ref{sec:applications}}.
 
@@
 \end{align}
-where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in SU(d)$.
+where $a_j^\dag$ and $b_i^\dag$ are the creation operators of a single input and output photon in the $j$-th and $i$-th modes respectively, and $U\in {\rm SU}(d)$.
 All such transformations can be expressed as sequences of beamsplitters and phase-shifters \cite{bib:Reck1994} (see Section \ref{sec:decomp}).
@@
 Control of indistinguishability of these photons may enable future applications.
-Mathematical methods have been developed to deal with partial distinguishabilities among interfering photons, including those using group theory \cite{bib:Tan2013,bib:deGuise2014,bib:deGuise2015}, and quantum-to-classical transitions \cite{bib:Ra2013}.
+Mathematical methods have been developed to deal with partial distinguishabilities among interfering photons, including those using group theory \cite{bib:Tan2013,bib:deGuise2014,bib:Shchesnovich15,bib:deGuise2015}, and quantum-to-classical transitions \cite{bib:Ra2013}.
 Recently, by controlling multiple degrees of freedom of single photons, genuine three-photon interference that has no independent entanglement between any two subpairs of photons was demonstrated  \cite{bib:Agne17,bib:Menssen17}.
@@
 In dual-rail encoding, a single photon encodes a logical qubit as a superposition across two spatial modes,
-\begin{align}
+\begin{align}\label{eq:dualrail}
 \ket\psi_L = \alpha\ket{1,0} + \beta\ket{0,1},
@@
 \centering
-\includegraphics[width=0.4\columnwidth]{reck}
+\includegraphics[width=0.55\columnwidth]{reck}
 \caption{Efficient decomposition of arbitrary linear optics 
 networks into a sequence of beamsplitters and phase-shifters. 
-\sihui{This setup describes a generalized multi-port Mach-
-Zehnder interferometer}} \label{fig:Reck}	
+\sihui{This setup describes a generalized $n\times n$ multi-port Mach-Zehnder interferometer. Adapted from \cite{bib:Reck1994}.}} \label{fig:Reck}	
 \end{figure}
@@
 \peter{These traces correspond exactly to the expectation values in the respective bases, which are easily determined using separable measurements.
-\sihui{Sometimes, it is possible to be able to do a tomography from an incomplete number of measurements, {\it i.e.} a number that is less than the number of expectation values, and it is possible using compressed sensing provided some sparsity conditions are met \cite{bib:GLFBE2010,bib:Titchener16,bib:Oren16}.} Process tomography employs state tomography as a primitive, applying an equivalent completeness relation, but across the space of quantum processes, which may be decomposed into a basis input to output states.
+\sihui{Sometimes, it is possible to be able to do a tomography from an incomplete number of measurements, {\it i.e.} a number that is less than the number of expectation values, and it is possible using compressed sensing provided some sparsity conditions are met \cite{bib:GLFBE2010,bib:Titchener16,bib:Oren16}.
+In cases where one only wishes to know if a given state is close to a presumed state, one can perform a certification test instead of state tomography \cite{bib:Aolita15}.}
+
+Process tomography employs state tomography as a primitive, applying an equivalent completeness relation, but across the space of quantum processes, which may be decomposed into a basis input to output states.
 For a single qubit process this may be represented as,}
@@
 \end{align}
-in the second quantization representation. This notation is commonly used in quantum metrological applications.
+in the second quantization representation, \sihui{and the basis is the same as that for eq.~(\ref{eq:dualrail})}. This notation is commonly used in quantum metrological applications.
 
@@
 Linear optical inteferometers have been used for quantum state engineering.
-One well-known example is that of optical state truncation, sometimes also referred to as quantum scissors, and it happens by way of a process known as projection synthesis [figure for this?].
+One well-known example is that of optical state truncation, sometimes also referred to as quantum scissors, and it happens by way of a process known as projection synthesis.
 Projection synthesis works by projecting an input state onto an output state by putting the former through a multiport interferometer, and then postselecting on a certain photon number output.
 Optical state truncation is a use of projection synthesis to use a continuous variable state represented in the Fock-state basis, $\ket{\phi}=\sum_{n=0}^\infty c_n\ket{n}$, to produce the normalized form of $\sum_{n=0}^d c_n\ket{n}$.
+An example of the interferometer used for optical state truncation for the case $d=1$ is shown in Fig.~\ref{fig:qscissors}.
 The idea of projection synthesis was first conceived for the special case of $d=2$ \cite{bib:Pegg98, bib:Barnett99}, and later extended to $d=3$ \cite{bib:Koniorczyk2000}, and arbitrarily large $d$ \cite{bib:Miranowicz07, bib:Goyal13}.
@@
 
+\begin{figure}[!htb]
+\centering
+\includegraphics[width=0.3\columnwidth]{qscissors}
+\caption{Figure showing optical state truncation for $d=1$.
+The input state is $\ket{\phi}$, and when the photodetectors $D_1$ and $D_2$ register one and zero photons respectively, the output state is $\ket{\phi}_{\rm out}=c_0\ket{0}+c_1\ket{1}$ with an appropriate normalization factor.
+Adapted from \cite{bib:Pegg98}.} \label{fig:qscissors}
+\end{figure}
+
 \section{Time-bin loop-based architecture for linear optical networks}\label{sec:timebins}
 
-Using time-bin encoding of optical qubits, the obvious question is how to perform operations upon them.
+\sihui{When} using time-bin encoding of optical qubits, the obvious question is\sihui{: how do we perform single-qubit and two-qubit} operations upon them.
 In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains with time-bin separation $\tau$, shown in Fig.~\ref{fig:FL_arch}.
-The inner loop has lengtxh exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the
+The inner loop has length exactly $\tau$, while the outer one has length $>n\tau$ ($n$ is the
 number of optical modes). The architecture is controlled via three 
@@
 The above description applies to passive linear optics, which is sufficient for protocols such as {\sc BosonSampling}, but insufficient for universal optical quantum computation, which requires the addition of ancillary states, and measurement with fast-feedforward.
-To address this, it was shown in \cite{Rohde15} that by dynamically preparing ancillary pulse-trains (from the already-existing source), classically controlled by time-resolved measurements at the output, and changing the switching sequence, we can effectively couple in and out arbitrary subsets of the optical modes, enabling partial measurements to be implemented.
+To address this, it was shown in \cite{Rohde15} that \sihui{partial measurements can be implemented by coupling in and out arbitrary subsets of the optical modes.
+The coupling is in turn achieved via dynamically preparing ancillary pulse-trains (using the already existing source) that are classically controlled by time-resolved measurements at the output, and changing the switching sequence conditional on these measurement outcomes.}
 
 \section{Photodetection}\label{sec:detector}
+
+\begin{table}[t]\label{table:PNR}
+\centering
+\begin{threeparttable}
+\caption{Comparison of performance between some photodetectors. In part adapted from \cite{bib:Eisaman11}.}\label{table:PNR}
+\begin{tabular}{| >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{3cm} | >{\centering\arraybackslash}m{2cm} |>{\centering\arraybackslash}m{2cm} |>{\centering\arraybackslash}m{2cm} |}
+ \hline 
+\vspace{0.8mm} Detector type & detector efficiency (\%) & timing jitter ($ns$) & dark counts ($1/s$) & maximum photon number \\ \hhline{|=|=|=|=|=|}
+&&&& \\
+APD \cite{bib:Webster2012} & 72@560$nm$ & 0.09 & 18 & 1\tnote{a} \\
+&&&& \\
+SNSPD \cite{bib:Takesue07} & 0.7@1550$nm$ & 0.06 & 10 & 1\tnote{a} \\
+&&&&\\
+  VLPC \cite{bib:Waks03}   & 85@543$nm$  & 2 & 20 000 & 5 \\
+  & & & & \\
+  TES \cite{bib:Lita08} & 95@1556$nm$ & 100 & - & 7\\
+ TES \cite{bib:MillerNam03} & 20@1310$nm$  & 100 & $<10^{-3}$ & 15 \\
+  & 20@1550$nm$ & & & \\
+  TES \cite{bib:Gerrits12} & 89@1550$nm$ & - & - & 1000 \\
+  &&&& \\
+ Parallel SNSPD \cite{bib:Divochiy08} & 2@1300$nm$ & 0.05 & 0.15 & 4 \\
+ &&&&\\
+ Series SNSPD \cite{bib:Mattioli16} & 0.5@1310$nm$ & 0.116 & - & 24\\
+ &&&&\\
+ MPPC \cite{bib:Afek09} & 50@400$nm$ & 20 & 115 000 & 10 \\
+ & 8@800$nm$&&& \\
+&&&& \\
+ \hline
+\end{tabular}
+\begin{tablenotes}
+\item[a] Has no photon-number-resolving capabilities.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
 
@@
 \end{align}
-\sihui{Theoretical modeling of these photodetectors can be made to include realistic effects such as detector finite efficiency, finite-number resolution, dark counts, and crosstalk.
+\sihui{Theoretical modeling of these photodetectors can be made to include realistic effects such as detector finite efficiency, finite-number resolution, dark counts, and crosstalk \cite{bib:LeeYurtsever04, bib:Ramilli10,bib:Kalashnikov12}.
 These effects are typically described as projections onto mixed states \cite{bib:BARNETT1998}, and their outcomes are represented by positive-operator valued measures.
-Such modeling allows us to analyze these realistic effects on various quantum information protocols, see for {\it e.g.~}\cite{bib:Ozdemir2001,bib:Sperling2014,bib:Tan2016}.}
+Such modeling allows us to analyze these realistic effects on various quantum information protocols, see for {\it e.g.~}\cite{bib:Ozdemir2001,bib:Sperling2014, bib:Matthews16}, and update our characterization of non-classicality \cite{bib:Sperlingbinomial12,bib:Kalashnikov12b, bib:Sperling15,bib:Heilmanndc15, bib:Tan2016}.}
 
@@
 For instance, like in the theoretical proposal of \cite{bib:Sperling12}.
-Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and APDs \cite{bib:Kalashnikov12,bib:Chrapkiewicz14,bib:Heilmanndc15}.
-\sihui{Some characteristic experimental values for the detector efficiency, timing jitter, dark count rates, and maximum photon number of different photodetectors are given in Table \ref{table:PNR}.}
+Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and spatially multiplexed APDs known as multi-pixel photon counters (MPPCs) \cite{bib:Afek09, bib:Chrapkiewicz14}.
+\sihui{Characteristic experimental values for the detector efficiency, timing jitter, dark count rates, and maximum photon number of some types of photodetectors are given in Table \ref{table:PNR}.}
 
-\begin{table}[t]\label{table:PNR}
-\centering
-\begin{threeparttable}
-\caption{Comparison of performance between some photodetectors. In part adapted from \cite{bib:Eisaman11}.}\label{table:PNR}
-\begin{tabular}{| >{\centering\arraybackslash}m{2cm} | >{\centering\arraybackslash}m{3cm} | >{\centering\arraybackslash}m{2cm} |>{\centering\arraybackslash}m{2cm} |>{\centering\arraybackslash}m{2cm} |}
- \hline 
-\vspace{0.8mm} Detector type & detector efficiency (\%) & timing jitter ($ns$) & dark counts ($1/s$) & maximum photon number \\ \hhline{|=|=|=|=|=|}
-&&&& \\
-APD \cite{bib:Webster2012} & 72@560$nm$ & 0.09 & 18 & 1\tnote{a} \\
-&&&& \\
-SNSPD \cite{bib:Takesue07} & 0.7@1550$nm$ & 0.06 & 10 & 1\tnote{a} \\
-&&&&\\
-  VLPC \cite{bib:Waks03}   & 85@543$nm$  & 2 & 20000 & 5 \\
-  & & & & \\
-  TES \cite{bib:Lita08} & 95@1556 & 100 & - & 7\\
- TES \cite{bib:MillerNam03} & 20@1310$nm$  & 100 & $<10^{-3}$ & 15 \\
-  & 20@1550$nm$ & & & \\
-  TES \cite{bib:Gerrits12} & 89@1550$nm$ & - & - & 1000 \\
-  &&&& \\
- Parallel SNSPD \cite{bib:Divochiy08} & 2@1300 & 0.05 & 0.15 & 4 \\
- &&&&\\
- Series SNSPD \cite{bib:Mattioli16} & 0.5@1310 & 0.116 & - & 24\\
-&&&& \\
- \hline
-\end{tabular}
-\begin{tablenotes}
-\item[a] Has no photon-number-resolving capabilities.
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-%\footnote{Has no photon-number-resolving capabilities.}
-\section{Optical switching}
+\section{Optical switching}\label{sec:switch}
 
@@
 Some of the protocols thus far require switching between different optical modes.
-\sihui{One way to achieve this experimentally for time-bin qubits is} via a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path \cite{bib:Takesue14}.
+\sihui{One way to achieve this experimentally for time-bin qubits uses} a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path \cite{bib:Takesue14} (see Fig.~\ref{figMZ}).
 The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.
-With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.
-This is shown in Fig.
-\ref{figMZ}.
-\sihui{Ref.~\cite{bib:Takesue14} reports a switching time of 100 picoseconds for this type of switch.}
+With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.\sihui{Ref.~\cite{bib:Takesue14} reports a switching time of 100 picoseconds for this type of switch.}
 }
@@
 
- \sihui{It is also possible to perform switching of photons by first converting temporal and spatial labels of the photon to a polarization one, and then perform a fast polarization switch before converting it back \cite{bib:HAK11,bib:Humphreys13}.
+ \sihui{Another way to perform switching is to first convert temporal and spatial labels of the photon to a polarization one, and then perform a fast polarization switch before converting it back \cite{bib:HAK11,bib:Humphreys13}.
 Such switches are able to achieve a polarization switch within a 10 picoseconds time window.
@@
 
-\sihui{This concept for switching is widely used in current labs, however it is very slow using present-day technology.
-Although switching on its own can be completed in a timespan of the order of picoseconds, the process is slowed by the time needed for its control electronic.
-This is especially crucial in switching for the purposes of fast-feedforward that is required, for example, for universal optical quantum computing.
+\sihui{This concept for switching is widely used in current laboratories, however it is very slow using present-day technology.
+Although switching on its own can be completed in a timespan of the order of picoseconds, the process is slowed by the response time needed for its electronic control.
+Overcoming this hurdle is especially crucial in switching for fast-feedforward that is required, for example, in universal optical quantum computing.
 In this application, we would require total switching times, including time for control electronics to respond, on the order of nanoseconds, {\it i.e.~}faster than the time to the destination of the light it needs to switch, and this is still not possible.
@@
 
-\section{Applications for linear optics interferometry}
+\section{Applications for linear optics interferometry}\label{sec:applications}
 
@@
   Although there has been tremendous progress in linear optics, it seems likely that an efficient, and fault-tolerant universal quantum computer will require a hybrid system.
-\sihui{We also briefly mention here that single photons and waveplates are used in a related application, namely, quantum key distribution (QKD).
+\sihui{Linear optics is still interesting in its own right for other tasks as discussed in the remainder of this sections.
+We also briefly mention here that single photons and waveplates are used in an already commercial application, namely, quantum key distribution (QKD).
 While QKD fundamentally does not require interferometry \cite{bib:BennetBrassard84,bib:Ekert91}, some QKD protocols rely on the Mach-Zehnder \cite{Bennett92, bib:Hughes2000,bib:Sasaki14,bib:Takesue15} and Franson interferometers \cite{bib:Ali-Khan07,bib:Brougham13}.
@@
 Nonetheless, this is a classically intractable problem.
-It is also known that boson-sampling is as hard as stimulating the short time evolution of a certain Hamiltonian\cite{bib:Peropadre17}.
+It is also known that boson-sampling is as hard as stimulating the short time evolution of a certain Hamiltonian \cite{bib:Peropadre17}.
 
@@
 \includegraphics[width=0.3\columnwidth]{BS_model}
-\caption{The Boson-Sampling model. A string of n single
-photons is prepared in m optical modes. They are evolved
+\caption{The Boson-Sampling model. A string of $n$ single
+photons is prepared in $m$ optical modes. They are evolved
 via a passive interferometer $U$. Finally the photon-statistics
@@
 
-As experimental imperfections threaten the scalability of {\sc bosonsampling}, there have been efforts to look into its error tolerance \cite{bib:Rohde12_tol}, fault-tolerance \cite{bib:Leverrier15}, and experimental artefacts \cite{bib:Shchesnobich14,bib:Tamma16}.
-Some works have resulted in interesting connections to exotic mathematical entities like immanants \cite{bib:Tan2013,bib:deGuise2014} and the multi-dimensional permanent \cite{bib:Tichy15}.
-A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14} seems particularly attractive in terms of robustness \cite{bib:Motes15_timebin}.
-
-\subsection{Other sampling problems -- hard \& easy}
-
 \peter{
@@
 	\item Cat states (superpositions of coherent states)
-	\item Photon-added coherent states .
-	\item Photon-added or -subtracted squeezed vacuum states.
+	\item Photon-added coherent states.
+	\item Photon-added or photon-subtracted squeezed vacuum states.
 	\item Two-mode squeezed vacuum states (SPDC states).
@@
 \peter{
-Of these, 1-4 have been shown to yield hard sampling problems under photodetection, assuming certain reasonable complexity assumptions.
-And 5-6 have been shown to implement polynomial-time classical algorithms, under Gaussian measurements.}
+Of these, 1--4 have been shown to yield hard sampling problems under photodetection, assuming certain reasonable complexity assumptions.
+And 5--6 have been shown to implement polynomial-time classical algorithms, under Gaussian measurements.}
+
+As experimental imperfections threaten the scalability of {\sc bosonsampling}, there have been efforts to look into its error tolerance \cite{bib:Rohde12_tol}, fault-tolerance \cite{bib:Leverrier15}, and experimental artefacts \cite{bib:Shchesnobich14,bib:Tamma16}.
+Some works have resulted in interesting connections to exotic mathematical entities like immanants \cite{bib:Tan2013,bib:deGuise2014} and the multi-dimensional permanent \cite{bib:Tichy15}.
+A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14,bib:HeDing17} seems particularly attractive in terms of robustness \cite{bib:Motes15_timebin}.
 
@@
 The purpose of such a quantum network is to communicate and process quantum information over long distances.
-While photons serve as great medium for information transfer, many implementations of photonic repeater network require some kind of nonlinear interactions involving cavities for entanglement distillation \cite{Briegel98}, quantum memories \cite{Duan01}, or feedforwarding \cite{bib:Azuma15}.
+While photons serve as useful medium for information transfer, many implementations of photonic repeater network require some kind of nonlinear interactions involving cavities for entanglement distillation \cite{Briegel98}, quantum memories \cite{Duan01}, or feedforwarding \cite{bib:Azuma15}.
 The seminal work of Duan et al.~ \cite{Duan01}, in particular, uses atomic ensemble as quantum memories.
@@
 \cite{bib:Sinclair14} are able to exceed the TGW bound.
-Other benchmarking tools have also been used to analyze many of these repeater schemes in detail \cite{bib:Muralidhara16}.
+Other benchmarking tools have also been used to analyze some of these repeater schemes in detail \cite{bib:Muralidhara16}.
 In terms of implementation, the greatest distance that a quantum state has been teleported to-date is 1400 km \cite{bib:Ren17}, and is demonstrated between an earth-based source with a detection unit on a satellite in space.
@@
 Linear optical interferometry has become a leading contender for the implementation of quantum information processing protocols.
-The preparation, manipulation and measurement of photonic quantum information has become mainstream and widely employed, with impressive experimental accuracies.
+The preparation, manipulation and measurement of photonic quantum information \sihui{is already} mainstream and widely employed, with impressive experimental accuracies.
 
@@
 Although there are countless physical architectures for the implementation of quantum information processing, and it is far from certain which will win `the quantum race for supremacy, optics will always find a home as the only contender for applications involving quantum communication.
-For this reason, the future of linear optics interferometry is a bright one, which will find inevitable applicability in the future quantum world.
+For this reason, the future of linear optics interferometry is a bright one, a sentiment echoed by others \cite{bib:Rudolph17}, which will find inevitable applicability in the future quantum world.
 

### 2018-02-21 paper.tex
Minor edits by peter

@@
 
-\title{The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications}
+\title{The resurgence of the linear optics quantum interferometer --- recent advances \& applications}
 
@@
 \begin{align} \label{eq:process_matrix}
-\mathcal{E}(\hat\rho) = \sum_{i,j=1}^4 \chi_{i,j} \hat{\sigma}_i\hat\rho\,\hat{\sigma}_j^\dag.
+\mathcal{E}(\hat\rho) = \sum_{i,j=1}^4 \chi_{i,j} \hat{\sigma}_i\hat\rho\,\hat{\sigma}_j^\dag,
 \end{align}
-\peter{which generalises to an arbitrary number of qubits. Here $\chi$ is the process matrix in the Pauli basis.}
+\peter{where $\hat\sigma_i$ are the Pauli operators.
+This generalises to an arbitrary number of qubits.
+Here $\chi$ is the process matrix in the Pauli basis, which fully characterises the quantum process.}
 %\cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
@@
 
+\subsection{NOON states}
+
+A closely related state is the NOON state, written as
+\begin{align}
+\ket{\psi^{\rm (NOON)}_n}=\frac{1}{\sqrt{2}}(\ket{n,0}+\ket{0,n})\ ,
+\end{align}
+in the second quantization representation, \sihui{and the basis is the same as that for eq.~(\ref{eq:dualrail})}.
+This state is structurally similar to an EPR state, but its large photon-number give it great metrological power in quantum phase estimation, allowing saturation of the Heisenberg limit -- a physical bound on accuracy in phase estimation.
+
 \subsection{Greenberger-Horne-Zeilinger (GHZ) states}
@@
 To date, six- \cite{bib:Lu06,bib:Zhang15}, eight- \cite{bib:Huang11,bib:Yao12}, and ten-photons \cite{bib:WangChen16,bib:Chen17} GHZ states have been produced.
-
-The GHZ state is also known as the NOON state, because it is written as
-\begin{align}
-\ket{\psi^{\rm (NOON)}_n}=\frac{1}{\sqrt{2}}(\ket{n,0}+\ket{0,n})\ ,
-\end{align}
-in the second quantization representation, \sihui{and the basis is the same as that for eq.~(\ref{eq:dualrail})}. This notation is commonly used in quantum metrological applications.
 
@@
 The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.
-With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.\sihui{Ref.~\cite{bib:Takesue14} reports a switching time of 100 picoseconds for this type of switch.}
+With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.
+\sihui{Ref.~\cite{bib:Takesue14} reports a switching time of 100 picoseconds for this type of switch.}
 }
@@
 
-\peter{
-Numerous other sampling problems have since been described, using, for example,
+Numerous other hard sampling problems have since been described, using, for example,
 \begin{enumerate}
-	\item Cat states (superpositions of coherent states)
-	\item Photon-added coherent states.
-	\item Photon-added or photon-subtracted squeezed vacuum states.
-	\item Two-mode squeezed vacuum states (SPDC states).
-	\item Gaussian states.
-	\item Positive P-function states.
+	\item Cat states (superpositions of coherent states) \cite{RohdeCat15}.
+	\item Photon-added coherent states \cite{RohdeDisp15}.
+	\item Photon-added or photon-subtracted squeezed vacuum states \cite{RohdePhotAdd15}.
+	\item Two-mode squeezed vacuum states (SPDC states) \cite{SalehSPDC}.
 \end{enumerate}
-}
 
-\peter{
-Of these, 1--4 have been shown to yield hard sampling problems under photodetection, assuming certain reasonable complexity assumptions.
+%\peter{
+%Of these, 1--4 have been shown to yield hard sampling problems under photodetection, assuming certain reasonable complexity assumptions.
 And 5--6 have been shown to implement polynomial-time classical algorithms, under Gaussian measurements.}
@@
 \subsection{Quantum simulations}
-Quantum simulations is about simulating a quantum system by quantum mechanical means \cite{bib:Georgescu14}, and there are generally two approaches to achieving this.
+Quantum simulation involves simulating a quantum system by quantum mechanical means \cite{bib:Georgescu14}, and there are generally two approaches to achieving this.
 The first approach is known as digital quantum simulation and achieved by building a quantum computer from unitary gate components that are generated by a Hamiltonians of quantum processes.
@@
 \subsection{Quantum metrology}\label{subsec:metrology}
-An archetypal task for quantum metrology is the following: Given a Mach-\sihui{Zehnder} interferometer, with an unknown phase shift of magnitude $\varphi$ inserted in one of the two paths (see Fig.
+An archetypal task for quantum metrology is the following: Given a Mach-Zehnder interferometer, with an unknown phase shift of magnitude $\varphi$ inserted in one of the two paths (see Fig.
 \ref{fig:MZ}), can one deduce $\varphi$ via a judicious use of quantum states and measurements with a higher sensitivity than that of a completely classical interferometer?
-Indeed, one can, and the standard deviation, $\Delta\varphi$, after $N$ trials using quantum estimation is $\Delta\varphi=1/N$, which gets a factor of $\sqrt{N}$ improvement over classical phase estimation.
+Indeed, one can, and the standard deviation, $\Delta\varphi$, after $N$ trials using quantum estimation is $\Delta\varphi=1/N$, which achieves a factor of $\sqrt{N}$ improvement over classical phase estimation.
 As this sensitivity is also a fundamental limit arising from Heisenberg's uncertainty principle, {\it i.e.} we cannot measure definitively the phase, it is known as the Heisenberg limit.
@@
 
- As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling \peter{are} readily available, but executes a task that is believed to be hard classically.
+ As discussed in Section \ref{sec:bosonsampling}, the resources needed for Boson-sampling are readily available, but executes a task that is believed to be hard classically.
 Surprisingly, an entanglement between a large number of path labels is possible with single photons in a passive linear optical device.
@@
 The purpose of such a quantum network is to communicate and process quantum information over long distances.
-While photons serve as useful medium for information transfer, many implementations of photonic repeater network require some kind of nonlinear interactions involving cavities for entanglement distillation \cite{Briegel98}, quantum memories \cite{Duan01}, or feedforwarding \cite{bib:Azuma15}.
+While photons serve as a useful medium for information transfer, many implementations of photonic repeater network require some kind of nonlinear interactions involving cavities for entanglement distillation \cite{Briegel98}, quantum memories \cite{Duan01}, or feedforwarding \cite{bib:Azuma15}.
 The seminal work of Duan et al.~ \cite{Duan01}, in particular, uses atomic ensemble as quantum memories.
@@
 Linear optical interferometry has become a leading contender for the implementation of quantum information processing protocols.
-The preparation, manipulation and measurement of photonic quantum information \sihui{is already} mainstream and widely employed, with impressive experimental accuracies.
+The preparation, manipulation and measurement of photonic quantum information is already mainstream and widely employed, with impressive experimental accuracies.
 
-We have discussed the various ways in which quantum information can be represented \sihui{in photonics}, how they can be manipulated and detected, and some of their leading applications.
+We have discussed the various ways in which quantum information can be represented photonically, how they can be manipulated and detected, and some of their leading applications.
 

### 2018-03-28 paper.tex
Final touch up
Added more references, cleaned up some citations, revised a few
grammatical errors

@@
 One of the major successes for linear optics is \sihui{the detection of gravitational waves by the LIGO experiments based on the Michelson interferometer \cite{bib:LIGO2015}.
-Another is} the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}.
+The further application of squeezed light to the detectors promises to reduce quantum noise, which currently limits their performance \cite{bib:Barsotti18}.
+Another advancement is} the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}.
 The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized.
@@
 As a consequence, quantum interference between multiple photons only occur when all quantum labels are the same.
-It is also possible to derive an analogous decomposition to that of Reck {\it et al.~}that realizes the unitary transformation on such photons as a sequence of beamsplitters and internal transformations.
+It is also possible to derive an analogous decomposition to that of Reck {\it et al.~}that realizes the unitary transformation on such photons as a sequence of beamsplitters and internal transformations \cite{bib:Dhand2015}.
 
@@
 The $r_{jk}$ terms can be calculated from the ratios of output intensities at the $k$th port to the input intensity at the $j$th port.
-The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha}\ket{\alpha e^{\phi}}$.
+The remaining phases $\theta_{ij}$ are found by the interference pattern given by a two-mode coherent state $\ket{\alpha}\ket{\alpha e^{i\phi}}$.
 When the states are injected into ports 1, and $j$ respectively, the output intensity at the $k$th port is
@@
 Here, having such a state as a resource enables universal quantum computation using only single-qubit measurements \cite{bib:Raussendorf03}.
-In fact, only (X,Y)-plane measurements are needed \cite{bib:Mantri17}.
+In fact, only $(X,Y)$-plane measurements are needed \cite{bib:Mantri17}.
 Therefore, the preparation of such states is highly valuable, generating much interest in their efficient preparation.
@@
 
-\sihui{This concept for switching is widely used in current laboratories, however it is very slow using present-day technology.
+\sihui{This concept for switching is widely used in current laboratories, however, it is very slow using present-day technology.
 Although switching on its own can be completed in a timespan of the order of picoseconds, the process is slowed by the response time needed for its electronic control.
@@
 This can be challenging given the limited resources to begin with.
-\sihui{Various linear-optical implementations of two-qubit gates important for approximately universal quantum computation are listed in Ref.~\cite{bib:Bartkowiak2010}, and comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05}, hence we will focus on recent advances.}
+\sihui{Various linear-optical implementations of two-qubit gates important for approximately universal quantum computation are listed in Ref.~\cite{bib:Bartkowiak2010}, and comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05, bib:Flamini2018}, hence we will focus on recent advances.}
 
- Integrated photonic circuits has greatly improved the feasibility of LOQC.
+ Integrated photonic circuits have greatly improved the feasibility of LOQC.
 Their small size and interferometric stability enable the requisite quantum interference to happen in certain LOQC settings.
@@
   Although there has been tremendous progress in linear optics, it seems likely that an efficient, and fault-tolerant universal quantum computer will require a hybrid system.
-\sihui{Linear optics is still interesting in its own right for other tasks as discussed in the remainder of this sections.
+\sihui{Linear optics is still interesting in its own right for other tasks as discussed in the remainder of this section.
 We also briefly mention here that single photons and waveplates are used in an already commercial application, namely, quantum key distribution (QKD).
@@
 where $\text{Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first $n$ columns and repeating its $j$th row $s_j$ times.
-The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard), in this statistics contributes to the hardness of the boson-sampling problem.
+The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard) \sihui{to compute}, in this statistics contributes to the hardness of the boson-sampling problem.
 Note that the number of configurations $|S|=\binom{n+m-1}{n}$ in the output superposition scales exponentially with $m$.
@@
 Nonetheless, this is a classically intractable problem.
-It is also known that boson-sampling is as hard as stimulating the short time evolution of a certain Hamiltonian \cite{bib:Peropadre17}.
+It is also known that {\sc BosonSampling} is as hard as stimulating the short time evolution of a certain Hamiltonian \cite{bib:Peropadre17}.
 
@@
 A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14,bib:HeDing17} seems particularly attractive in terms of robustness \cite{bib:Motes15_timebin}.
+\sihui{More discussions of {\sc BosonSampling} can be found in the review paper that is Ref.~\cite{bib:Lund2017}}.
 
@@
 Surprisingly, an entanglement between a large number of path labels is possible with single photons in a passive linear optical device.
-Motes {\it et al.~}harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15_LOQM}.
-Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig.
-\ref{fig:MORDOR}).
+Motes {\it et al.~}harnessed this so-called number-path entanglement for quantum metrology without the use of entangled states \cite{bib:Motes15_LOQM,bib:Olsen2017}.
+Here, the phase shift to be estimated, $\varphi$, manifests itself as a linear phase gradient across $N$ modes (See Fig.~\ref{fig:MORDOR}).
 By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve $\Delta \varphi=\mathcal{O}(N^{-3/2})$ using a coincidence measurement with just a string of $N$ single photons, for up to at least $N=25$ modes.
+\sihui{Shortly after its construction, this scheme was realized experimentally \cite{bib:Zu-En2017}.
+The quantum Cram\'{e}r-Rao bound of estimating $\varphi$ in such interferometers was also analytically computed \cite{bib:Chenglong2017}.}
 

### 2018-04-27 paper.tex
Minor change.
Synchronized color, added reference to new review

@@
 
-\newcommand{\sihui}[1]{{\color{Orchid}{#1}}}
-\newcommand{\peter}[1]{{\color{blue}{#1}}}
+\newcommand{\sihui}[1]{{\color{red}{#1}}}
+\newcommand{\peter}[1]{{\color{red}{#1}}}
 \newcommand{\comment}[1]{{\color{YellowGreen}{#1}}}
@@
 
-\title{The resurgence of the linear optics quantum interferometer --- recent advances \& applications}
+\title{The resurgence of the linear optics \sihui{quantum} interferometer --- recent advances \& applications}
 
@@
 Having all components on chip reduces coupling losses which would be crucial for fault-tolerance \cite{bib:Li15}.
+\sihui{Experimental advancements and limitations of photonic implementations of quantum information processing are discussed at length in another review \cite{bib:Flamini2018}.}
 
@@
 
-\peter{
 In many practical situations, the structure of a linear optical device in terms of its constituent beamsplitters and phase-shifters is known once it is built.
@@
 While the input-to-output amplitudes of a linear optics network may be efficiently determined (in terms of number of measurements), it does not characterise the full quantum process it implements, which may contain errors in other degrees of freedom.
-}
 
@@
 \end{document}
+i

### 2018-05-30 arxiv/paper.tex
Added a folder for the arxiv version.

--- 2018-04-27 paper.tex
@@
-%\documentclass[aps,rmp,twocolumn,amsmath,amssymb,nofootinbib,superscripta
-%ddress]{revtex4}
+\documentclass[pra,singlecolumn,superscriptaddress,twoside,pra]{revtex4}
 
-\documentclass[times,final]{elsarticle}
-\usepackage{revip}
+%\documentclass[times,final]{elsarticle}
+%\usepackage{revip}
 \usepackage{framed,multirow,threeparttable}
@@
 \usepackage{graphicx}
-\usepackage{caption}
 \usepackage{subcaption}
+\captionsetup{compatibility=false}
 
@@
 
-\journal{Reviews in Physics}
-
 \begin{document}
-\verso{Tan and Rohde}
-
-\begin{frontmatter}
-
 %
@@
 %
-
-\author[1,2]{Si-Hui \snm{Tan}}
-\cortext[cor1]{\peter{sihui\_tan@sutd.edu.sg}}
-
-\author[3]{Peter P. \snm{Rohde}\corref{cor1}}
-
-\address[1]{Singapore University of Technology and Design, Singapore 
-University of Technology and Design, 8 Somapah Rd, Singapore 487372}
-\address[2]{Centre for 
-Quantum Technologies, National University of Singapore, Block S15, 3 
-Science Drive 2, Singapore 117543, Singapore}
-\address[3]{Centre for Quantum Software \& Information (CQSI), Faculty 
+\author{Si-Hui Tan}
+\affiliation{Singapore University of Technology and Design, 20 Dover Drive, Singapore 138682}
+\affiliation{Centre for Quantum Technologies, National University of Singapore, Block S15, 3 Science Drive 2, Singapore 117543, Singapore}
+%
+\author{Peter P.~Rohde}
+\affiliation{Centre for Quantum Software \& Information (CQSI), Faculty 
 of Engineering \& Information Technology, University of Technology 
 Sydney, NSW 2007, Australia}
-
-\received{}
-\finalform{}
-\accepted{}
-\availableonline{}
-\communicated{}
 
@@
 
-\begin{keyword}
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
-\MSC 41A05\sep 41A10\sep 65D05\sep 65D17
-%% Keywords
-\KWD Keyword1\sep Keyword2\sep Keyword3
-\end{keyword}
-
-\end{frontmatter}
+\date{\today}
+%\pacs{03.67.Ac,03.67.Dd,03.67.Lx,05.40.Fb}
+\maketitle
 
@@
 Photons make fantastic `flying' qubits, and are readily used for quantum communication \cite{bib:Northup14} and quantum key distribution \cite{bib:Lo14}.
-In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting  \sihui{for spatially encoded qubits \cite{bib:KLM01}.
-At about the same time, Koashi, Yamamoto, and Imoto (KYI) essentially came to the same result for polarization-encoded qubits \cite{Koashi01}.} Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
+In 2001, Knill, Laflamme and Milburn (KLM) showed that efficient quantum computing is possible using only linear optical components, that is single photons, beamsplitters, phase shifters and photon counting for spatially encoded qubits \cite{bib:KLM01}.
+At about the same time, Koashi, Yamamoto, and Imoto (KYI) essentially came to the same result for polarization-encoded qubits \cite{Koashi01}.
+Furthermore, an optical implementation of quantum protocols can potentially piggyback on existing communication infrastructure.
 Combined with the relative ease of transporting quantum states of light, as compared to say trapped ions or superconducting qubits, linear optics forms a powerful platform for quantum information processing.
 
-The promises offered by linear optics have spearheaded many \sihui{scientific and} technical advancements.
-One of the major successes for linear optics is \sihui{the detection of gravitational waves by the LIGO experiments based on the Michelson interferometer \cite{bib:LIGO2015}.
+The promises offered by linear optics have spearheaded many scientific and technical advancements.
+One of the major successes for linear optics is the detection of gravitational waves by the LIGO experiments based on the Michelson interferometer \cite{bib:LIGO2015}.
 The further application of squeezed light to the detectors promises to reduce quantum noise, which currently limits their performance \cite{bib:Barsotti18}.
-Another advancement is} the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}.
+Another advancement is the paradigm shift from bulk optics to integrated photonics \cite{bib:Meany15}.
 The advantage of using such integrated photonics over bulk optics is that it is more stable against phase fluctuations, and miniaturized.
@@
 Having all components on chip reduces coupling losses which would be crucial for fault-tolerance \cite{bib:Li15}.
-\sihui{Experimental advancements and limitations of photonic implementations of quantum information processing are discussed at length in another review \cite{bib:Flamini2018}.}
+Experimental advancements and limitations of photonic implementations of quantum information processing are discussed at length in another review \cite{bib:Flamini2018}.
 
-In the last decade, single photons have been produced mainly through \sihui{nonlinear optical processes know as spontaneous parametric down-conversion (SPDC) and spontaneous four-wave mixing (SFWM) \cite{bib:Eisaman11,bib:Xiong16,bib:Solntsev17}.} \sihui{Both SPDC and SFWM produce} single photons in correlated pairs that has been a staple source of entanglement.
-\sihui{However, SPDC uses up one pump photons per pair, while SFWM requires two.} Through developments in production, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
-Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical \sihui{laboratories}, and three or four photons have become commonplace \cite{bib:Spagnolo12, bib:Tillmann13, bib:Spring13,bib:Broome13, bib:Crespi13}.
+In the last decade, single photons have been produced mainly through nonlinear optical processes know as spontaneous parametric down-conversion (SPDC) and spontaneous four-wave mixing (SFWM) \cite{bib:Eisaman11,bib:Xiong16,bib:Solntsev17}.
+Both SPDC and SFWM produce single photons in correlated pairs that has been a staple source of entanglement.
+However, SPDC uses up one pump photons per pair, while SFWM requires two.
+Through developments in production, the number of high quality indistinguishable photons that can be simultaneously produced have increased steadily over the years.
+Single-photon pairs, once a novelty, are now run-of-the-mill business for quantum optical laboratories, and three or four photons have become commonplace \cite{bib:Spagnolo12, bib:Tillmann13, bib:Spring13,bib:Broome13, bib:Crespi13}.
 Experiments using up to ten photons have been demonstrated \cite{bib:WangChen16, bib:Chen17}.
 We have also seen the meteoric rise of quantum dots in the role for producing single photons \cite{bib:Ding16,bib:WangHe16, bib:213601}.
-They are a scalable source of single photons which are highly indistinguishable, and are produced on demand--a significant advantage over \sihui{nonlinear optical processes which are inherently probabilistic.}
+They are a scalable source of single photons which are highly indistinguishable, and are produced on demand--a significant advantage over nonlinear optical processes which are inherently probabilistic.
 
@@
 freedom like polarization, time-of-arrival, and orbital angular momentum \cite{bib:Tillmann2015,bib:Bozinovic2013, 
-bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM \sihui{and KYI}, new proposals 
+bib:Nicolas2014, bib:Humphreys2013, bib:Donohue2013}. Since KLM and KYI, new proposals 
 for linear optical quantum computations (LOQC) have surfaced 
 \cite{bib:Nielsen04,bib:BrowneRudolph05,bib:Gimeno-Segovia15,bib:Pant17}. 
-\sihui {Some of them support new functionalities like secure delegated quantum 
-computations \cite{bib:Barz12,bib:Fisher14, bib:Tan16}}.
-Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, and \sihui{encrypted quantum walks \cite{bib:Rohde_qw12}} that might be hard or
+Some of them support new functionalities like secure delegated quantum 
+computations \cite{bib:Barz12,bib:Fisher14, bib:Tan16}.
+Others do not promise universality in their processing, but still performs tasks such as sampling \cite{bib:Aaronson11}, and encrypted quantum walks \cite{bib:Rohde_qw12} that might be hard or
 impossible with a classical system.  Such methods open up new ways to engineer 
@@
 A full quantum tomography is costly and time-consuming.
-Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction} \sihui{while quantum tomography is briefly discussed in Section \ref{secQPT}}.
+Some practical methods have been devised to do this reconstruction without resorting to tomography, and these are described in Section \ref{sec:reconstruction} while quantum tomography is briefly discussed in Section \ref{secQPT}.
 In Section \ref{sec:state}, we recap the experimental breakthroughs in state preparation of single photons, and some entangled quantum states.
-This is followed by advances in time-bin based architecture for linear optical networks, \sihui{photodectors, and optical switches in Sections \ref{sec:timebins}, \ref{sec:detector}, and \ref{sec:switch} respectively}.
-Last, but not least, we review applications for linear optical interferometry in \sihui{Section \ref{sec:applications}}.
+This is followed by advances in time-bin based architecture for linear optical networks, photodectors, and optical switches in Sections \ref{sec:timebins}, \ref{sec:detector}, and \ref{sec:switch} respectively.
+Last, but not least, we review applications for linear optical interferometry in Section \ref{sec:applications}.
 
@@
 Rather, fast switching can be used to spatially separate neighbouring time-bins, implement a beamsplitter operation between them, before converting back to time-bin encoding.
-\sihui{Typical switch times that can be achieved are in the picoseconds range \cite{bib:Dietrich16}.} An experiment has built on this idea to implement a two-qubit gate by fast switching to a polarization basis \cite{bib:Humphreys2013}.
+Typical switch times that can be achieved are in the picoseconds range \cite{bib:Dietrich16}.
+An experiment has built on this idea to implement a two-qubit gate by fast switching to a polarization basis \cite{bib:Humphreys2013}.
 Another promising advance is an ultrafast measurement technique for time bins based on converting into frequency bins \cite{bib:Donohue2013}.
@@
 \centering
-\includegraphics[width=0.55\columnwidth]{reck}
+\includegraphics[width=0.4\columnwidth]{reck}
 \caption{Efficient decomposition of arbitrary linear optics 
 networks into a sequence of beamsplitters and phase-shifters.
-\sihui{This setup describes a generalized $n\times n$ multi-port Mach-Zehnder interferometer. Adapted from \cite{bib:Reck1994}.}} \label{fig:Reck}	
+This setup describes a generalized $n\times n$ multi-port Mach-Zehnder interferometer.
+Adapted from \cite{bib:Reck1994}.} \label{fig:Reck}
 \end{figure}
@@
 \centering
-\includegraphics[width=\columnwidth]{configMZI}
-\caption{ \sihui{(a) A decomposition of arbitrary linear optics networks into a sequence of subunitaries, $D_i$, made up of Mach-Zehnder interferometers, and is a universal linear-optical processing unit.
+\includegraphics[width=0.8\columnwidth]{configMZI}
+\caption{(a) A decomposition of arbitrary linear optics networks into a sequence of subunitaries, $D_i$, made up of Mach-Zehnder interferometers, and is a universal linear-optical processing unit.
 These subunitaries are controlled via their photon amplitudes ($\alpha_{i,j}$) and phases ($\phi_{i,j}$).
@@
 The classical control and processing unit sets the parameters for the interferometer, and actively cools it.
-Adapted from \cite{bib:Carolan15}.}} \label{fig:Carolan}
+Adapted from \cite{bib:Carolan15}.} \label{fig:Carolan}
 \end{figure}
 
-Alternatively, \sihui{Mach-Zehnder} interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}.
-\sihui{Such a decomposition and its implementation on an integrated photonic chip are shown in Fig.~\ref{fig:Carolan}.
-} Later, it was shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
+Alternatively, Mach-Zehnder interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}.
+Such a decomposition and its implementation on an integrated photonic chip are shown in Fig.~\ref{fig:Carolan}.
+Later, it was shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
 However, they do not provide an explicit construction for arbitrary unitaries.
 
-If the linear optical transformations \sihui{is to} be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
+If the linear optical transformations is to be realized on various degrees of freedom of light, then it is possible to realize a $n\times n$ arbitrary unitary transformation, where $n=n_s n_p$ for $n_s$ spatial modes, and $n_p$ internal modes, by a sequence of $\mathcal{O}(n_s^2 n_p)$ beamsplitters and $\mathcal{O}(n_s^2)$ internal transformations \cite{bib:Dhand2015}.
 This approach reduces the required number of beamsplitters but increases the total number of optical elements needed by a factor of 2.
@@
 
-\peter{When demonstrating quantum protocols experimentally it is generally absolutely critical to characterise the device prior to actual protocol execution.
+When demonstrating quantum protocols experimentally it is generally absolutely critical to characterise the device prior to actual protocol execution.
 Tomography can be used to reconstruct the full density operator of an output state, and quantum process tomography to reconstruct the full process matrix implemented by a device.
@@
 State tomography is achieved by measuring expectation values in a complete basis for the state Hilbert space.
-For one qubit, for example, a complete basis is the Pauli basis, which wields the completeness relation,}
+For one qubit, for example, a complete basis is the Pauli basis, which wields the completeness relatio,n
 \begin{align}
@@
 \end{align}
-\peter{These traces correspond exactly to the expectation values in the respective bases, which are easily determined using separable measurements.
-\sihui{Sometimes, it is possible to be able to do a tomography from an incomplete number of measurements, {\it i.e.} a number that is less than the number of expectation values, and it is possible using compressed sensing provided some sparsity conditions are met \cite{bib:GLFBE2010,bib:Titchener16,bib:Oren16}.
-In cases where one only wishes to know if a given state is close to a presumed state, one can perform a certification test instead of state tomography \cite{bib:Aolita15}.}
+These traces correspond exactly to the expectation values in the respective bases, which are easily determined using separable measurements.
+Sometimes, it is possible to be able to do a tomography from an incomplete number of measurements, {\it i.e.} a number that is less than the number of expectation values, and it is possible using compressed sensing provided some sparsity conditions are met \cite{bib:GLFBE2010,bib:Titchener16,bib:Oren16}.
+In cases where one only wishes to know if a given state is close to a presumed state, one can perform a certification test instead of state tomography \cite{bib:Aolita15}.
 
 Process tomography employs state tomography as a primitive, applying an equivalent completeness relation, but across the space of quantum processes, which may be decomposed into a basis input to output states.
-For a single qubit process this may be represented as,}
+For a single qubit process this may be represented as,
 \begin{align} \label{eq:process_matrix}
@@
 \end{align}
-\peter{where $\hat\sigma_i$ are the Pauli operators.
-This generalises to an arbitrary number of qubits.
-Here $\chi$ is the process matrix in the Pauli basis, which fully characterises the quantum process.}
+where $\hat\sigma_i$ are the Pauli operators. This generalises to an arbitrary number of qubits. Here $\chi$ is the process matrix in the Pauli basis, which fully characterises the quantum process.
 %\cite{bib:Mitchell03,bib:Obrien04,bib:Lobino08,bib:Saleh11}.
@@
 We will consider advances in each of these.
-\sihui{Quantum state engineering using quantum interferometers has also attracted some interest, and is discussed at the end of this section.}
+Quantum state engineering using quantum interferometers has also attracted some interest, and is discussed at the end of this section.
 
@@
 Recent developments using resonant excitation of quantum dots were able to overcome these limitations.
-Laser pulses are used to excite the electronic resonance of the quantum dots and trigger the emission of high quality single photons \cite{bib:WangHe16}
+Laser pulses are used to excite the electronic resonance of the quantum dots and trigger the emission of high quality single photons \cite{bib:WangHe16}.
 %\cite{bib:Ding16,bib:213601,bib:Ates09, bib:Dirk10,bib:
@@
 \end{align}
-in the second quantization representation, \sihui{and the basis is the same as that for eq.~(\ref{eq:dualrail})}.
+in the second quantization representation, and the basis is the same as that for eq.~(\ref{eq:dualrail}).
 This state is structurally similar to an EPR state, but its large photon-number give it great metrological power in quantum phase estimation, allowing saturation of the Heisenberg limit -- a physical bound on accuracy in phase estimation.
@@
   \centering
-  \includegraphics[width=.7\columnwidth]{fusion}
+  \includegraphics[width=.65\columnwidth]{fusion}
   \caption{}
@@
 
-\sihui{
 \subsection{Quantum state engineering based on the multi-port Mach-Zehnder interferometer}
@@
 Notably, the scheme proposed in \cite{bib:Goyal13} uses multimode single photons and repeated uses of $d=2$ quantum scissors to extend the depth of truncation.
-}
 
@@
 
-\sihui{When} using time-bin encoding of optical qubits, the obvious question is\sihui{: how do we perform single-qubit and two-qubit} operations upon them.
+When using time-bin encoding of optical qubits, the obvious question is: how do we perform single-qubit and two-qubit operations upon them.
 In \cite{bib:Motes14}, a dual-loop architecture was presented for implementing arbitrary passive linear-optics on photonic pulse-trains with time-bin separation $\tau$, shown in Fig.~\ref{fig:FL_arch}.
@@
 The above description applies to passive linear optics, which is sufficient for protocols such as {\sc BosonSampling}, but insufficient for universal optical quantum computation, which requires the addition of ancillary states, and measurement with fast-feedforward.
-To address this, it was shown in \cite{Rohde15} that \sihui{partial measurements can be implemented by coupling in and out arbitrary subsets of the optical modes.
-The coupling is in turn achieved via dynamically preparing ancillary pulse-trains (using the already existing source) that are classically controlled by time-resolved measurements at the output, and changing the switching sequence conditional on these measurement outcomes.}
+To address this, it was shown in \cite{Rohde15} that partial measurements can be implemented by coupling in and out arbitrary subsets of the optical modes.
+The coupling is in turn achieved via dynamically preparing ancillary pulse-trains (using the already existing source) that are classically controlled by time-resolved measurements at the output, and changing the switching sequence conditional on these measurement outcomes.
 
@@
 
-\begin{table}[t]\label{table:PNR}
+\begin{table}[t]
 \centering
@@
 \end{align}
-\sihui{Theoretical modeling of these photodetectors can be made to include realistic effects such as detector finite efficiency, finite-number resolution, dark counts, and crosstalk \cite{bib:LeeYurtsever04, bib:Ramilli10,bib:Kalashnikov12}.
+Theoretical modeling of these photodetectors can be made to include realistic effects such as detector finite efficiency, finite-number resolution, dark counts, and crosstalk \cite{bib:LeeYurtsever04, bib:Ramilli10,bib:Kalashnikov12}.
 These effects are typically described as projections onto mixed states \cite{bib:BARNETT1998}, and their outcomes are represented by positive-operator valued measures.
-Such modeling allows us to analyze these realistic effects on various quantum information protocols, see for {\it e.g.~}\cite{bib:Ozdemir2001,bib:Sperling2014, bib:Matthews16}, and update our characterization of non-classicality \cite{bib:Sperlingbinomial12,bib:Kalashnikov12b, bib:Sperling15,bib:Heilmanndc15, bib:Tan2016}.}
+Such modeling allows us to analyze these realistic effects on various quantum information protocols, see for {\it e.g.~}\cite{bib:Ozdemir2001,bib:Sperling2014, bib:Matthews16}, and update our characterization of non-classicality \cite{bib:Sperlingbinomial12,bib:Kalashnikov12b, bib:Sperling15,bib:Heilmanndc15, bib:Tan2016}.
 
-\sihui{There are many different types of photodetectors.
-Detailed reviews have been written about \sihui{them} \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few important examples.
-}A common example of a non-PNR detector is the avalanche photodiode (APD).
+There are many different types of photodetectors.
+Detailed reviews have been written about them \cite{bib:Hadfield09,bib:Eisaman11}, so we shall only outline a few important examples.
+A common example of a non-PNR detector is the avalanche photodiode (APD).
 These devices are made up of semiconductor material, usually silicon, which generate an electron that quickly generates a cascade of electrons.
@@
 APDs are affordable, offer low dark count rates with reasonable efficiency, and can be made to operate in a broad spectrum of wavelengths.
-\sihui{It is the preferred detection method in quantum information protocols as they are widely available, and do not require special environments to run like some of the other detectors, as we discuss later in this section.
+It is the preferred detection method in quantum information protocols as they are widely available, and do not require special environments to run like some of the other detectors, as we discuss later in this section.
 Nonetheless, they have their limitations.
@@
 deadtime and contributes to photon loss in an APD.
-Deadtime delays for APDs range from tens of nanoseconds to $\mu$s.} Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector.
-This detector operates in its superconducting phase just below the critical density, and it\sihui{s} phase changes back to normal when a photon is absorbed.
+Deadtime delays for APDs range from tens of nanoseconds to $\mu$s.
+Superconducting nanowire single-photon detector (SNSPD) is another  type of non-PNR detector.
+This detector operates in its superconducting phase just below the critical density, and its phase changes back to normal when a photon is absorbed.
 This causes a spike in current around it, which, when detected, would indicate the absorption of the photon.
-\sihui{This SNSPD detector tends to be faster than the APD detector with lower dark count rates.
-However, they require low operating temperatures of 4K maintained by special cryogenic equipment that are expensive and bulky.}
+This SNSPD detector tends to be faster than the APD detector with lower dark count rates.
+However, they require low operating temperatures of 4K maintained by special cryogenic equipment that are expensive and bulky.
 
-PNR detectors are a wonderful addition to the \sihui{linear optical} toolbox.
+PNR detectors are a wonderful addition to the linear optical toolbox.
 A notable example is the superconducting transition edge sensor (TES) which has an extremely high quantum efficiency.
 The principle it operates on is very similar to the SNSPD, but with a much higher sensitivity that allows it to detect the energy of single photons.
-\sihui{They have low dark count rates, however, they are also quite slow, have low maximum counting rates, and, like the SNSPD detectors, are costly to operate due to their very low operating temperatures.} The visible light photon counter (VLPC) is another kind of PNR detector.
+They have low dark count rates, however, they are also quite slow, have low maximum counting rates, and, like the SNSPD detectors, are costly to operate due to their very low operating temperatures.
+The visible light photon counter (VLPC) is another kind of PNR detector.
 The way VLPC works is in principle very similar to the APD, but with an additional layer of silicon that is lightly doped with arsenic (As).
@@
 Thus, the output electrical signal is just proportional to the number of detected photons.
-\sihui{The VLPC can achieve a high quantum efficiency, in fact almost as high as that of the TES, and has a distinct advantage over the TES of not requiring superconducting temperatures.
-However, they do suffer from high dark count rate, and low speeds.}
+The VLPC can achieve a high quantum efficiency, in fact almost as high as that of the TES, and has a distinct advantage over the TES of not requiring superconducting temperatures.
+However, they do suffer from high dark count rate, and low speeds.
 Last, PNR detectors can be created by connecting many non-PNR detectors in parallel to one another, and summing the signals at the output.
@@
 Such an approach has been successfully demonstrated with SNSPD \cite{bib:Divochiy08}, and spatially multiplexed APDs known as multi-pixel photon counters (MPPCs) \cite{bib:Afek09, bib:Chrapkiewicz14}.
-\sihui{Characteristic experimental values for the detector efficiency, timing jitter, dark count rates, and maximum photon number of some types of photodetectors are given in Table \ref{table:PNR}.}
+Characteristic experimental values for the detector efficiency, timing jitter, dark count rates, and maximum photon number of some types of photodetectors are given in Table \ref{table:PNR}.
 
@@
 
-\peter{
 Some of the protocols thus far require switching between different optical modes.
-\sihui{One way to achieve this experimentally for time-bin qubits uses} a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path \cite{bib:Takesue14} (see Fig.~\ref{figMZ}).
+One way to achieve this experimentally for time-bin qubits uses a Mach-Zehnder interferometer with a dynamic, classically-controlled phase-shift in one path \cite{bib:Takesue14} (see Fig.~\ref{figMZ}).
 The variable phase may be implemented in a number of ways using various types of phase modulators, such as electro-optic or acousto-optic modulators.
 With this construction setting the phase to $\phi=0$ performs the identity operation, whereas for $\phi=\pi$ it performs a swap gate.
-\sihui{Ref.~\cite{bib:Takesue14} reports a switching time of 100 picoseconds for this type of switch.}
-}
+Ref.~\cite{bib:Takesue14} reports a switching time of 100 picoseconds for this type of switch.
 
@@
 \centering
-\includegraphics[width=0.55\columnwidth]{MZ}	
-\caption{} \label{figMZ}
+\includegraphics[width=0.4\columnwidth]{MZ}	
+\caption{An optical switch for time-bin qubits that uses a Mach-Zehnder interferometer with a dynamic, classicallly-controlled phase-shift in one path.}
+\label{figMZ}
 \end{figure}
 
- \sihui{Another way to perform switching is to first convert temporal and spatial labels of the photon to a polarization one, and then perform a fast polarization switch before converting it back \cite{bib:HAK11,bib:Humphreys13}.
+Another way to perform switching is to first convert temporal and spatial labels of the photon to a polarization one, and then perform a fast polarization switch before converting it back \cite{bib:HAK11,bib:Humphreys13}.
 Such switches are able to achieve a polarization switch within a 10 picoseconds time window.
@@
 The typical speed for this type of switching is of order of picoseconds \cite{bib:Dietrich16}.
- }
 
-\sihui{This concept for switching is widely used in current laboratories, however, it is very slow using present-day technology.
+This concept for switching is widely used in current laboratories, however, it is very slow using present-day technology.
 Although switching on its own can be completed in a timespan of the order of picoseconds, the process is slowed by the response time needed for its electronic control.
@@
 Presently this remains a daunting challenge, requiring much further research, with quantum memories being a candidate for loosening the switching time limitations.
-}
 
@@
 This can be challenging given the limited resources to begin with.
-\sihui{Various linear-optical implementations of two-qubit gates important for approximately universal quantum computation are listed in Ref.~\cite{bib:Bartkowiak2010}, and comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05, bib:Flamini2018}, hence we will focus on recent advances.}
+Various linear-optical implementations of two-qubit gates important for approximately universal quantum computation are listed in Ref.~\cite{bib:Bartkowiak2010}, and comprehensive reviews have been written previously to cover this topic \cite{bib:JW12,bib:Kok05, bib:Flamini2018}, hence we will focus on recent advances.
 
@@
   Although there has been tremendous progress in linear optics, it seems likely that an efficient, and fault-tolerant universal quantum computer will require a hybrid system.
-\sihui{Linear optics is still interesting in its own right for other tasks as discussed in the remainder of this section.
+Linear optics is still interesting in its own right for other tasks as discussed in the remainder of this section.
 We also briefly mention here that single photons and waveplates are used in an already commercial application, namely, quantum key distribution (QKD).
@@
 Thus, linear optics remains fascinating platform for applications and foundation work.
-}
 
@@
 where $\text{Per}()$ denotes the permanent of a matrix, $S=\{s_1,\dots,s_m\}$ denotes an output photon-number configuration, and $U_S$ is obtained from the interferometer unitary $U$ by keeping its first $n$ columns and repeating its $j$th row $s_j$ times.
-The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard) \sihui{to compute}, in this statistics contributes to the hardness of the boson-sampling problem.
+The appearance of the permanent, which is \#P-hard in general (a complexity class even harder than NP-hard) to compute, in this statistics contributes to the hardness of the boson-sampling problem.
 Note that the number of configurations $|S|=\binom{n+m-1}{n}$ in the output superposition scales exponentially with $m$.
@@
 A time-bin implementation of {\sc bosonsampling} \cite{bib:Motes14,bib:HeDing17} seems particularly attractive in terms of robustness \cite{bib:Motes15_timebin}.
-\sihui{More discussions of {\sc BosonSampling} can be found in the review paper that is Ref.~\cite{bib:Lund2017}}.
+More discussions of {\sc BosonSampling} can be found in the review paper that is Ref.~\cite{bib:Lund2017}.
 
-\sihui{
 \subsection{Quantum simulations}
@@
 Quantum interferometers can also be used to simulate quantum walks which in turn can be used to simulate topological phases \cite{bib:Kitagawa12}, transitions between fermionic and bosonic behavior \cite{bib:Schreiber11, bib:Sansoni12,bib:Matthews13,bib:Keil16}, fractional statistics of anyons \cite{bib:Han07,bib:Pachos09, bib:Chao-Yang09}, and excitation transfer in biological systems \cite{bib:Caruso11,bib:Viciani16}.
-  }
 
@@
 By straddling these modes among a quantum Fourier transform and its conjugate operation, it is possible to achieve $\Delta \varphi=\mathcal{O}(N^{-3/2})$ using a coincidence measurement with just a string of $N$ single photons, for up to at least $N=25$ modes.
-\sihui{Shortly after its construction, this scheme was realized experimentally \cite{bib:Zu-En2017}.
-The quantum Cram\'{e}r-Rao bound of estimating $\varphi$ in such interferometers was also analytically computed \cite{bib:Chenglong2017}.}
+Shortly after its construction, this scheme was realized experimentally \cite{bib:Zu-En2017}.
+The quantum Cram\'{e}r-Rao bound of estimating $\varphi$ in such interferometers was also analytically computed \cite{bib:Chenglong2017}.
 
@@
   \centering
-  \includegraphics[width=0.5\columnwidth]{phE}
+  \includegraphics[width=0.4\columnwidth]{phE}
   \caption{}
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{MORDOR}
+  \includegraphics[width=0.75\columnwidth]{MORDOR}
   \caption{}
@@
 
-\sihui{
 \subsection{Repeater networks}
@@
 If it could be made to work with other basic units of quantum repeater networks that have been implemented \cite{bib:Kimble08,bib:Sangouard11, bib:MATN15}, a large-scale, long-distance repeater network could soon be possible.
-
-}
 
@@
 
-%% `Elsevier LaTeX' style
-\bibliographystyle{elsarticle-num}
+\bibliography{paper}
+\bibliographystyle{apsrev4-1.bst}
 
 %%%%%%%%%%%%%%%%%%%%%%%
-\bibliography{paper}
 

### 2019-01-03 arxiv/paper.tex
Added references

@@
-\documentclass[pra,singlecolumn,superscriptaddress,twoside,pra]{revtex4}
+\documentclass[pra,singlecolumn,superscriptaddress]{revtex4}
 
@@
 \usepackage{framed,multirow,threeparttable}
-\usepackage{hyperref,mathrsfs,amsmath,amssymb,latexsym,array,hhline}
+\usepackage{mathrsfs,amsmath,amssymb,latexsym,array,hhline}
 \newcommand{\bra}[1]{\langle#1|}
@@
 %\usepackage[colorlinks]{hyperref}
-\usepackage[dvipsnames]{xcolor}
 
-\newcommand{\sihui}[1]{{\color{red}{#1}}}
-\newcommand{\peter}[1]{{\color{red}{#1}}}
-\newcommand{\comment}[1]{{\color{YellowGreen}{#1}}}
 \newcommand{\ah}{\hat{a}}
 \newcommand{\adagh}{\hat{a}^\dag}
-
-\definecolor{newcolor}{rgb}{.8,.349,.1}
 
@@
 %
-\author{Si-Hui Tan}
+\author{Si-Hui Tan}\email{sihui\_tan@sutd.edu.sg}
 \affiliation{Singapore University of Technology and Design, 20 Dover Drive, Singapore 138682}
@@
 %
+
 \author{Peter P.~Rohde}
@@
 \centering
-\includegraphics[width=0.4\columnwidth]{reck}
+\includegraphics[width=0.4\columnwidth]{Reck.pdf}
 \caption{Efficient decomposition of arbitrary linear optics 
@@
 \centering
-\includegraphics[width=0.8\columnwidth]{configMZI}
+\includegraphics[width=0.8\columnwidth]{configMZI.pdf}
 \caption{(a) A decomposition of arbitrary linear optics networks into a sequence of subunitaries, $D_i$, made up of Mach-Zehnder interferometers, and is a universal linear-optical processing unit.
@@
   \centering
-  \includegraphics[width=.5\columnwidth]{cluster_state}
+  \includegraphics[width=.5\columnwidth]{cluster_state.pdf}
   \caption{}
@@
   \centering
-  \includegraphics[width=.65\columnwidth]{fusion}
+  \includegraphics[width=.65\columnwidth]{fusion.pdf}
   \caption{}
@@
 \centering
-\includegraphics[width=0.3\columnwidth]{qscissors}
+\includegraphics[width=0.3\columnwidth]{qscissors.pdf}
 \caption{Figure showing optical state truncation for $d=1$.
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{full_architecture}
+  \includegraphics[width=0.7\columnwidth]{full_architecture.pdf}
   \caption{}
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{PBS_TB}
+  \includegraphics[width=0.8\columnwidth]{PBS_TB.pdf}
   \caption{}
@@
 \centering
-\includegraphics[width=0.4\columnwidth]{MZ}	
+\includegraphics[width=0.4\columnwidth]{MZ.pdf}	
 \caption{An optical switch for time-bin qubits that uses a Mach-Zehnder interferometer with a dynamic, classicallly-controlled phase-shift in one path.}
@@
 \centering
-\includegraphics[width=0.3\columnwidth]{BS_model}
+\includegraphics[width=0.3\columnwidth]{BS_model.pdf}
 \caption{The Boson-Sampling model. A string of $n$ single
@@
   \centering
-  \includegraphics[width=0.4\columnwidth]{phE}
+  \includegraphics[width=0.4\columnwidth]{phE.pdf}
   \caption{}
@@
   \centering
-  \includegraphics[width=0.75\columnwidth]{MORDOR}
+  \includegraphics[width=0.75\columnwidth]{MORDOR.pdf}
   \caption{}
@@
 \section*{Acknowledgments}
+The authors thank A.~Laing and J.~O'Brien for their permission to use Figure 1 of \cite{bib:Carolan15}.
 PPR is funded by an ARC Future Fellowship (project FT160100397).
-This research was supported in part by the Singapore National Research Foundation under NRF Award No.
-NRF-NRFF2013-01.
+This research was supported in part by the Singapore National Research Foundation under NRF Award No.~NRF-NRFF2013-01.
 ST acknowldeges support from the Air Force Office of Scientific Research under AOARD grant FA2386-15-1-4082.

### 2019-01-03 submitted_v2/review_v3/paper.tex
Added references

--- 2018-04-27 paper.tex
@@
 
-Alternatively, \sihui{Mach-Zehnder} interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Englert2001}.
+Alternatively, \sihui{Mach-Zehnder} interferometers can also be employed as building blocks instead of beamsplitters and phase-shifters \cite{bib:Carolan15,bib:Englert2001, bib:Clements16}.
 \sihui{Such a decomposition and its implementation on an integrated photonic chip are shown in Fig.~\ref{fig:Carolan}.
-} Later, it was shown that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics \cite{bib:Bouland2014}.
+The scheme deployed by Clements {\it et al.}~\cite{bib:Clements16} requires only half the optical depth of Reck {\it et al.} and is robust to optical losses.
+A different route was taken by de Guise et al.~\cite{bib:deguise18} following a technique that decomposes a $n \times n$ unitary matrix into a beamsplitter sandwiched by two $(n-1) \times (n-1)$ unitary matrices.
+The technique can be used recursively to an elegant sequence of adjacent beamsplitters.
+This could be good experimentally for hard coded photonic circuits because it is difficult to mix non-adjacent modes there.
+The method of Clements et al.~share this advantage, but that of de Guise et al.~has an added advantage, that is, it uses fewer infinitesimal generators to get the same $n \times n$ unitary matrix.
+When the size of $n$ gets large and/or  the number of photons in the system is also large, the size of the full Hilbert space becomes large and a decomposition that uses fewer generators becomes obviously advantageous.} Later, it was shown by Bouland and Aaronson \cite{bib:Bouland2014} that any nontrivial beamsplitter, that does more than permuting modes or adding phases to them, is universal for linear optics.
 However, they do not provide an explicit construction for arbitrary unitaries.
@@
 \sihui{Shortly after its construction, this scheme was realized experimentally \cite{bib:Zu-En2017}.
-The quantum Cram\'{e}r-Rao bound of estimating $\varphi$ in such interferometers was also analytically computed \cite{bib:Chenglong2017}.}
+The quantum Cram\'{e}r-Rao bound of estimating $\varphi$ in such interferometers was also analytically computed \cite{bib:Chenglong2017}.
+Also making use of entanglement, in this case, that of continuous variable multipartite entanglement, Zhuang et al.~showed that Heisenberg scaling in $N$ can be achieved when sensing a small phase shift that is distributed across $N$ modes \cite{ZZS18}.
+ }
 
@@
 
-Without the use of repeaters, it has been shown that the rate transmission of a channel with loss without entanglement assistance has a linear fallout \cite{bib:TGW14}, and its bound is known as the Takeoka-Guha-Wilde (TGW) bound.
-The minimal resources required to exceed the TGW bound is a subject of active research, and so far it has been shown that the performance of the repeater schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al.
-\cite{bib:Sinclair14} are able to exceed the TGW bound.
+%Without the use of repeaters, it has been shown that the rate transmission of a 
+%channel with loss without entanglement assistance has a linear fallout 
+%\cite{bib:TGW14}, and its bound is known as the Takeoka-Guha-Wilde (TGW) bound. 
+%The minimal resources required to exceed the TGW bound is a subject of active 
+%research, and so far it has been shown that the performance of the repeater 
+%schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al. 
+%\cite{bib:Sinclair14} are able to exceed the TGW bound. 
+Without the use of repeaters it has been shown that the asymptotic rate of transmission of a channel with loss without entanglement assistance has a linear fallout according to the Takeoka-Guha-Wilde (TGW) bound \cite{bib:TGW14} and the tighter Pirandola-Laurenza-Ottaviani-Banchi (PLOB) bound \cite{PLOB17}.
+In particular, the PLOB bound coincides with the best known lower bound \cite{PGBL09} and establishes the two-way quantum capacity of the lossy channel.
+These results were refined by Wilde, Tomamichel and Berta who derived non-asymptotic rates that are applicable to protocols using such a channel finitely many times \cite{WTB17}.
+Others have generalized the TGW bound for arbitrary network topology \cite{AML16}.
+The minimal resources required to exceed the linear fallout is a subject of active research, and so far it has been beaten by the repeater schemes of Ewert-Bergmann-van Loock \cite{bib:Ewert16}, and Sinclair et al.~\cite{bib:Sinclair14}.
+
 Other benchmarking tools have also been used to analyze some of these repeater schemes in detail \cite{bib:Muralidhara16}.
@@
 If it could be made to work with other basic units of quantum repeater networks that have been implemented \cite{bib:Kimble08,bib:Sangouard11, bib:MATN15}, a large-scale, long-distance repeater network could soon be possible.
-
 }
@@
 \section*{Acknowledgments}
-PPR is funded by an ARC Future Fellowship (project FT160100397).
-This research was supported in part by the Singapore National Research Foundation under NRF Award No.
-NRF-NRFF2013-01.
-ST acknowldeges support from the Air Force Office of Scientific Research under AOARD grant FA2386-15-1-4082.
+\sihui{We thank Hubert de Guise, Stefano Pirandola, Marco Tomamichel, and Quntao Zhuang for useful comments.} PPR is funded by an ARC Future Fellowship (project FT160100397).
+This research was supported in part by the Singapore National Research Foundation under NRF Award No.~NRF-NRFF2013-01.
+ST acknowledges support from the Air Force Office of Scientific Research under AOARD grant FA2386-15-1-4082 \sihui{and FA2386-18-1-4003.
+ST conducted part of this writing while she was a Guest Researcher at the Niels Bohr International Academy.}
 

### 2019-01-04 submitted_v2/review_v3/paper.tex
Reflected changes in reply-to-referee file.

@@
 In particular, the PLOB bound coincides with the best known lower bound \cite{PGBL09} and establishes the two-way quantum capacity of the lossy channel.
-These results were refined by Wilde, Tomamichel and Berta who derived non-asymptotic rates that are applicable to protocols using such a channel finitely many times \cite{WTB17}.
+PLOB showed that if the transmission rate is above the PLOB bound, the error will not vanish asymptotically.
+These results were refined by Wilde, Tomamichel and Berta who showed that with a rate above the PLOB bound one will decode wrongly with certainty, and also derived non-asymptotic bounds that are applicable when the channel is used only a finite number of times \cite{WTB17}.
 Others have generalized the TGW bound for arbitrary network topology \cite{AML16}.
